### 2022-12-11 latex/beale_best_fits.tex
First Commit

\begin{tabular}{llrrr}
\toprule
Algorithm &                               Solution &  Iterations &  Function Evaluations &  Function Value \\
\midrule
      dfp &  2.9999999997259486,0.4999999999232928 &           8 &                    10 &    1.378756e-20 \\
     bfgs &   3.000000000000004,0.5000000000000007 &          15 &                    18 &    8.125884e-30 \\
    lbfgs &  3.0000000003576988,0.5000000000625404 &          14 &                    50 &    3.625854e-20 \\
      lma & 2.9999997171743287,0.49999992960730744 &          12 &                    13 &    1.280491e-14 \\
\bottomrule
\end{tabular}

### 2022-12-11 latex/matyas_best_fits.tex
First Commit

\begin{tabular}{llrrr}
\toprule
Algorithm &                                        Solution &  Iterations &  Function Evaluations &  Function Value \\
\midrule
      dfp &   1.7926757117875478e-11,1.7863785568107216e-11 &           7 &                    10 &    1.281062e-23 \\
     bfgs & -4.0285184756435043e-19,-4.0615726129211233e-19 &           7 &                    10 &    6.547689e-39 \\
    lbfgs &   -3.837208328860697e-15,4.6629367034256575e-15 &           4 &                    16 &    1.806993e-29 \\
      lma &   3.5389027698051246e-06,3.5389027799876804e-06 &          14 &                    15 &    5.009533e-13 \\
\bottomrule
\end{tabular}

### 2022-12-11 latex/matyas_function_values.tex
First Commit

\begin{tabular}{lrrrr}
\toprule
Algorithm &      Minimal &      Maximum &         Mean &       Median \\
\midrule
      dfp & 1.281062e-23 & 1.159689e-09 & 6.085427e-11 & 5.222055e-12 \\
     bfgs & 6.547689e-39 & 6.314078e-18 & 2.829248e-19 & 4.146166e-22 \\
    lbfgs & 1.806993e-29 & 4.906348e-10 & 1.455184e-11 & 5.802267e-14 \\
      lma & 5.009533e-13 & 2.403290e-09 & 1.680342e-10 & 2.454947e-11 \\
\bottomrule
\end{tabular}

### 2022-12-11 latex/rastrigin2d_best_fits.tex
First Commit

\begin{tabular}{llrrr}
\toprule
Algorithm &                                       Solution &  Iterations &  Function Evaluations &  Function Value \\
\midrule
      dfp & -1.3945825916973396e-12,1.3762564161053067e-12 &           6 &                    11 &             0.0 \\
     bfgs &  4.190758074827946e-12,-2.1862133845293774e-11 &           8 &                    49 &             0.0 \\
    lbfgs &  8.784224615873606e-12,-3.6460273411768743e-11 &           5 &                   133 &             0.0 \\
      lma &  2.6660763338975985e-10,1.5611908894664897e-09 &           4 &                     5 &             0.0 \\
\bottomrule
\end{tabular}

### 2022-12-11 latex/rastrigin2d_function_values.tex
First Commit

\begin{tabular}{lrrrr}
\toprule
Algorithm &  Minimal &      Maximum &         Mean &       Median \\
\midrule
      dfp &      0.0 & 1.492140e-13 & 1.186606e-14 & 0.000000e+00 \\
     bfgs &      0.0 & 0.000000e+00 & 0.000000e+00 & 0.000000e+00 \\
    lbfgs &      0.0 & 1.989918e+00 & 1.989918e-02 & 0.000000e+00 \\
      lma &      0.0 & 3.552714e-15 & 1.882938e-15 & 3.552714e-15 \\
\bottomrule
\end{tabular}

### 2022-12-11 latex/rastrigin30d_function_values.tex
First Commit

\begin{tabular}{lrrrr}
\toprule
Algorithm &  Minimal &      Maximum &         Mean &  Median \\
\midrule
      dfp &      0.0 & 1.648459e-12 & 5.002221e-14 &     0.0 \\
     bfgs &      0.0 & 0.000000e+00 & 0.000000e+00 &     0.0 \\
    lbfgs &      0.0 & 0.000000e+00 & 0.000000e+00 &     0.0 \\
      lma &      0.0 & 5.684342e-14 & 1.477929e-14 &     0.0 \\
\bottomrule
\end{tabular}

### 2022-12-11 latex/rastrigin4d_best_fits.tex
First Commit

\begin{tabular}{llrrr}
\toprule
Algorithm &                                           Solution &  Iterations &  Function Evaluations &  Function Value \\
\midrule
      dfp & 7.824099927923849e-11,-2.1366231163644037e-10,-... &          10 &                    21 &             0.0 \\
     bfgs & 5.405272390841542e-12,-2.7239120065655507e-11,-... &          11 &                    61 &             0.0 \\
    lbfgs & 1.471102762075013e-10,1.9145855829354901e-10,8.... &           5 &                   133 &             0.0 \\
      lma & 2.6660763338975985e-10,1.5611908894664897e-09,-... &           4 &                     5 &             0.0 \\
\bottomrule
\end{tabular}

### 2022-12-11 latex/rosenbrock2d_best_fits.tex
First Commit

\begin{tabular}{llrrr}
\toprule
Algorithm &                              Solution &  Iterations &  Function Evaluations &  Function Value \\
\midrule
      dfp & 0.9999999999008999,0.9999999997978861 &          24 &                    31 &    1.135257e-20 \\
     bfgs &                1.0,0.9999999999999999 &          30 &                    43 &    1.232595e-30 \\
    lbfgs & 0.9999999994699225,0.9999999989299816 &          27 &                    76 &    2.907107e-19 \\
      lma & 0.9999999979097256,0.9999999958107717 &          16 &                    18 &    4.376780e-18 \\
\bottomrule
\end{tabular}

### 2022-12-11 latex/rosenbrock2d_function_values.tex
First Commit

\begin{tabular}{lrrrr}
\toprule
Algorithm &      Minimal &      Maximum &         Mean &       Median \\
\midrule
      dfp & 1.135257e-20 & 1.330822e+00 & 3.883331e-02 & 1.008079e-13 \\
     bfgs & 1.232595e-30 & 5.420407e-20 & 1.520616e-21 & 3.568745e-24 \\
    lbfgs & 2.907107e-19 & 6.027957e-11 & 1.010571e-12 & 1.481586e-15 \\
      lma & 4.376780e-18 & 1.308671e-10 & 7.473415e-12 & 8.945853e-13 \\
\bottomrule
\end{tabular}

### 2022-12-11 latex/rosenbrock30d_best_fits.tex
First Commit

\begin{tabular}{llrrr}
\toprule
Algorithm &                                           Solution &  Iterations &  Function Evaluations &  Function Value \\
\midrule
      dfp & 1.000000001426901,1.0000000035108567,1.00000000... &        2767 &                  2790 &    2.303328e-14 \\
     bfgs & 1.0000000000000022,1.0,0.9999999999999846,0.999... &         207 &                   231 &    2.745279e-23 \\
    lbfgs & 1.0000000005707574,1.0000000006791032,1.0000000... &         160 &                   389 &    4.773145e-16 \\
      lma & 1.0,0.9999999999999999,0.9999999999999999,0.999... &          53 &                   131 &    1.018105e-16 \\
\bottomrule
\end{tabular}

### 2022-12-11 latex/rosenbrock30d_function_values.tex
First Commit

\begin{tabular}{lrrrr}
\toprule
Algorithm &      Minimal &   Maximum &      Mean &       Median \\
\midrule
      dfp & 2.303328e-14 & 29.257503 & 13.357326 & 1.307731e+01 \\
     bfgs & 2.745279e-23 &  3.986624 &  0.797325 & 6.316386e-22 \\
    lbfgs & 4.773145e-16 &  3.986624 &  0.199331 & 4.316852e-14 \\
      lma & 1.018105e-16 &  3.986624 &  0.478395 & 2.761710e-13 \\
\bottomrule
\end{tabular}

### 2022-12-11 latex/rosenbrock4d_best_fits.tex
First Commit

\begin{tabular}{llrrr}
\toprule
Algorithm &                                           Solution &  Iterations &  Function Evaluations &  Function Value \\
\midrule
      dfp & 0.9999999966340929,0.9999999907960823,0.9999999... &         292 &                   301 &    3.610838e-15 \\
     bfgs & 1.0000000000000053,1.0000000000000098,1.0000000... &          29 &                    35 &    6.042675e-28 \\
    lbfgs & 0.999999999931242,0.999999999845467,0.999999999... &          45 &                   134 &    1.861496e-19 \\
      lma & 0.9999999999421001,0.9999999998839636,0.9999999... &          18 &                    20 &    7.114597e-20 \\
\bottomrule
\end{tabular}

### 2022-12-11 latex/rosenbrock4d_function_values.tex
First Commit

\begin{tabular}{lrrrr}
\toprule
Algorithm &      Minimal &  Maximum &     Mean &       Median \\
\midrule
      dfp & 3.610838e-15 & 3.707671 & 0.601430 & 1.338231e-03 \\
     bfgs & 6.042675e-28 & 3.701429 & 0.370143 & 1.679398e-23 \\
    lbfgs & 1.861496e-19 & 3.701429 & 0.407157 & 2.624568e-15 \\
      lma & 7.114597e-20 & 3.701429 & 0.333129 & 1.322880e-13 \\
\bottomrule
\end{tabular}

### 2022-12-11 paper/CW01.tex
First Commit

\documentclass{ieeeaccess}
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{mathtools}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{microtype}
\usepackage{float}
\usepackage{adjustbox}
\usepackage{booktabs,makecell,tabularx}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{verbatim}
\usepackage{xcolor}
\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{epsfig} % for postscript graphics files
\usepackage{mathptmx} % assumes new font selection scheme installed
\usepackage{multicol}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Quasi-Newton Methods Comparision using Ackley, Beale, Booth, Matyas, Rastrigin and RosenBrock Functions}
\author{
	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}}
    \IEEEauthorblockN{Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}}
    \IEEEauthorblockN{Christian Piltz Araújo\IEEEauthorrefmark{3}}
    \IEEEauthorblockN{Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}
	\IEEEauthorblockA{\IEEEauthorrefmark{1}augusto.adams@ufpr.br}
	\IEEEauthorblockA{\IEEEauthorrefmark{2}caiomizerkowski@gmail.com}
	\IEEEauthorblockA{\IEEEauthorrefmark{3}christian0294@yahoo.com.br}
	\IEEEauthorblockA{\IEEEauthorrefmark{4}eduardo.reis02@gmail.com}
}

\markboth
{Adams \headeretal: Quasi-Newton Methods Comparision using Ackley, Beale, Booth, Matyas, Rastrigin and RosenBrock Functions}
{Adams \headeretal: Quasi-Newton Methods Comparision using Ackley, Beale, Booth, Matyas, Rastrigin and RosenBrock Functions}

\corresp{Corresponding author: First A. Author (e-mail: author@ boulder.nist.gov).}

\begin{abstract}
In this paper, four optimization algorithms belonging to Quasi-Newton Class are implemented, tested and discussed.

\begin{keywords}
Enter key words or phrases in alphabetical 
order, separated by commas. For a list of suggested keywords, send a blank 
e-mail to keywords@ieee.org or visit \underline
{http://www.ieee.org/organizations/pubs/ani\_prod/keywrd98.txt}
\end{keywords}

\titlepgskip=-15pt

\maketitle

\section{Introduction}
\label{sec:introduction}
\PARstart{T}{his} document is a template for \LaTeX. If you are 
reading a paper or PDF version of this document, please download the 
electronic file, trans\_jour.tex, from the IEEE Web site at \underline
{http://ieeeauthorcenter.ieee.org/create-your-ieee-article/}\break\underline{use-authoring-tools-and-ieee-article-templates/ieee-article-}\break\underline{templates/} so you can use it to prepare your manuscript. If 
you would prefer to use LaTeX, download IEEE's LaTeX style and sample files 
from the same Web page. You can also explore using the Overleaf editor at 
\underline
{https://www.overleaf.com/blog/278-how-to-use-overleaf-}\break\underline{with-ieee-collabratec-your-quick-guide-to-getting-started}\break\underline{\#.xsVp6tpPkrKM9}

If your paper is intended for a conference, please contact your conference 
editor concerning acceptable word processor formats for your particular 
conference.

IEEE will do the final formatting of your paper. If your paper is intended 
for a conference, please observe the conference page limits.

\subsection{Abbreviations and Acronyms}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have already been defined in the abstract. Abbreviations 
such as IEEE, SI, ac, and dc do not have to be defined. Abbreviations that 
incorporate periods should not have spaces: write ``C.N.R.S.,'' not ``C. N. 
R. S.'' Do not use abbreviations in the title unless they are unavoidable 
(for example, ``IEEE'' in the title of this article).

\subsection{Other Recommendations}
Use one space after periods and colons. Hyphenate complex modifiers: 
``zero-field-cooled magnetization.'' Avoid dangling participles, such as, 
``Using \eqref{eq}, the potential was calculated.'' [It is not clear who or what 
used \eqref{eq}.] Write instead, ``The potential was calculated by using \eqref{eq},'' or 
``Using \eqref{eq}, we calculated the potential.''

Use a zero before decimal points: ``0.25,'' not ``.25.'' Use 
``cm$^{3}$,'' not ``cc.'' Indicate sample dimensions as ``0.1 cm 
$\times $ 0.2 cm,'' not ``0.1 $\times $ 0.2 cm$^{2}$.'' The 
abbreviation for ``seconds'' is ``s,'' not ``sec.'' Use 
``Wb/m$^{2}$'' or ``webers per square meter,'' not 
``webers/m$^{2}$.'' When expressing a range of values, write ``7 to 
9'' or ``7--9,'' not ``7$\sim $9.''

A parenthetical statement at the end of a sentence is punctuated outside of 
the closing parenthesis (like this). (A parenthetical sentence is punctuated 
within the parentheses.) In American English, periods and commas are within 
quotation marks, like ``this period.'' Other punctuation is ``outside''! 
Avoid contractions; for example, write ``do not'' instead of ``don't.'' The 
serial comma is preferred: ``A, B, and C'' instead of ``A, B and C.''

If you wish, you may write in the first person singular or plural and use 
the active voice (``I observed that $\ldots$'' or ``We observed that $\ldots$'' 
instead of ``It was observed that $\ldots$''). Remember to check spelling. If 
your native language is not English, please get a native English-speaking 
colleague to carefully proofread your paper.

Try not to use too many typefaces in the same article. You're writing
scholarly papers, not ransom notes. Also please remember that MathJax
can't handle really weird typefaces.

\subsection{Equations}
Number equations consecutively with equation numbers in parentheses flush 
with the right margin, as in \eqref{eq}. To make your equations more 
compact, you may use the solidus (~/~), the exp function, or appropriate 
exponents. Use parentheses to avoid ambiguities in denominators. Punctuate 
equations when they are part of a sentence, as in
\begin{equation}E=mc^2.\label{eq}\end{equation}

Be sure that the symbols in your equation have been defined before the 
equation appears or immediately following. Italicize symbols ($T$ might refer 
to temperature, but T is the unit tesla). Refer to ``\eqref{eq},'' not ``Eq. \eqref{eq}'' 
or ``equation \eqref{eq},'' except at the beginning of a sentence: ``Equation \eqref{eq} 
is $\ldots$ .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\section{Units}
Use either SI (MKS) or CGS as primary units. (SI units are strongly 
encouraged.) English units may be used as secondary units (in parentheses). 
This applies to papers in data storage. For example, write ``15 
Gb/cm$^{2}$ (100 Gb/in$^{2})$.'' An exception is when 
English units are used as identifiers in trade, such as ``3\textonehalf-in 
disk drive.'' Avoid combining SI and CGS units, such as current in amperes 
and magnetic field in oersteds. This often leads to confusion because 
equations do not balance dimensionally. If you must use mixed units, clearly 
state the units for each quantity in an equation.

The SI unit for magnetic field strength $H$ is A/m. However, if you wish to use 
units of T, either refer to magnetic flux density $B$ or magnetic field 
strength symbolized as $\mu _{0}H$. Use the center dot to separate 
compound units, e.g., ``A$\cdot $m$^{2}$.''

\section{Some Common Mistakes}
The word ``data'' is plural, not singular. The subscript for the 
permeability of vacuum $\mu _{0}$ is zero, not a lowercase letter 
``o.'' The term for residual magnetization is ``remanence''; the adjective 
is ``remanent''; do not write ``remnance'' or ``remnant.'' Use the word 
``micrometer'' instead of ``micron.'' A graph within a graph is an 
``inset,'' not an ``insert.'' The word ``alternatively'' is preferred to the 
word ``alternately'' (unless you really mean something that alternates). Use 
the word ``whereas'' instead of ``while'' (unless you are referring to 
simultaneous events). Do not use the word ``essentially'' to mean 
``approximately'' or ``effectively.'' Do not use the word ``issue'' as a 
euphemism for ``problem.'' When compositions are not specified, separate 
chemical symbols by en-dashes; for example, ``NiMn'' indicates the 
intermetallic compound Ni$_{0.5}$Mn$_{0.5}$ whereas 
``Ni--Mn'' indicates an alloy of some composition 
Ni$_{x}$Mn$_{1-x}$.

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt){fig1.png}
{Magnetization as a function of applied field.
It is good practice to explain the significance of the figure in the caption.\label{fig1}}

Be aware of the different meanings of the homophones ``affect'' (usually a 
verb) and ``effect'' (usually a noun), ``complement'' and ``compliment,'' 
``discreet'' and ``discrete,'' ``principal'' (e.g., ``principal 
investigator'') and ``principle'' (e.g., ``principle of measurement''). Do 
not confuse ``imply'' and ``infer.''

Prefixes such as ``non,'' ``sub,'' ``micro,'' ``multi,'' and ``ultra'' are 
not independent words; they should be joined to the words they modify, 
usually without a hyphen. There is no period after the ``et'' in the Latin 
abbreviation ``\emph{et al.}'' (it is also italicized). The abbreviation ``i.e.,'' means 
``that is,'' and the abbreviation ``e.g.,'' means ``for example'' (these 
abbreviations are not italicized).

A general IEEE styleguide is available at \underline{http://www.ieee.org/}\break\underline{authortools}.

\section{Guidelines for Graphics Preparation and Submission}
\label{sec:guidelines}

\subsection{Types of Graphics}
The following list outlines the different types of graphics published in 
IEEE journals. They are categorized based on their construction, and use of 
color/shades of gray:

\subsubsection{Color/Grayscale figures}
{Figures that are meant to appear in color, or shades of black/gray. Such 
figures may include photographs, illustrations, multicolor graphs, and 
flowcharts.}

\subsubsection{Line Art figures}
{Figures that are composed of only black lines and shapes. These figures 
should have no shades or half-tones of gray, only black and white.}

\subsubsection{Author photos}
{Head and shoulders shots of authors that appear at the end of our papers. }

\subsubsection{Tables}
{Data charts which are typically black and white, but sometimes include 
color.}

\begin{table}
\caption{Units for Magnetic Properties}
\label{table}
\setlength{\tabcolsep}{3pt}
\begin{tabular}{|p{25pt}|p{75pt}|p{115pt}|}
\hline
Symbol& 
Quantity& 
Conversion from Gaussian and \par CGS EMU to SI $^{\mathrm{a}}$ \\
\hline
$\Phi $& 
magnetic flux& 
1 Mx $\to  10^{-8}$ Wb $= 10^{-8}$ V$\cdot $s \\
$B$& 
magnetic flux density, \par magnetic induction& 
1 G $\to  10^{-4}$ T $= 10^{-4}$ Wb/m$^{2}$ \\
$H$& 
magnetic field strength& 
1 Oe $\to  10^{3}/(4\pi )$ A/m \\
$m$& 
magnetic moment& 
1 erg/G $=$ 1 emu \par $\to 10^{-3}$ A$\cdot $m$^{2} = 10^{-3}$ J/T \\
$M$& 
magnetization& 
1 erg/(G$\cdot $cm$^{3}) =$ 1 emu/cm$^{3}$ \par $\to 10^{3}$ A/m \\
4$\pi M$& 
magnetization& 
1 G $\to  10^{3}/(4\pi )$ A/m \\
$\sigma $& 
specific magnetization& 
1 erg/(G$\cdot $g) $=$ 1 emu/g $\to $ 1 A$\cdot $m$^{2}$/kg \\
$j$& 
magnetic dipole \par moment& 
1 erg/G $=$ 1 emu \par $\to 4\pi \times  10^{-10}$ Wb$\cdot $m \\
$J$& 
magnetic polarization& 
1 erg/(G$\cdot $cm$^{3}) =$ 1 emu/cm$^{3}$ \par $\to 4\pi \times  10^{-4}$ T \\
$\chi , \kappa $& 
susceptibility& 
1 $\to  4\pi $ \\
$\chi_{\rho }$& 
mass susceptibility& 
1 cm$^{3}$/g $\to  4\pi \times  10^{-3}$ m$^{3}$/kg \\
$\mu $& 
permeability& 
1 $\to  4\pi \times  10^{-7}$ H/m \par $= 4\pi \times  10^{-7}$ Wb/(A$\cdot $m) \\
$\mu_{r}$& 
relative permeability& 
$\mu \to \mu_{r}$ \\
$w, W$& 
energy density& 
1 erg/cm$^{3} \to  10^{-1}$ J/m$^{3}$ \\
$N, D$& 
demagnetizing factor& 
1 $\to  1/(4\pi )$ \\
\hline
\multicolumn{3}{p{251pt}}{Vertical lines are optional in tables. Statements that serve as captions for 
the entire table do not need footnote letters. }\\
\multicolumn{3}{p{251pt}}{$^{\mathrm{a}}$Gaussian units are the same as cg emu for magnetostatics; Mx 
$=$ maxwell, G $=$ gauss, Oe $=$ oersted; Wb $=$ weber, V $=$ volt, s $=$ 
second, T $=$ tesla, m $=$ meter, A $=$ ampere, J $=$ joule, kg $=$ 
kilogram, H $=$ henry.}
\end{tabular}
\label{tab1}
\end{table}

\subsection{Multipart figures}
Figures compiled of more than one sub-figure presented side-by-side, or 
stacked. If a multipart figure is made up of multiple figure
types (one part is lineart, and another is grayscale or color) the figure 
should meet the stricter guidelines.

\subsection{File Formats For Graphics}\label{formats}
Format and save your graphics using a suitable graphics processing program 
that will allow you to create the images as PostScript (PS), Encapsulated 
PostScript (.EPS), Tagged Image File Format (.TIFF), Portable Document 
Format (.PDF), Portable Network Graphics (.PNG), or Metapost (.MPS), sizes them, and adjusts 
the resolution settings. When 
submitting your final paper, your graphics should all be submitted 
individually in one of these formats along with the manuscript.

\subsection{Sizing of Graphics}
Most charts, graphs, and tables are one column wide (3.5 inches/88 
millimeters/21 picas) or page wide (7.16 inches/181 millimeters/43 
picas). The maximum depth a graphic can be is 8.5 inches (216 millimeters/54
picas). When choosing the depth of a graphic, please allow space for a 
caption. Figures can be sized between column and page widths if the author 
chooses, however it is recommended that figures are not sized less than 
column width unless when necessary.

There is currently one publication with column measurements that do not 
coincide with those listed above. Proceedings of the IEEE has a column 
measurement of 3.25 inches (82.5 millimeters/19.5 picas).

The final printed size of author photographs is exactly
1 inch wide by 1.25 inches tall (25.4 millimeters$\,\times\,$31.75 millimeters/6 
picas$\,\times\,$7.5 picas). Author photos printed in editorials measure 1.59 inches 
wide by 2 inches tall (40 millimeters$\,\times\,$50 millimeters/9.5 picas$\,\times\,$12 
picas).

\subsection{Resolution }
The proper resolution of your figures will depend on the type of figure it 
is as defined in the ``Types of Figures'' section. Author photographs, 
color, and grayscale figures should be at least 300dpi. Line art, including 
tables should be a minimum of 600dpi.

\subsection{Vector Art}
In order to preserve the figures' integrity across multiple computer 
platforms, we accept files in the following formats: .EPS/.PDF/.PS. All 
fonts must be embedded or text converted to outlines in order to achieve the 
best-quality results.

\subsection{Color Space}
The term color space refers to the entire sum of colors that can be 
represented within the said medium. For our purposes, the three main color 
spaces are Grayscale, RGB (red/green/blue) and CMYK 
(cyan/magenta/yellow/black). RGB is generally used with on-screen graphics, 
whereas CMYK is used for printing purposes.

All color figures should be generated in RGB or CMYK color space. Grayscale 
images should be submitted in Grayscale color space. Line art may be 
provided in grayscale OR bitmap colorspace. Note that ``bitmap colorspace'' 
and ``bitmap file format'' are not the same thing. When bitmap color space 
is selected, .TIF/.TIFF/.PNG are the recommended file formats.

\subsection{Accepted Fonts Within Figures}
When preparing your graphics IEEE suggests that you use of one of the 
following Open Type fonts: Times New Roman, Helvetica, Arial, Cambria, and 
Symbol. If you are supplying EPS, PS, or PDF files all fonts must be 
embedded. Some fonts may only be native to your operating system; without 
the fonts embedded, parts of the graphic may be distorted or missing.

A safe option when finalizing your figures is to strip out the fonts before 
you save the files, creating ``outline'' type. This converts fonts to 
artwork what will appear uniformly on any screen.

\subsection{Using Labels Within Figures}

\subsubsection{Figure Axis labels }
Figure axis labels are often a source of confusion. Use words rather than 
symbols. As an example, write the quantity ``Magnetization,'' or 
``Magnetization M,'' not just ``M.'' Put units in parentheses. Do not label 
axes only with units. As in Fig. 1, for example, write ``Magnetization 
(A/m)'' or ``Magnetization (A$\cdot$m$^{-1}$),'' not just ``A/m.'' Do not label axes with a ratio of quantities and 
units. For example, write ``Temperature (K),'' not ``Temperature/K.''

Multipliers can be especially confusing. Write ``Magnetization (kA/m)'' or 
``Magnetization (10$^{3}$ A/m).'' Do not write ``Magnetization 
(A/m)$\,\times\,$1000'' because the reader would not know whether the top 
axis label in Fig. 1 meant 16000 A/m or 0.016 A/m. Figure labels should be 
legible, approximately 8 to 10 point type.

\subsubsection{Subfigure Labels in Multipart Figures and Tables}
Multipart figures should be combined and labeled before final submission. 
Labels should appear centered below each subfigure in 8 point Times New 
Roman font in the format of (a) (b) (c).

\subsection{File Naming}
Figures (line artwork or photographs) should be named starting with the 
first 5 letters of the author's last name. The next characters in the 
filename should be the number that represents the sequential 
location of this image in your article. For example, in author 
``Anderson's'' paper, the first three figures would be named ander1.tif, 
ander2.tif, and ander3.ps.

Tables should contain only the body of the table (not the caption) and 
should be named similarly to figures, except that `.t' is inserted 
in-between the author's name and the table number. For example, author 
Anderson's first three tables would be named ander.t1.tif, ander.t2.ps, 
ander.t3.eps.

Author photographs should be named using the first five characters of the 
pictured author's last name. For example, four author photographs for a 
paper may be named: oppen.ps, moshc.tif, chen.eps, and duran.pdf.

If two authors or more have the same last name, their first initial(s) can 
be substituted for the fifth, fourth, third$\ldots$ letters of their surname 
until the degree where there is differentiation. For example, two authors 
Michael and Monica Oppenheimer's photos would be named oppmi.tif, and 
oppmo.eps.

\subsection{Referencing a Figure or Table Within Your Paper}
When referencing your figures and tables within your paper, use the 
abbreviation ``Fig.'' even at the beginning of a sentence. Do not abbreviate 
``Table.'' Tables should be numbered with Roman Numerals.

\subsection{Checking Your Figures: The IEEE Graphics Analyzer}
The IEEE Graphics Analyzer enables authors to pre-screen their graphics for 
compliance with IEEE Access standards before submission. 
The online tool, located at
\underline{http://graphicsqc.ieee.org/}, allows authors to 
upload their graphics in order to check that each file is the correct file 
format, resolution, size and colorspace; that no fonts are missing or 
corrupt; that figures are not compiled in layers or have transparency, and 
that they are named according to the IEEE Access naming 
convention. At the end of this automated process, authors are provided with 
a detailed report on each graphic within the web applet, as well as by 
email.

For more information on using the Graphics Analyzer or any other graphics 
related topic, contact the IEEE Graphics Help Desk by e-mail at 
graphics@ieee.org.

\subsection{Submitting Your Graphics}
Because IEEE will do the final formatting of your paper,
you do not need to position figures and tables at the top and bottom of each 
column. In fact, all figures, figure captions, and tables can be placed at 
the end of your paper. In addition to, or even in lieu of submitting figures 
within your final manuscript, figures should be submitted individually, 
separate from the manuscript in one of the file formats listed above in 
Section \ref{formats}. Place figure captions below the figures; place table titles 
above the tables. Please do not include captions as part of the figures, or 
put them in ``text boxes'' linked to the figures. Also, do not place borders 
around the outside of your figures.

\subsection{Color Processing/Printing in IEEE Journals}
All IEEE Transactions, Journals, and Letters allow an author to publish 
color figures on IEEE Xplore\textregistered\ at no charge, and automatically 
convert them to grayscale for print versions. In most journals, figures and 
tables may alternatively be printed in color if an author chooses to do so. 
Please note that this service comes at an extra expense to the author. If 
you intend to have print color graphics, include a note with your final 
paper indicating which figures or tables you would like to be handled that 
way, and stating that you are willing to pay the additional fee.

\section{Conclusion}
A conclusion section is not required. Although a conclusion may review the 
main points of the paper, do not replicate the abstract as the conclusion. A 
conclusion might elaborate on the importance of the work or suggest 
applications and extensions.

\appendices

Appendixes, if needed, appear before the acknowledgment.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in American English is 
without an ``e'' after the ``g.'' Use the singular heading even if you have 
many acknowledgments. Avoid expressions such as ``One of us (S.B.A.) would 
like to thank $\ldots$ .'' Instead, write ``F. A. Author thanks $\ldots$ .'' In most 
cases, sponsor and financial support acknowledgments are placed in the 
unnumbered footnote on the first page, not here.

\section*{References and Footnotes}

\subsection{References}
References need not be cited in text. When they are, they appear on the 
line, in square brackets, inside the punctuation. Multiple references are 
each numbered with separate brackets. When citing a section in a book, 
please give the relevant page numbers. In text, refer simply to the 
reference number. Do not use ``Ref.'' or ``reference'' except at the 
beginning of a sentence: ``Reference \cite{b3} shows $\ldots$ .'' Please do not use 
automatic endnotes in \emph{Word}, rather, type the reference list at the end of the 
paper using the ``References'' style.

Reference numbers are set flush left and form a column of their own, hanging 
out beyond the body of the reference. The reference numbers are on the line, 
enclosed in square brackets. In all references, the given name of the author 
or editor is abbreviated to the initial only and precedes the last name. Use 
them all; use \emph{et al.} only if names are not given. Use commas around Jr., 
Sr., and III in names. Abbreviate conference titles. When citing IEEE 
transactions, provide the issue number, page range, volume number, year, 
and/or month if available. When referencing a patent, provide the day and 
the month of issue, or application. References may not include all 
information; please obtain and include relevant information. Do not combine 
references. There must be only one reference with each number. If there is a 
URL included with the print reference, it can be included at the end of the 
reference.

Other than books, capitalize only the first word in a paper title, except 
for proper nouns and element symbols. For papers published in translation 
journals, please give the English citation first, followed by the original 
foreign-language citation See the end of this document for formats and 
examples of common references. For a complete discussion of references and 
their formats, see the IEEE style manual at
\underline{http://www.ieee.org/authortools}.

\subsection{Footnotes}
Number footnotes separately in superscript numbers.\footnote{It is recommended that footnotes be avoided (except for 
the unnumbered footnote with the receipt date on the first page). Instead, 
try to integrate the footnote information into the text.} Place the actual 
footnote at the bottom of the column in which it is cited; do not put 
footnotes in the reference list (endnotes). Use letters for table footnotes 
(see Table \ref{table}).

\section{Submitting Your Paper for Review}

\subsection{Final Stage}
When you submit your final version (after your paper has been accepted), 
print it in two-column format, including figures and tables. You must also 
send your final manuscript on a disk, via e-mail, or through a Web 
manuscript submission system as directed by the society contact. You may use 
\emph{Zip} for large files, or compress files using \emph{Compress, Pkzip, Stuffit,} or \emph{Gzip.}

Also, send a sheet of paper or PDF with complete contact information for all 
authors. Include full mailing addresses, telephone numbers, fax numbers, and 
e-mail addresses. This information will be used to send each author a 
complimentary copy of the journal in which the paper appears. In addition, 
designate one author as the ``corresponding author.'' This is the author to 
whom proofs of the paper will be sent. Proofs are sent to the corresponding 
author only.

\subsection{Review Stage Using ScholarOne\textregistered\ Manuscripts}
Contributions to the Transactions, Journals, and Letters may be submitted 
electronically on IEEE's on-line manuscript submission and peer-review 
system, ScholarOne\textregistered\ Manuscripts. You can get a listing of the 
publications that participate in ScholarOne at 
\underline{http://www.ieee.org/publications\_standards/publications/}\break\underline{authors/authors\_submission.html}.
First check if you have an existing account. If there is none, please create 
a new account. After logging in, go to your Author Center and click ``Submit 
First Draft of a New Manuscript.''

Along with other information, you will be asked to select the subject from a 
pull-down list. Depending on the journal, there are various steps to the 
submission process; you must complete all steps for a complete submission. 
At the end of each step you must click ``Save and Continue''; just uploading 
the paper is not sufficient. After the last step, you should see a 
confirmation that the submission is complete. You should also receive an 
e-mail confirmation. For inquiries regarding the submission of your paper on 
ScholarOne Manuscripts, please contact oprs-support@ieee.org or call +1 732 
465 5861.

ScholarOne Manuscripts will accept files for review in various formats. 
Please check the guidelines of the specific journal for which you plan to 
submit.

You will be asked to file an electronic copyright form immediately upon 
completing the submission process (authors are responsible for obtaining any 
security clearances). Failure to submit the electronic copyright could 
result in publishing delays later. You will also have the opportunity to 
designate your article as ``open access'' if you agree to pay the IEEE open 
access fee.

\subsection{Final Stage Using ScholarOne Manuscripts}
Upon acceptance, you will receive an email with specific instructions 
regarding the submission of your final files. To avoid any delays in 
publication, please be sure to follow these instructions. Most journals 
require that final submissions be uploaded through ScholarOne Manuscripts, 
although some may still accept final submissions via email. Final 
submissions should include source files of your accepted manuscript, high 
quality graphic files, and a formatted pdf file. If you have any questions 
regarding the final submission process, please contact the administrative 
contact for the journal.

In addition to this, upload a file with complete contact information for all 
authors. Include full mailing addresses, telephone numbers, fax numbers, and 
e-mail addresses. Designate the author who submitted the manuscript on 
ScholarOne Manuscripts as the ``corresponding author.'' This is the only 
author to whom proofs of the paper will be sent.

\subsection{Copyright Form}
Authors must submit an electronic IEEE Copyright Form (eCF) upon submitting 
their final manuscript files. You can access the eCF system through your 
manuscript submission system or through the Author Gateway. You are 
responsible for obtaining any necessary approvals and/or security 
clearances. For additional information on intellectual property rights, 
visit the IEEE Intellectual Property Rights department web page at 
\underline{http://www.ieee.org/publications\_standards/publications/}\break\underline{rights/index.html}.

\section{IEEE Publishing Policy}
The general IEEE policy requires that authors should only submit original 
work that has neither appeared elsewhere for publication, nor is under 
review for another refereed publication. The submitting author must disclose 
all prior publication(s) and current submissions when submitting a 
manuscript. Do not publish ``preliminary'' data or results. The submitting 
author is responsible for obtaining agreement of all coauthors and any 
consent required from employers or sponsors before submitting an article. 
The IEEE Access Department strongly discourages courtesy 
authorship; it is the obligation of the authors to cite only relevant prior 
work.

The IEEE Access Department does not publish conference 
records or proceedings, but can publish articles related to conferences that 
have undergone rigorous peer review. Minimally, two reviews are required for 
every article submitted for peer review.

\section{Publication Principles}
The two types of contents of that are published are; 1) peer-reviewed and 2) 
archival. The Access Department publishes scholarly 
articles of archival value as well as tutorial expositions and critical 
reviews of classical subjects and topics of current interest.

Authors should consider the following points:

\begin{enumerate}
\item Technical papers submitted for publication must advance the state of knowledge and must cite relevant prior work. 
\item The length of a submitted paper should be commensurate with the importance, or appropriate to the complexity, of the work. For example, an obvious extension of previously published work might not be appropriate for publication or might be adequately treated in just a few pages.
\item Authors must convince both peer reviewers and the editors of the scientific and technical merit of a paper; the standards of proof are higher when extraordinary or unexpected results are reported. 
\item Because replication is required for scientific progress, papers submitted for publication must provide sufficient information to allow readers to perform similar experiments or calculations and 
use the reported results. Although not everything need be disclosed, a paper 
must contain new, useable, and fully described information. For example, a 
specimen's chemical composition need not be reported if the main purpose of 
a paper is to introduce a new measurement technique. Authors should expect 
to be challenged by reviewers if the results are not supported by adequate 
data and critical details.
\item Papers that describe ongoing work or announce the latest technical achievement, which are suitable for presentation at a professional conference, may not be appropriate for publication.
\end{enumerate}

\section{Reference Examples}

\begin{itemize}

\item \emph{Basic format for books:}\\
J. K. Author, ``Title of chapter in the book,'' in \emph{Title of His Published Book, x}th ed. City of Publisher, (only U.S. State), Country: Abbrev. of Publisher, year, ch. $x$, sec. $x$, pp. \emph{xxx--xxx.}\\
See \cite{b1,b2}.

\item \emph{Basic format for periodicals:}\\
J. K. Author, ``Name of paper,'' \emph{Abbrev. Title of Periodical}, vol. \emph{x, no}. $x, $pp\emph{. xxx--xxx, }Abbrev. Month, year, DOI. 10.1109.\emph{XXX}.123456.\\
See \cite{b3}--\cite{b5}.

\item \emph{Basic format for reports:}\\
J. K. Author, ``Title of report,'' Abbrev. Name of Co., City of Co., Abbrev. State, Country, Rep. \emph{xxx}, year.\\
See \cite{b6,b7}.

\item \emph{Basic format for handbooks:}\\
\emph{Name of Manual/Handbook, x} ed., Abbrev. Name of Co., City of Co., Abbrev. State, Country, year, pp. \emph{xxx--xxx.}\\
See \cite{b8,b9}.

\item \emph{Basic format for books (when available online):}\\
J. K. Author, ``Title of chapter in the book,'' in \emph{Title of
Published Book}, $x$th ed. City of Publisher, State, Country: Abbrev.
of Publisher, year, ch. $x$, sec. $x$, pp. \emph{xxx--xxx}. [Online].
Available: \underline{http://www.web.com}\\
See \cite{b10}--\cite{b13}.

\item \emph{Basic format for journals (when available online):}\\
J. K. Author, ``Name of paper,'' \emph{Abbrev. Title of Periodical}, vol. $x$, no. $x$, pp. \emph{xxx--xxx}, Abbrev. Month, year. Accessed on: Month, Day, year, DOI: 10.1109.\emph{XXX}.123456, [Online].\\
See \cite{b14}--\cite{b16}.

\item \emph{Basic format for papers presented at conferences (when available online): }\\
J.K. Author. (year, month). Title. presented at abbrev. conference title. [Type of Medium]. Available: site/path/file\\
See \cite{b17}.

\item \emph{Basic format for reports and handbooks (when available online):}\\
J. K. Author. ``Title of report,'' Company. City, State, Country. Rep. no., (optional: vol./issue), Date. [Online] Available: site/path/file\\
See \cite{b18,b19}.

\item \emph{Basic format for computer programs and electronic documents (when available online): }\\
Legislative body. Number of Congress, Session. (year, month day). \emph{Number of bill or resolution}, \emph{Title}. [Type of medium]. Available: site/path/file\\
\textbf{\emph{NOTE: }ISO recommends that capitalization follow the accepted practice for the language or script in which the information is given.}\\
See \cite{b20}.

\item \emph{Basic format for patents (when available online):}\\
Name of the invention, by inventor's name. (year, month day). Patent Number [Type of medium]. Available: site/path/file\\
See \cite{b21}.

\item \emph{Basic format}\emph{for conference proceedings (published):}\\
J. K. Author, ``Title of paper,'' in \emph{Abbreviated Name of Conf.}, City of Conf., Abbrev. State (if given), Country, year, pp. \emph{xxxxxx.}\\
See \cite{b22}.

\item \emph{Example for papers presented at conferences (unpublished):}\\
See \cite{b23}.

\item \emph{Basic format for patents}$:$\\
J. K. Author, ``Title of patent,'' U.S. Patent \emph{x xxx xxx}, Abbrev. Month, day, year.\\
See \cite{b24}.

\item \emph{Basic format for theses (M.S.) and dissertations (Ph.D.):}
\begin{enumerate}
\item J. K. Author, ``Title of thesis,'' M.S. thesis, Abbrev. Dept., Abbrev. Univ., City of Univ., Abbrev. State, year.
\item J. K. Author, ``Title of dissertation,'' Ph.D. dissertation, Abbrev. Dept., Abbrev. Univ., City of Univ., Abbrev. State, year.
\end{enumerate}
See \cite{b25,b26}.

\item \emph{Basic format for the most common types of unpublished references:}
\begin{enumerate}
\item J. K. Author, private communication, Abbrev. Month, year.
\item J. K. Author, ``Title of paper,'' unpublished.
\item J. K. Author, ``Title of paper,'' to be published.
\end{enumerate}
See \cite{b27}--\cite{b29}.

\item \emph{Basic formats for standards:}
\begin{enumerate}
\item \emph{Title of Standard}, Standard number, date.
\item \emph{Title of Standard}, Standard number, Corporate author, location, date.
\end{enumerate}
See \cite{b30,b31}.

\item \emph{Article number in~reference examples:}\\
See \cite{b32,b33}.

\item \emph{Example when using et al.:}\\
See \cite{b34}.

\end{itemize}

\begin{thebibliography}{00}

\bibitem{b1} G. O. Young, ``Synthetic structure of industrial plastics,'' in \emph{Plastics,} 2\textsuperscript{nd} ed., vol. 3, J. Peters, Ed. New York, NY, USA: McGraw-Hill, 1964, pp. 15--64.

\bibitem{b2} W.-K. Chen, \emph{Linear Networks and Systems.} Belmont, CA, USA: Wadsworth, 1993, pp. 123--135.

\bibitem{b3} J. U. Duncombe, ``Infrared navigation---Part I: An assessment of feasibility,'' \emph{IEEE Trans. Electron Devices}, vol. ED-11, no. 1, pp. 34--39, Jan. 1959, 10.1109/TED.2016.2628402.

\bibitem{b4} E. P. Wigner, ``Theory of traveling-wave optical laser,'' \emph{Phys. Rev}., vol. 134, pp. A635--A646, Dec. 1965.

\bibitem{b5} E. H. Miller, ``A note on reflector arrays,'' \emph{IEEE Trans. Antennas Propagat}., to be published.

\bibitem{b6} E. E. Reber, R. L. Michell, and C. J. Carter, ``Oxygen absorption in the earth's atmosphere,'' Aerospace Corp., Los Angeles, CA, USA, Tech. Rep. TR-0200 (4230-46)-3, Nov. 1988.

\bibitem{b7} J. H. Davis and J. R. Cogdell, ``Calibration program for the 16-foot antenna,'' Elect. Eng. Res. Lab., Univ. Texas, Austin, TX, USA, Tech. Memo. NGL-006-69-3, Nov. 15, 1987.

\bibitem{b8} \emph{Transmission Systems for Communications}, 3\textsuperscript{rd} ed., Western Electric Co., Winston-Salem, NC, USA, 1985, pp. 44--60.

\bibitem{b9} \emph{Motorola Semiconductor Data Manual}, Motorola Semiconductor Products Inc., Phoenix, AZ, USA, 1989.

\bibitem{b10} G. O. Young, ``Synthetic structure of industrial
plastics,'' in Plastics, vol. 3, Polymers of Hexadromicon, J. Peters,
Ed., 2\textsuperscript{nd} ed. New York, NY, USA: McGraw-Hill, 1964, pp. 15-64.
[Online]. Available:
\underline{http://www.bookref.com}.

\bibitem{b11} \emph{The Founders' Constitution}, Philip B. Kurland
and Ralph Lerner, eds., Chicago, IL, USA: Univ. Chicago Press, 1987.
[Online]. Available: \underline{http://press-pubs.uchicago.edu/founders/}

\bibitem{b12} The Terahertz Wave eBook. ZOmega Terahertz Corp., 2014.
[Online]. Available:
\underline{http://dl.z-thz.com/eBook/zomega\_ebook\_pdf\_1206\_sr.pdf}. Accessed on: May 19, 2014.

\bibitem{b13} Philip B. Kurland and Ralph Lerner, eds., \emph{The
Founders' Constitution.} Chicago, IL, USA: Univ. of Chicago Press,
1987, Accessed on: Feb. 28, 2010, [Online] Available:
\underline{http://press-pubs.uchicago.edu/founders/}

\bibitem{b14} J. S. Turner, ``New directions in communications,'' \emph{IEEE J. Sel. Areas Commun}., vol. 13, no. 1, pp. 11-23, Jan. 1995.

\bibitem{b15} W. P. Risk, G. S. Kino, and H. J. Shaw, ``Fiber-optic frequency shifter using a surface acoustic wave incident at an oblique angle,'' \emph{Opt. Lett.}, vol. 11, no. 2, pp. 115--117, Feb. 1986.

\bibitem{b16} P. Kopyt \emph{et al., ``}Electric properties of graphene-based conductive layers from DC up to terahertz range,'' \emph{IEEE THz Sci. Technol.,} to be published. DOI: 10.1109/TTHZ.2016.2544142.

\bibitem{b17} PROCESS Corporation, Boston, MA, USA. Intranets:
Internet technologies deployed behind the firewall for corporate
productivity. Presented at INET96 Annual Meeting. [Online].
Available: \underline{http://home.process.com/Intranets/wp2.htp}

\bibitem{b18} R. J. Hijmans and J. van Etten, ``Raster: Geographic analysis and modeling with raster data,'' R Package Version 2.0-12, Jan. 12, 2012. [Online]. Available: \underline {http://CRAN.R-project.org/package=raster}

\bibitem{b19} Teralyzer. Lytera UG, Kirchhain, Germany [Online].
Available:
\underline{http://www.lytera.de/Terahertz\_THz\_Spectroscopy.php?id=home}, Accessed on: Jun. 5, 2014

\bibitem{b20} U.S. House. 102\textsuperscript{nd} Congress, 1\textsuperscript{st} Session. (1991, Jan. 11). \emph{H. Con. Res. 1, Sense of the Congress on Approval of}  \emph{Military Action}. [Online]. Available: LEXIS Library: GENFED File: BILLS

\bibitem{b21} Musical toothbrush with mirror, by L.M.R. Brooks. (1992, May 19). Patent D 326 189 [Online]. Available: NEXIS Library: LEXPAT File: DES

\bibitem{b22} D. B. Payne and J. R. Stern, ``Wavelength-switched pas- sively coupled single-mode optical network,'' in \emph{Proc. IOOC-ECOC,} Boston, MA, USA, 1985, pp. 585--590.

\bibitem{b23} D. Ebehard and E. Voges, ``Digital single sideband detection for interferometric sensors,'' presented at the \emph{2\textsuperscript{nd} Int. Conf. Optical Fiber Sensors,} Stuttgart, Germany, Jan. 2-5, 1984.

\bibitem{b24} G. Brandli and M. Dick, ``Alternating current fed power supply,'' U.S. Patent 4 084 217, Nov. 4, 1978.

\bibitem{b25} J. O. Williams, ``Narrow-band analyzer,'' Ph.D. dissertation, Dept. Elect. Eng., Harvard Univ., Cambridge, MA, USA, 1993.

\bibitem{b26} N. Kawasaki, ``Parametric study of thermal and chemical nonequilibrium nozzle flow,'' M.S. thesis, Dept. Electron. Eng., Osaka Univ., Osaka, Japan, 1993.

\bibitem{b27} A. Harrison, private communication, May 1995.

\bibitem{b28} B. Smith, ``An approach to graphs of linear forms,'' unpublished.

\bibitem{b29} A. Brahms, ``Representation error for real numbers in binary computer arithmetic,'' IEEE Computer Group Repository, Paper R-67-85.

\bibitem{b30} IEEE Criteria for Class IE Electric Systems, IEEE Standard 308, 1969.

\bibitem{b31} Letter Symbols for Quantities, ANSI Standard Y10.5-1968.

\bibitem{b32} R. Fardel, M. Nagel, F. Nuesch, T. Lippert, and A. Wokaun, ``Fabrication of organic light emitting diode pixels by laser-assisted forward transfer,'' \emph{Appl. Phys. Lett.}, vol. 91, no. 6, Aug. 2007, Art. no. 061103.~

\bibitem{b33} J. Zhang and N. Tansu, ``Optical gain and laser characteristics of InGaN quantum wells on ternary InGaN substrates,'' \emph{IEEE Photon. J.}, vol. 5, no. 2, Apr. 2013, Art. no. 2600111

\bibitem{b34} S. Azodolmolky~\emph{et al.}, Experimental demonstration of an impairment aware network planning and operation tool for transparent/translucent optical networks,''~\emph{J. Lightw. Technol.}, vol. 29, no. 4, pp. 439--448, Sep. 2011.

\end{thebibliography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a1.png}}]{First A. Author} (M'76--SM'81--F'87) and all authors may include 
biographies. Biographies are often not included in conference-related
papers. This author became a Member (M) of IEEE in 1976, a Senior
Member (SM) in 1981, and a Fellow (F) in 1987. The first paragraph may
contain a place and/or date of birth (list place, then date). Next,
the author's educational background is listed. The degrees should be
listed with type of degree in what field, which institution, city,
state, and country, and year the degree was earned. The author's major
field of study should be lower-cased.

The second paragraph uses the pronoun of the person (he or she) and not the 
author's last name. It lists military and work experience, including summer 
and fellowship jobs. Job titles are capitalized. The current job must have a 
location; previous positions may be listed 
without one. Information concerning previous publications may be included. 
Try not to list more than three books or published articles. The format for 
listing publishers of a book within the biography is: title of book 
(publisher name, year) similar to a reference. Current and previous research 
interests end the paragraph. The third paragraph begins with the author's 
title and last name (e.g., Dr.\ Smith, Prof.\ Jones, Mr.\ Kajor, Ms.\ Hunter). 
List any memberships in professional societies other than the IEEE. Finally, 
list any awards and work for IEEE committees and publications. If a 
photograph is provided, it should be of good quality, and 
professional-looking. Following are two examples of an author's biography.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a2.png}}]{Second B. Author} was born in Greenwich Village, New York, NY, USA in 
1977. He received the B.S. and M.S. degrees in aerospace engineering from 
the University of Virginia, Charlottesville, in 2001 and the Ph.D. degree in 
mechanical engineering from Drexel University, Philadelphia, PA, in 2008.

From 2001 to 2004, he was a Research Assistant with the Princeton Plasma 
Physics Laboratory. Since 2009, he has been an Assistant Professor with the 
Mechanical Engineering Department, Texas A{\&}M University, College Station. 
He is the author of three books, more than 150 articles, and more than 70 
inventions. His research interests include high-pressure and high-density 
nonthermal plasma discharge processes and applications, microscale plasma 
discharges, discharges in liquids, spectroscopic diagnostics, plasma 
propulsion, and innovation plasma applications. He is an Associate Editor of 
the journal \emph{Earth, Moon, Planets}, and holds two patents.

Dr. Author was a recipient of the International Association of Geomagnetism 
and Aeronomy Young Scientist Award for Excellence in 2008, and the IEEE 
Electromagnetic Compatibility Society Best Symposium Paper Award in 2011. 
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a3.png}}]{Third C. Author, Jr.} (M'87) received the B.S. degree in mechanical 
engineering from National Chung Cheng University, Chiayi, Taiwan, in 2004 
and the M.S. degree in mechanical engineering from National Tsing Hua 
University, Hsinchu, Taiwan, in 2006. He is currently pursuing the Ph.D. 
degree in mechanical engineering at Texas A{\&}M University, College 
Station, TX, USA.

From 2008 to 2009, he was a Research Assistant with the Institute of 
Physics, Academia Sinica, Tapei, Taiwan. His research interest includes the 
development of surface processing and biological/medical treatment 
techniques using nonthermal atmospheric pressure plasmas, fundamental study 
of plasma sources, and fabrication of micro- or nanostructured surfaces.

Mr. Author's awards and honors include the Frew Fellowship (Australian 
Academy of Science), the I. I. Rabi Prize (APS), the European Frequency and 
Time Forum Award, the Carl Zeiss Research Award, the William F. Meggers 
Award and the Adolph Lomb Medal (OSA).
\end{IEEEbiography}

\EOD

\end{document}

### 2022-12-11 paper/new/CW01.tex
First Commit

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{mathtools}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{microtype}
\usepackage{float}
\usepackage{adjustbox}
\usepackage{booktabs,makecell,tabularx}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{verbatim}
\usepackage{xcolor}
\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{epsfig} % for postscript graphics files
\usepackage{mathptmx} % assumes new font selection scheme installed
\usepackage{multicol}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\newcommand\norm[1]{\left\Vert#1\right\Vert}
\begin{document}

\title{List of exercises 01\\
	Fundamentals of optimization}
\author{
	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}}
	\IEEEauthorblockA{\IEEEauthorrefmark{1}augusto.adams@ufpr.br}
}

\maketitle

\begin{abstract}
	This document is submitted as a partial requirement for	evaluation of the discipline of \textit{Evolutionary Computation and Inteligence of Swarms(TE-943)} of the Electrical Engineering Course, with emphasis in Embedded Systems, of the Electrical Engineering Department at the Federal University of Paraná.
\end{abstract}

\begin{IEEEkeywords}Optimization Problem; Linear Programming; Non-linear Programming;\end{IEEEkeywords}

\section{Question 01}

\textbf{\textit{Given the design vector: $\vec{X} = \left\{ \mathbf{x}_{1}, \mathbf{x}_{2}, \mathbf{x}_{3}, \hdots \mathbf{x}_{n}\right\}^T$, match the following terms and descriptions:}}

\begin{multicols}{2}

	$(a)$ Free feasible point

	$(b)$ Free infeasible point

	$(c)$ Bound feasible point

	$(d)$ Bound infeasible point

	$(e)$ Active constraints

	\columnbreak

	$(e)$ $g_j(\vec{X}) = 0$

	$(c)$ Some $g_j(\vec{X}) = 0$ and other $g_j(\vec{X}) < 0$

	$(d)$ Some $g_j(\vec{X}) = 0$ and other $g_j(\vec{X}) \geq 0$

	$(b)$ Some $g_j(\vec{X})>0$ and other $g_j(\vec{X}) < 0$

	$(a)$ All $g_j(\vec{X}) < 0$
\end{multicols}

From the book \textit{``Engineering Optimization - Theory and Practice''} (Rao, 2019):

\begin{quotation}
	Consider an optimization problem with only inequality constraints $g_j (\vec{\mathbf{X}}) \leq 0$. The set of values of $\vec{\mathbf{X}}$ that satisfy the equation $g_j(\vec{\mathbf{X}}) = 0$ forms a hypersurface in the design space and is called a constraint surface. Note that this is an $\left(n - 1\right)$-dimensional subspace, where $n$ is the number of design variables. The constraint surface divides the design space into two regions: one in which $g_j (\vec{\mathbf{X}}) \le 0$ and the other in which $g_j (\vec{\mathbf{X}}) > 0$. Thus, the points lying on the hypersurface will satisfy the constraint $g_j (\vec{\mathbf{X}})$ critically, whereas the points lying in the region where $g_j (\vec{\mathbf{X}}) > 0$ are infeasible or unacceptable, and the points lying in the region where $g_j (\vec{\mathbf{X}}) < 0$ are feasible or acceptable. The collection of all the constraint surfaces $g_j (\vec{\mathbf{X}}) = 0, j = 1, 2, . . . ,m$ which separates the acceptable region is called the \textit{composite constraint surface}.

	A design point that lies on one or more than one constraint surface is called a \textit{bound point}, and the associated constraint is called an\textit{ active constraint}. Design points that do not lie on any constraint surface are known as \textit{free points}. Depending on whether a particular design point belongs to the \textit{acceptable} or \textit{unacceptable} region, it can be identified as one of the following four types:

	\begin{enumerate}
		\item \textit{Free and acceptable point}
		\item \textit{Free and unacceptable point}
		\item \textit{Bound and acceptable point}
		\item \textit{Bound and unacceptable point}
	\end{enumerate}

\end{quotation}

\section{Question 02}
\textit{\textbf{How do you solve a maximization problem as a minimization problem?}}

\textit{Answer:} The point $\hat{\mathbf{x}}$ that maximizes $f(\mathbf{x})$ minimizes $-f(\mathbf{x})$, thus to solve a maximization problem as a minimization problem is to solve for the negative objective function.

From the book \textit{``Engineering Optimization - Theory and Practice''}  (Rao, 2019):

\begin{quotation}
	It can be seen from \textit{Figure 1.1} that if a point $\hat{\mathbf{x}}$ corresponds to the minimum value of function $f (\mathbf{x})$, the same point also corresponds to the maximum value of the negative of the function, $-f (\mathbf{x})$. Thus, without loss of generality, optimization can be taken to mean minimization, since the maximum of a function can be found by seeking the minimum of the negative of the same function.
\end{quotation}

From the Book \textit{``Practical Mathematical Optimization''} (Synman and Wilke, 2018):

\begin{quotation}
	The maximization problem: $max\{f(\mathbf{x})\}$ can be cast in the standard form by observing that $max\{f(\mathbf{x})\}$ = $-min\{-f(\mathbf{x})\}$. Therefore in applying a minimization algorithm set $F(\mathbf{x}) = -f (\mathbf{x})$. Also if the inequality constraints are given in the non-standard form:	$g_j (\mathbf{x}) \geq 0$, then set $\hat{g}_j (\mathbf{x}) = -g_j (\mathbf{x})$. In standard form the problem then becomes:
	\begin{center}
		minimize $F(\mathbf{x})$ such that $\hat{g}_j (\mathbf{x}) \leq 0$.
	\end{center}

	Once the minimizer $\hat{\mathbf{x}}$ is obtained, the maximum value of the original maximization problem is given by $-F(\hat{\mathbf{x}})$.
\end{quotation}

\section{Question 03}

\textbf{\textit{What is the difference between linear and nonlinear	programming problems?}}

\textit{Answer:} The major difference between linear and nonlinear programming problems is the function type of objective function and constraints. In the \textit{Linear Programming Problem} (\textbf{\textit{LP}}), both objective function and constraints are linear, that is, the objective function and constraints are of zero or first order. In the case of \textit{Nonlinear Programming Problem} (\textbf{\textit{NLP}}), any of objective function or constraints are nonlinear functions, that is, are of second or higher order or have exotic functions (trigonometrical functions, exponential functions, etc).

From the book \textit{``Engineering Optimization - Theory and Practice''}  (Rao, 2019):

\begin{quotation}
	\textbf{\textit{Linear Programming Problem}} If the objective function and all the constraints are linear functions of the design variables, the mathematical programming problem is called a \textit{Linear Programming Problem} (\textbf{\textit{LP}}).

	\textbf{\textit{Nonlinear Programming Problem}} If any of the functions among the objective and
	constraint functions in Eq. (1.1) is nonlinear, the problem is called an \textit{NLP problem}.
	This is the most general programming problem and all other problems can be considered as special cases of the \textit{NLP problem}.

\end{quotation}

\section{Question 04}

\textbf{\textit{What is the difference between design variables and	preassigned parameters?}}

\textit{Answer:}

\begin{itemize}
	\item \textit{\textbf{Preassigned parameters:}} fixed values or quantities of the problem;
	\item \textit{\textbf{Design Variables:}} other values or quantities of the problem, usually called \textit{design} or \textit{decision} variables. As the names says, obviously they can vary to accomodate the optimal result for the problem.
\end{itemize}

From the book \textit{``Engineering Optimization - Theory and Practice''}  (Rao, 2019):
\begin{quotation}
Any engineering system or component is defined by a set of quantities, some of which are viewed as variables during the design process. In general, certain quantities are usually fixed at the outset and these are called preassigned parameters. All the other quantities are treated as variables in the design process and are called design or decision variables $\mathbf{x}_i$ , $i = 1, 2, \hdots , n$. The design variables are collectively represented as a design vector $\vec{X} = \left\{ \mathbf{x}_{1} , \mathbf{x}_{2} , \hdots , \mathbf{x}_{n} \right\}^{T}$. As an example, consider the design of the gear pair, characterized by its face width $b$, number of teeth $T_1$ and $T_2$ , center distance $d$, pressure angle $\phi$, tooth profile, and material. If center distance $d$, pressure angle $\phi$, tooth profile, and material of the gears are fixed in advance, these quantities can be called preassigned parameters. The remaining quantities can be collectively represented by a design vector $X = \left\{ \mathbf{x}_1 , \mathbf{x}_2 , \mathbf{x}_3 \right\}^{T} = \left\{ b, T_1 , T_2 \right\}^{T}$ . If there are no restrictions on the choice of $b$, $T_1$ , and $T_2$ , any set of three numbers will constitute a design for the gear pair. If an $n$-dimensional Cartesian space with each coordinate axis representing a design variable $\mathbf{x}_i$ $(i = 1, 2, \hdots , n)$ is considered, the space is called the design variable space or simply design space. Each point in the $n$-dimensional design space is called a design point and represents either a possible or an impossible solution to the design problem.

\end{quotation}

\section{Question 05}

\textbf{\textit{What is the difference between a bound point and a free point in the design space?}}

\textit{Answer:} a bounding point is a design point that lies on one or more constraints, a free point is a design point that does not lie on any constraint.

From the book \textit{``Engineering Optimization - Theory and Practice''} (Rao, 2019):

\begin{quotation}

	A design point that lies on one or more than one constraint surface is called a \textit{bound point}, and the associated constraint is called an\textit{ active constraint}. Design points that do not lie on any constraint surface are known as \textit{free points}.

\end{quotation}

\section{Question 06}

\textbf{\textit{What are the differences between zero, first and second order optimization methods?}}

\textit{Answer:} the terms zero, first and second order refers to the nth-derivative used by the method.

\begin{itemize}
	\item \textbf{\textit{Zero order methods:}} employs the objective function $f$ directly. Examples of zero order methods are Nelder-Mead simplex (direct search),  Powell conjugate directions and Optimization metaheuristics;
	\subitem From the Book \textit{``Practical Mathematical Optimization''} (Synman and Wilke, 2018):
		\begin{quotation}
			These methods are called such because they neither use first order nor second order derivative information, but only function values, i.e. only zero order derivative information.

			Zero order methods are of the earliest methods and many of them	are based on rough and ready ideas with few theoretical background.	Although these ad hoc methods are, as one may expect, much slower and computationally much more expensive than the higher order methods, they are usually reliable and easy to program. One of the most
			successful of these methods is the \textit{downhill simplex method} of Nelder and Mead (1965), also known as Nelder-Mead.

		\end{quotation}

	\item \textbf{\textit{First order methods:}} employs at least the first derivative $f$ (first order information). It approximates $f$ as a plane. Examples of first order methods are Steepest descent methods, Nonlinear conjugate gradients methods and Broyden-Fletcher-Goldfarb-Shanno algorithms (BFGS).

	\subitem From the Book \textit{``Practical Mathematical Optimization''} (Synman and Wilke, 2018):
		\begin{quotation}
			Line search descent methods (see Section 2.1.1), that use the gradient vector $\nabla f(\mathbf{x})$  to determine the search direction for each iteration, are called first order methods because they employ first order partial derivatives of $f(\mathbf{x})$ to compute the search direction at the current iterate. The simplest and most famous of these methods is the method of steepest	descent, first proposed by Cauchy in 1847.
		\end{quotation}

	\item \textbf{\textit{Second order methods:}} employs at least the second derivative of $f$ (second order information). It approximates $f$ as a quadratic form. Examples of second order method are Newton’s method, Newton conjugate gradient and Quasi-Newton method.
		\subitem From the Book \textit{``Practical Mathematical Optimization''} (Synman and Wilke, 2018):

		\begin{quotation}
			These methods are based on Newton’s method (see Section 1.5.4.1) for solving $\nabla f (\mathbf{x}) = 0$ iteratively: Given $\mathbf{x}_0$ , then $\mathbf{x}_i = \mathbf{x}_{i-1} - H^{-1} (\mathbf{x}_{i-1})\nabla f (\mathbf{x}_{i-1} )$, $i = 1, 2, \hdots $
			The main characteristics of this method are:

			\begin{itemize}
				\item In the neighbourhood of the solution it may converge very fast. In fact, it has the very desirous property of being quadratically	convergent if it converges. Unfortunately convergence is not guaranteed and it may sometimes diverge, even from close to the solution.
				\item The implementation of the method requires that $H(\mathbf{x})$  be evaluated at each step.
				\item To obtain the Newton step, $\Delta = \mathbf{x}_i - \mathbf{x}_{i-1}$ it is also necessary to solve a $n \times n$ linear system $H(\mathbf{x})\Delta = -\nabla f (\mathbf{x})$ at each iteration. This is computationally very expensive for large $n$, since an order $n^3$ multiplication operations are required to solve the system numerically.
			\end{itemize}

		\end{quotation}
		$H(\mathbf{x})$ is the \textit{Hessian} matrix or the second derivative of $f(\mathbf{x})$.
\end{itemize}

\section{Question 07}
\textbf{\textit{Considering an optimization global problem given by $min\{f(\mathbf{x})\}$, define global minimum, strong local minimum, weak local minimum, weak global minimum, strong global minimum, and	saddle points.}}

\begin{itemize}
	\item \textbf{\textit{Global Minimum (Synman and Wilke, 2018):}} $\hat{\mathbf{x}}$ is a \textit{global minimum} over the set $X$ if $f (\mathbf{x}) \geq f(\hat{\mathbf{x}})$ for all $x \in X \subset \mathbb{R} ^ n $.
	\item \textbf{\textit{Strong and Weak Global Minima (Arora, 2016):}} A function $f(\mathbf{x})$ of $n$ variables has a \textit{global (absolute) minimum} at $\hat{\mathbf{x}}$ if 
		\begin{equation}
			f(\mathbf{x}) \geq f(\hat{\mathbf{x}})
			\label{ineq01}
		\end{equation}
	for all $\mathbf{x}$ in the feasible design space $S$. If strict inequality holds for all $\mathbf{x}$ other than $\hat{\mathbf{x}}$ in Inequality \ref{ineq01}, then  $\hat{\mathbf{x}}$ is called a \textit{strong (strict) global minimum}; otherwise it is called a \textit{weak global minimum}.
	\item \textbf{\textit{Strong and Weak Local Minima (Arora, 2016):}} A function $f(\mathbf{x})$ of $n$ variables has a \textit{local (relative) minimum}	at $\hat{\mathbf{x}}$ if Inequality \ref{ineq01} holds for all $\mathbf{x}$ in a small neighborhood $N$ of $\hat{\mathbf{x}}$ in the feasible design space $S$. If strict inequality holds, then $\hat{\mathbf{x}}$ is called a \textit{strong (strict) local minimum}; otherwise it is called a \textit{weak local minimum}.
	\item \textbf{\textit{Saddle Points (Rao, 2019):}} In the case of a function of two variables, $f (x, y)$, the \textit{Hessian} matrix may be neither positive nor negative definite at a point $(\hat{x}, \hat{y})$ at which
	\begin{equation}
		\frac{\partial f}{\partial x} = \frac{\partial f}{\partial y} = 0
		\label{saddlecond}
	\end{equation}
	In such a case, the point $(\hat{x}, \hat{y})$ is called a \textit{saddle point}. The characteristic of a saddle
	point is that it corresponds to a relative minimum or maximum of $f(x, y)$ with respect to one variable, say, $x$ (the other variable being fixed at $y = \hat{y}$) and a relative maximum or minimum of $f(x, y)$ with respect to the second variable $y$ (the other variable being	fixed at $x = \hat{x}$).
\end{itemize}

\section{Question 08}
\textbf{\textit{Considering a constrained optimization problem, define Lagrange multiplier and Karush-Kuhn-Tucker (KKT) conditions.}}

\begin{itemize}
	\item \textbf{\textit{Lagrange Multiplier (Figments of my deranged mind about my Calculus Course, 2017 - Prof. Viviana Cocco Mariani; Rao, 2019; Synman and Wilke, 2018; Arora, 2016):}} An optimization problem is given in the form:

	\begin{equation}
		\begin{split}
		\text{minimize}\ f(\hat{\mathbf{x}})\\
		\text{such that}\ g(\hat{\mathbf{x}}) = 0
		\end{split}
		\label{optimizationproblem01}
	\end{equation}

	It is possible to write the problem as:
	\begin{equation}
		\mathcal{L}(\hat{\mathbf{x}},\hat{\lambda}) = f(\hat{\mathbf{x}}) - \hat{\lambda}^T g(\hat{\mathbf{x}})
	\end{equation}

	Where $\mathcal{L}(\hat{\mathbf{x}},\hat{\lambda})$ is called the \textit{Lagrangian Function}, a linear combination of  $f(\hat{\mathbf{x}})$ and $g(\hat{\mathbf{x}})$. The $\hat{\lambda}$ factor is called the \textit{Lagrange Multiplier}. If there is a $\hat{\mathbf{x}}$ which is the optimization problem solution, then there exists a unique Lagrange multiplier $\hat{\lambda}$ such that $\nabla f(\hat{\mathbf{x}}) = \hat{\lambda}^{T}\nabla g(\hat{\mathbf{x}})$.
	\\
	The condition $\nabla f(\hat{\mathbf{x}}) = \hat{\lambda}^{T}\nabla g(\hat{\mathbf{x}})$ implies that any direction perpendicular to all gradients of the constraints is also perpendicular to the gradient of the function. In other words, the directional derivative of the function is 0 in every feasible direction.

	\item \textit{\textbf{Karush-Kuhn-Tucker conditions (Synman and Wilke, 2018): }} considering the optimization problem  in the form:
	 	\begin{equation}
	 	\begin{split}
	 		\text{minimize}\ f(\hat{\mathbf{x}})\\
	 		\text{such that}\ g_j(\hat{\mathbf{x}}) \leq 0, \ j = 1, 2, \hdots , m
	 	\end{split}
	 	\label{optimizationproblem02}
	 \end{equation}

 	and the Lagrangian function defined as:

 	\begin{equation}
 		\mathcal{L}(\hat{\mathbf{x}},\hat{\lambda}) = f(\hat{\mathbf{x}}) - \sum_{j=1}^{m} \hat{\lambda}_j g_j(\hat{\mathbf{x}})
 	\end{equation}

	  and assuming the existence of Lagrange multiplier $\hat{\lambda}$ , then at the point $\hat{x}$ , corresponding to the solution of the optimization problem, the following conditions must be satisfied:

	\begin{equation}
		\begin{split}
			\frac{\partial f}{\partial x_i} (\hat{\mathbf{x}}) - \sum_{j=1}^{m} \hat{\lambda}_j \frac{\partial g_j}{\partial x_i} (\hat{\mathbf{x}}) = 0 \ i = 1, 2, \hdots, n\\
			g_j(\hat{\mathbf{x}}) \leq 0, \  i = 1, 2, \hdots, m\\
			\hat{\lambda}_j g_j(\hat{\mathbf{x}}) = 0, \  i = 1, 2, \hdots, m\\
			\hat{\lambda}_j \geq 0, \  i = 1, 2, \hdots, m
		\end{split}
	\end{equation}
	Which are the \textit{Karush-Kuhn-Tucker conditions}. It can be shown, that the KKT conditions also constitute sufficient conditions (those that imply that) for $\hat{x}$ to be a constrained minimum, if $f(\mathbf{x})$ and the $g_j(\mathbf{x})$	are all convex functions.
\end{itemize}

\end{document}

### 2022-12-11 Solvers/Ackley.py

@@ -1,0 +1,42 @@
+"""
+Computational Work 01 - Fundamentals of optimization
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+ackley function and its derivatives
+"""
+
+from sympy import var, exp, cos, pi, euler, sqrt
+from .common import *
+
+
+def get_ackley_defs():
+
+    x, y = var("x y")
+
+    X = [x, y]
+
+    function = - 20 * exp(-0.2 * sqrt(0.5 * (x ** 2 + y ** 2))) \
+               - exp(0.5 * (cos(2 * pi * x) + cos(2 * pi * y))) \
+               + exp(1) + 20
+
+    function_function = get_lambdified_function(X, function)
+
+    gradient = get_gradient_vector(X, function)
+
+    gradient_function = get_lambdified_gradient_vector(X, function)
+
+    hessian = get_hessian_matrix(X, function)
+
+    hessian_function = get_lambdified_hessian_matrix(X, function)
+
+    return {"function": function,
+            "gradient": gradient,
+            "hessian": hessian,
+            "function_function": function_function,
+            "gradient_function": gradient_function,
+            "hessian_function": hessian_function,
+            "diff_vars": X,
+            "dimension": len(X)}

### 2022-12-11 Solvers/Beale.py

@@ -1,0 +1,40 @@
+"""
+Computational Work 01 - Fundamentals of optimization
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis  eduardo.reis02@gmail.com - GRR20175957
+
+beale function and its derivatives
+"""
+
+from sympy import var
+from .common import *
+
+
+def get_beale_defs():
+
+    x, y = var("x y")
+
+    X = [x, y]
+
+    function = (1.5 - x + x * y) ** 2 + (2.25 - x + x * (y ** 2)) ** 2 + (2.625 - x + x * (y ** 3)) ** 2
+
+    function_function = get_lambdified_function(X, function)
+
+    gradient = get_gradient_vector(X, function)
+
+    gradient_function = get_lambdified_gradient_vector(X, function)
+
+    hessian = get_hessian_matrix(X, function)
+
+    hessian_function = get_lambdified_hessian_matrix(X, function)
+
+    return {"function": function,
+            "gradient": gradient,
+            "hessian": hessian,
+            "function_function": function_function,
+            "gradient_function": gradient_function,
+            "hessian_function": hessian_function,
+            "diff_vars": X,
+            "dimension": len(X)}

### 2022-12-11 Solvers/Booth.py

@@ -1,0 +1,40 @@
+"""
+Computational Work 01 - Fundamentals of optimization
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+booth function and its derivatives
+"""
+
+from sympy import var
+from .common import *
+
+
+def get_booth_defs():
+
+    x, y = var("x y")
+
+    X = [x, y]
+
+    function = (x + 2 * y - 7) ** 2 + (2 * x + y - 5) ** 2
+
+    function_function = get_lambdified_function(X, function)
+
+    gradient = get_gradient_vector(X, function)
+
+    gradient_function = get_lambdified_gradient_vector(X, function)
+
+    hessian = get_hessian_matrix(X, function)
+
+    hessian_function = get_lambdified_hessian_matrix(X, function)
+
+    return {"function": function,
+            "gradient": gradient,
+            "hessian": hessian,
+            "function_function": function_function,
+            "gradient_function": gradient_function,
+            "hessian_function": hessian_function,
+            "diff_vars": X,
+            "dimension": len(X)}

### 2022-12-11 Solvers/Matyas.py

@@ -1,0 +1,40 @@
+"""
+Computational Work 01 - Fundamentals of optimization
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis  eduardo.reis02@gmail.com - GRR20175957
+
+matyas function and its derivatives
+"""
+
+from sympy import var
+from .common import *
+
+
+def get_matyas_defs():
+
+    x, y = var("x y")
+
+    X = [x, y]
+
+    function = 0.26 * (x ** 2 + y ** 2) - 0.48 * x * y
+
+    function_function = get_lambdified_function(X, function)
+
+    gradient = get_gradient_vector(X, function)
+
+    gradient_function = get_lambdified_gradient_vector(X, function)
+
+    hessian = get_hessian_matrix(X, function)
+
+    hessian_function = get_lambdified_hessian_matrix(X, function)
+
+    return {"function": function,
+            "gradient": gradient,
+            "hessian": hessian,
+            "function_function": function_function,
+            "gradient_function": gradient_function,
+            "hessian_function": hessian_function,
+            "diff_vars": X,
+            "dimension": len(X)}

### 2022-12-11 Solvers/Rastrigin2D.py

@@ -1,0 +1,42 @@
+"""
+Computational Work 01 - Fundamentals of optimization
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+Rastrigin 2D function and its derivatives
+"""
+
+from sympy import var, cos, sin, pi
+from .common import *
+
+
+def get_rastrigin2D_defs():
+
+    A = 10
+
+    x1, x2 = var("x1 x2")
+
+    X = [x1, x2]
+
+    function = 2 * A + x1 ** 2 + x2 ** 2 - A * (cos (2 * pi * x1) + cos(2 * pi * x2))
+
+    function_function = get_lambdified_function(X, function)
+
+    gradient = get_gradient_vector(X, function)
+
+    gradient_function = get_lambdified_gradient_vector(X, function)
+
+    hessian = get_hessian_matrix(X, function)
+
+    hessian_function = get_lambdified_hessian_matrix(X, function)
+
+    return {"function": function,
+            "gradient": gradient,
+            "hessian": hessian,
+            "function_function": function_function,
+            "gradient_function": gradient_function,
+            "hessian_function": hessian_function,
+            "diff_vars": X,
+            "dimension": len(X)}

### 2022-12-11 Solvers/Rastrigin30D.py

@@ -1,0 +1,88 @@
+"""
+Computational Work 01 - Fundamentals of optimization
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+Rastrigin 2D function and its derivatives
+"""
+
+from sympy import var, cos, sin, pi
+from .common import *
+
+
+def __get_rastrigin_function():
+    A = 10
+
+    (x1,
+     x2,
+     x3,
+     x4,
+     x5,
+     x6,
+     x7,
+     x8,
+     x9,
+     x10,
+     x11,
+     x12,
+     x13,
+     x14,
+     x15,
+     x16,
+     x17,
+     x18,
+     x19,
+     x20,
+     x21,
+     x22,
+     x23,
+     x24,
+     x25,
+     x26,
+     x27,
+     x28,
+     x29,
+     x30) = var(
+        "x1 x2 x3 x4 x5 x6 x7 x8 x9 x10 x11 x12 x13 x14 x15 x16 x17 x18 x19 x20 x21 x22 x23 x24 x25 x26 x27 x28 x29 x30")
+
+    x = [x1, x2, x3, x4, x5,
+         x6, x7, x8, x9, x10,
+         x11, x12, x13, x14,
+         x15, x16, x17, x18,
+         x19, x20, x21, x22,
+         x23, x24, x25, x26,
+         x27, x28, x29, x30]
+
+    function = 30 * A
+
+    for i in range(0, len(x)):
+        function += (x[i] ** 2 - A * cos(2 * pi * x[i]))
+
+    return x, function
+
+
+def get_rastrigin30D_defs():
+    
+    X, function = __get_rastrigin_function()
+
+    function_function = get_lambdified_function(X, function)
+
+    gradient = get_gradient_vector(X, function)
+
+    gradient_function = get_lambdified_gradient_vector(X, function)
+
+    hessian = get_hessian_matrix(X, function)
+
+    hessian_function = get_lambdified_hessian_matrix(X, function)
+
+    return {"function": function,
+            "gradient": gradient,
+            "hessian": hessian,
+            "function_function": function_function,
+            "gradient_function": gradient_function,
[…]

### 2022-12-11 Solvers/Rastrigin4D.py

@@ -1,0 +1,48 @@
+"""
+Computational Work 01 - Fundamentals of optimization
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+Rastrigin 4D function and its derivatives
+"""
+
+from sympy import var, cos, sin, pi
+from .common import *
+
+
+def get_rastrigin4D_defs():
+    A = 10
+
+    x1, x2, x3, x4 = var("x1 x2 x3 x4")
+
+    X = [x1, x2, x3, x4]
+
+    function = 4 * A + (x1 ** 2 +
+                        x2 ** 2 +
+                        x3 ** 2 +
+                        x4 ** 2) -\
+               A * (cos(2 * pi * x1) +
+                    cos(2 * pi * x2) +
+                    cos(2 * pi * x3) +
+                    cos(2 * pi * x4))
+
+    function_function = get_lambdified_function(X, function)
+
+    gradient = get_gradient_vector(X, function)
+
+    gradient_function = get_lambdified_gradient_vector(X, function)
+
+    hessian = get_hessian_matrix(X, function)
+
+    hessian_function = get_lambdified_hessian_matrix(X, function)
+
+    return {"function": function,
+            "gradient": gradient,
+            "hessian": hessian,
+            "function_function": function_function,
+            "gradient_function": gradient_function,
+            "hessian_function": hessian_function,
+            "diff_vars": X,
+            "dimension": len(X)}

### 2022-12-11 Solvers/Rosenbrock2D.py

@@ -1,0 +1,40 @@
+"""
+Computational Work 01 - Fundamentals of optimization
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+Rosenbrock 2D function and its derivatives
+"""
+
+from sympy import var
+from .common import *
+
+
+def get_rosenbrock2D_defs():
+
+    x1, x2 = var("x1 x2")
+
+    X = [x1, x2]
+
+    function = 100 * ((x2 - x1 ** 2) ** 2) + ((x1 - 1) ** 2)
+
+    function_function = get_lambdified_function(X, function)
+
+    gradient = get_gradient_vector(X, function)
+
+    gradient_function = get_lambdified_gradient_vector(X, function)
+
+    hessian = get_hessian_matrix(X, function)
+
+    hessian_function = get_lambdified_hessian_matrix(X, function)
+
+    return {"function": function,
+            "gradient": gradient,
+            "hessian": hessian,
+            "function_function": function_function,
+            "gradient_function": gradient_function,
+            "hessian_function": hessian_function,
+            "diff_vars": X,
+            "dimension": len(X)}

### 2022-12-11 Solvers/Rosenbrock30D.py

@@ -1,0 +1,85 @@
+"""
+Computational Work 01 - Fundamentals of optimization
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+Rosenbrock 30D function and its derivatives
+"""
+
+from sympy import var
+from .common import *
+
+
+def __get_rosenbrock_function():
+    (x1,
+    x2,
+    x3,
+    x4,
+    x5,
+    x6,
+    x7,
+    x8,
+    x9,
+    x10,
+    x11,
+    x12,
+    x13,
+    x14,
+    x15,
+    x16,
+    x17,
+    x18,
+    x19,
+    x20,
+    x21,
+    x22,
+    x23,
+    x24,
+    x25,
+    x26,
+    x27,
+    x28,
+    x29,
+    x30) = var("x1 x2 x3 x4 x5 x6 x7 x8 x9 x10 x11 x12 x13 x14 x15 x16 x17 x18 x19 x20 x21 x22 x23 x24 x25 x26 x27 x28 x29 x30")
+
+    x = [x1, x2, x3, x4, x5,
+         x6, x7, x8, x9, x10,
+         x11, x12, x13, x14,
+         x15, x16, x17, x18,
+         x19, x20, x21, x22,
+         x23, x24, x25, x26,
+         x27, x28, x29, x30]
+
+    function = 100 * ((x[1] - x[0] ** 2) ** 2) + (x[0] - 1) ** 2
+
+    for i in range(1, len(x)-1):
+
+         function += 100 * ((x[i+1] - x[i] ** 2) ** 2) + (x[i] - 1) ** 2
+
+    return x, function
+
+
+def get_rosenbrock30D_defs():
+
+    X, function = __get_rosenbrock_function()
+
+    function_function = get_lambdified_function(X, function)
+
+    gradient = get_gradient_vector(X, function)
+
+    gradient_function = get_lambdified_gradient_vector(X, function)
+
+    hessian = get_hessian_matrix(X, function)
+
+    hessian_function = get_lambdified_hessian_matrix(X, function)
+
+    return {"function": function,
+            "gradient": gradient,
+            "hessian": hessian,
+            "function_function": function_function,
[…]

### 2022-12-11 Solvers/Rosenbrock4D.py

@@ -1,0 +1,45 @@
+"""
+Computational Work 01 - Fundamentals of optimization
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+Rosenbrock 4D function and its derivatives
+"""
+
+from sympy import var
+from .common import *
+
+
+def get_rosenbrock4D_defs():
+
+    x1, x2, x3, x4 = var("x1 x2 x3 x4")
+
+    X = [x1, x2, x3, x4]
+
+    function = 100 * ((x2 - x1 ** 2) ** 2 +
+                      (x3 - x2 ** 2) ** 2 +
+                      (x4 - x3 ** 2) ** 2) +\
+               ((x1 - 1) ** 2 +
+                (x2 - 1) ** 2 +
+                (x3 - 1) ** 2)
+
+    function_function = get_lambdified_function(X, function)
+
+    gradient = get_gradient_vector(X, function)
+
+    gradient_function = get_lambdified_gradient_vector(X, function)
+
+    hessian = get_hessian_matrix(X, function)
+
+    hessian_function = get_lambdified_hessian_matrix(X, function)
+
+    return {"function": function,
+            "gradient": gradient,
+            "hessian": hessian,
+            "function_function": function_function,
+            "gradient_function": gradient_function,
+            "hessian_function": hessian_function,
+            "diff_vars": X,
+            "dimension": len(X)}

### 2022-12-11 Solvers/Solvers/BFGS.py

@@ -1,0 +1,36 @@
+"""
+Computational Work 01 - Fundamentals of optimization
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+BGFS algorithm
+"""
+import numpy as np
+from ..common import *
+from scipy.optimize import minimize
+
+
+def bfgs(of, jac, jac2, x0):
+    """
+    Minimizes a funtion using Quasi-Newton BFGS method
+    :param f: the function to be minimized
+    :param jac: the analytical jacobian (gradient) function
+    :param x0: the initial guess
+    :return: optimization results
+    """
+    objective = lambda x: of(*x.flatten())
+
+    derivative = lambda x: jac(*x.flatten())
+
+    hessian = lambda x: jac2(*x.flatten())
+
+    result = minimize(objective,
+                      x0,
+                      method='BFGS',
+                      jac=derivative,
+                      tol=1e-9,
+                      options={'return_all': True})
+
+    return result

### 2022-12-11 Solvers/Solvers/DFP.py

@@ -1,0 +1,40 @@
+"""
+Computational Work 01 - Fundamentals of optimization
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+DFP algorithm
+The minimizer is adapted from the original SciPy BFGS implementation, since DFP
+is it's dual algorithm
+"""
+
+import numpy as np
+from scipy.optimize import minimize
+from ..common import *
+from .custom_minimizers import fmin_dfp, _minimize_dfp
+
+
+def dfp(of, jac, jac2, x0):
+    """
+    Minimizes a funtion using Quasi-Newton DFP method
+    :param f: the function to be minimized
+    :param jac: the analytical jacobian (gradient) function
+    :param x0: the initial guess
+    :return: optimization results
+    """
+    objective = lambda x: of(*x.flatten())
+
+    derivative = lambda x: jac(*x.flatten())
+
+    hessian = lambda x: jac2(*x.flatten())
+
+    result = minimize(objective,
+                      x0,
+                      method=_minimize_dfp,
+                      jac=derivative,
+                      hess=hessian,
+                      tol=1e-9,
+                      options={'return_all': True})
+    return result

### 2022-12-11 Solvers/Solvers/LBFGS.py

@@ -1,0 +1,37 @@
+"""
+Computational Work 01 - Fundamentals of optimization
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+BGFS algorithm
+"""
+import numpy as np
+from ..common import *
+from scipy.optimize import minimize
+from .custom_minimizers import _minimize_lbfgs
+
+
+def lbfgs(of, jac, jac2, x0):
+    """
+    Minimizes a funtion using Quasi-Newton LBFGS method
+    :param of: the function to be minimized
+    :param jac: the analytical jacobian (gradient) function
+    :param x0: the initial guess
+    :return: optimization results
+    """
+    objective = lambda x: of(*x.flatten())
+
+    derivative = lambda x: jac(*x.flatten())
+
+    hessian = lambda x: jac2(*x.flatten())
+
+    result = minimize(objective,
+                      x0,
+                      method=_minimize_lbfgs,
+                      jac=derivative,
+                      hess=hessian, # only to compute final hessian values - to be compatible with other solvers
+                      tol=1e-9,
+                      options={'return_all': True})
+    return result

### 2022-12-11 Solvers/Solvers/LevenbergMarquardt.py

@@ -1,0 +1,41 @@
+"""
+Computational Work 01 - Fundamentals of optimization
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+LMA algorithm
+The minimizer is adapted from the original SciPy BFGS implementation, since DFP
+is it's dual algorithm
+"""
+
+import numpy as np
+from scipy.optimize import minimize
+from ..common import *
+from .custom_minimizers import _minimize_lma
+
+
+def lma(of, jac, jac2, x0):
+    """
+    Minimizes a funtion using Levenberg-Marquardt Algorithm
+    :param f: the function to be minimized
+    :param jac: the analytical jacobian (gradient) function
+    :param x0: the initial guess
+    :return: optimization results
+    """
+    objective = lambda x: of(*x.flatten())
+
+    derivative = lambda x: jac(*x.flatten())
+
+    hessian = lambda x: jac2(*x.flatten())
+
+    result = minimize(objective,
+                      x0,
+                      jac=derivative,
+                      hess=hessian,
+                      tol=1e-11,
+                      method=_minimize_lma,
+                      options={'return_all': True})
+
+    return result

### 2022-12-11 Solvers/Solvers/__init__.py

@@ -1,0 +1,4 @@
+from .DFP import dfp
+from .BFGS import bfgs
+from .LBFGS import lbfgs
+from .LevenbergMarquardt import lma

### 2022-12-11 Solvers/Solvers/custom_minimizers.py

@@ -1,0 +1,1258 @@
+__docformat__ = "restructuredtext en"
+
+# ******NOTICE***************
+# optimize.py module by Travis E. Oliphant
+#
+# You may copy and use this module as you see fit with no
+# guarantee implied provided you keep this notice in all copies.
+# *****END NOTICE************
+
+# A collection of optimization algorithms. Version 0.5
+# CHANGES
+#  Added fminbound (July 2001)
+#  Added brute (Aug. 2002)
+#  Finished line search satisfying strong Wolfe conditions (Mar. 2004)
+#  Updated strong Wolfe conditions line search to use
+#  cubic-interpolation (Mar. 2004)
+
+import warnings
+import sys
+from numpy import (atleast_1d, eye, argmin, zeros, shape, squeeze,
+                   asarray, sqrt, Inf, asfarray)
+import numpy as np
+from scipy.sparse.linalg import LinearOperator
+from scipy.optimize._linesearch import (line_search_wolfe1,
+                                        line_search_wolfe2,
+                                        line_search_wolfe2 as line_search,
+                                        LineSearchWarning)
+from scipy.optimize._numdiff import approx_derivative
+from scipy._lib._util import MapWrapper, check_random_state
+from scipy.optimize._differentiable_functions import ScalarFunction, FD_METHODS
+
+# standard status messages of optimizers
+_status_message = {'success': 'Optimization terminated successfully.',
+                   'maxfev': 'Maximum number of function evaluations has '
+                             'been exceeded.',
+                   'maxiter': 'Maximum number of iterations has been '
+                              'exceeded.',
+                   'pr_loss': 'Desired error not necessarily achieved due '
+                              'to precision loss.',
+                   'nan': 'NaN result encountered.',
+                   'out_of_bounds': 'The result is outside of the provided '
+                                    'bounds.'}
+
+#: LMA alpha computing parameters
+_BETA = 2.0
+_GAMMA = 3.0
+_P = 3.0
+_TAU = 0.1
+
+
+def _indenter(s, n=0):
+    """
+    Ensures that lines after the first are indented by the specified amount
+    """
+    split = s.split("\n")
+    indent = " " * n
+    return ("\n" + indent).join(split)
+
+
+def _float_formatter_10(x):
+    """
+    Returns a string representation of a float with exactly ten characters
+    """
+    if np.isposinf(x):
+        return "       inf"
+    elif np.isneginf(x):
+        return "      -inf"
+    elif np.isnan(x):
+        return "       nan"
[…]

### 2022-12-11 Solvers/__init__.py

@@ -1,0 +1,79 @@
+from .Solvers import *
+from .Ackley import *
+from .Beale import *
+from .Booth import *
+from .Matyas import *
+from .Rastrigin2D import *
+from .Rastrigin4D import *
+from .Rastrigin30D import *
+from .Rosenbrock2D import *
+from .Rosenbrock4D import *
+from .Rosenbrock30D import *
+from .common import *
+
+constraints = {"ackley": {"def_func": get_ackley_defs,
+                          "search_space": [-32, 32],
+                          "design_space": [-0.05, 0.05],
+                          "minimum": [0, 0],
+                          "isoline_space": [-0.2, 0.2]},
+               "beale": {"def_func": get_beale_defs,
+                         "search_space": [-4.5, 4.5],
+                         "design_space": [-1, 3.5],
+                         "minimum": [3, 0.5],
+                         "isoline_space": [-4.5, 4.5]},
+               "booth": {"def_func": get_booth_defs,
+                         "search_space": [-10, 10],
+                         "design_space": [0, 4],
+                         "minimum": [1, 3],
+                         "isoline_space": [-10, 10]},
+               "matyas": {"def_func": get_matyas_defs,
+                          "search_space": [-10, 10],
+                          "design_space": [-10, 10],
+                          "minimum": [0, 0],
+                          "isoline_space": [-10, 10]},
+               "rastrigin2d": {"def_func": get_rastrigin2D_defs,
+                               "search_space": [-5.12, 5.12],
+                               "design_space": [-0.15, 0.15],
+                               "minimum": [0] * 2,
+                               "isoline_space": [-0.5, 0.5]},
+               "rastrigin4d": {"def_func": get_rastrigin4D_defs,
+                               "search_space": [-5.12, 5.12],
+                               "design_space": [-0.15, 0.15],
+                               "minimum": [0] * 4,
+                               "isoline_space": [-0.5, 0.5]},
+               "rastrigin30d": {"def_func": get_rastrigin30D_defs,
+                                "search_space": [-5.12, 5.12],
+                                "design_space": [-0.15, 0.15],
+                                "minimum": [0] * 30,
+                                "isoline_space": [-0.5, 0.5]},
+               "rosenbrock2d": {"def_func": get_rosenbrock2D_defs,
+                                "search_space": [-10, 10],
+                                "design_space": [-1.5, 1.5],
+                                "minimum": [1] * 2,
[…]

### 2022-12-11 Solvers/common.py

@@ -1,0 +1,139 @@
+"""
+Computational Work 01 - Fundamentals of optimization
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+Common functions used by the whole system
+"""
+
+from sympy import latex, var, diff, simplify, lambdify
+import numpy as np
+import scipy.optimize as optimizer
+
+"""
+Sympy definitions for gradient and hessian functions
+"""
+
+
+def get_gradient_vector(diff_vars, function):
+    """
+    Analytical Gradient Vector
+    :param diff_vars: differentiation vars
+    :param function: differentiable function
+    :return: list the gradient
+    """
+    gradient = list()
+    for i in range(len(diff_vars)):
+        gradient.append(diff(function, diff_vars[i]))
+    return gradient
+
+
+def get_hessian_matrix(diff_vars, function):
+    """
+    Analytical Hessian Matrix
+    :param diff_vars: differentiation vars
+    :param function: differentiable function
+    :return: list the hessian matrix
+    """
+    hessian = list()
+    for i in range(len(diff_vars)):
+        line = list()
+        for j in range(len(diff_vars)):
+            line.append(diff(diff(function, diff_vars[i]), diff_vars[j]))
+        hessian.append(line)
+    return hessian
+
+
+def get_lambdified_function(diff_vars, function):
+    """
+    Transforms the function into python function
+    :param diff_vars: differentiation vars
+    :param function: differentiable function
+    :return: fun the function function
+    """
+    return lambdify(diff_vars, function, "numpy")
+
+
+def get_lambdified_gradient_vector(diff_vars, function):
+    """
+    Transforms the analytical gradient into python function
+    :param diff_vars: differentiation vars
+    :param function: differentiable function
+    :return: fun the gradient function
+    """
+    return lambdify(diff_vars, get_gradient_vector(diff_vars, function), "numpy")
+
+
+def get_lambdified_hessian_matrix(diff_vars, function):
+    """
+    Transforms the analytical hessian matrix into python function
+    :param diff_vars: differentiation vars
+    :param function: differentiable function
+    :return: list the hessian matrix
+    """
[…]

### 2022-12-11 app.py

@@ -1,0 +1,69 @@
+"""
+Computational Work 01 - Fundamentals of optimization
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+app runner
+"""
+
+import jdata as jd
+import json
+import time
+from Solvers import *
+
+N = 100
+
+
+def solve(alg_name, alg_func, function, search_space, defs):
+    print("Solving for {:s} - {:s}".format(alg_name, function))
+
+    results = list()
+    times = list()
+    for seed in range(1, N + 1):
+        start = time.time()
+
+        x0 = generate_random_sequence(seed,
+                                      search_space[0],
+                                      search_space[1],
+                                      defs['dimension'])
+
+        results.append(alg_func(defs['function_function'],
+                                defs['gradient_function'],
+                                defs['hessian_function'],
+                                x0))
+        stop = time.time()
+
+        times.append(stop - start)
+
+    results = {"runs": results,
+               "elapsed_time": times}
+
+    filename = "results/" + alg_name + "_" + function + ".json"
+
+    #: jdata saves very complex data structures directly in json
+    jd.save(results, filename)
+
+    #: some formatting that jdata doesn't handle by itself
+    with open(filename, "r") as f:
+        json_data = json.load(f)
+
+    with open(filename, "w") as f:
+        json.dump(json_data, f, indent=4)
+
+
+for function in constraints:
+
+    def_func = constraints[function]['def_func']
+
+    search_space = constraints[function]['search_space']
+
+    design_space = constraints[function]['design_space']
+
+    defs = def_func()
+
+    for alg_name in algorithms:
+        alg_func = algorithms[alg_name]
+        solve(alg_name + "_search_space", alg_func, function, search_space, defs)
+        solve(alg_name + "_design_space", alg_func, function, design_space, defs)

### 2022-12-11 cleandata.py

@@ -1,0 +1,138 @@
+"""
+Computational Work 01 - Fundamentals of optimization
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+Data Cleanup
+"""
+
+import json
+import numpy as np
+from Solvers import *
+
+
+def args_are_in_range(args, search_space):
+    """
+    Solution verifier
+    :param args: the coordinates
+    :param search_space: the search space
+    :return: the in_range flag
+    """
+    in_search_space = True
+    for arg in args:
+        if arg < search_space[0] or arg > search_space[1]:
+            in_search_space = False
+    return in_search_space
+
+
+def is_in_trust_region(x, minimum):
+    """
+    checks if the solution is in the strusted region for solution
+    :param x: the solution
+    :param minimum: the analytical minimum
+    :return: bool the trust region flag
+    """
+    result = np.array(x) - np.array(minimum)
+    norm = np.linalg.norm(result)
+    return norm < 1e-2
+
+
+for function in constraints:
+
+    def_func = constraints[function]['def_func']
+
+    search_space = constraints[function]['search_space']
+
+    design_space = constraints[function]['design_space']
+
+    minimum = constraints[function]['minimum']
+
+    defs = def_func()
+
+    for alg_name in algorithms:
+
+        #: defining filename
+
+        print("processing {:s} {:s}".format(function, alg_name))
+
+        filenames = [["results/" + alg_name + "_design_space_" + function + ".json", design_space],
+                     ["results/" + alg_name + "_search_space_" + function + ".json", design_space]]
+
+        for filename in filenames:
+
+            with open(filename[0], "r") as f:
+                results = json.load(f)
+
+            alg_data = results["runs"]
+
+            elapsed_times = results["elapsed_time"]
+
+            #: cleaning up file
+
+            clean_data = dict()
+
+            clean_data["hits"] = 0
+
+            clean_data["miss"] = 0
+
+            clean_data["out_of_range"] = 0
+
+            clean_data["data"] = list()
+
+            for i in  range(0, len(elapsed_times)):
+
+                node = alg_data[i]
+
+                new_node = dict()
+
[…]

### 2022-12-11 isolines.py

@@ -1,0 +1,78 @@
+"""
+Computational Work 01 - Fundamentals of optimization
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+Isolines and convergence line of the best fit
+"""
+
+import json
+import numpy as np
+import matplotlib.pyplot as plt
+from Solvers import *
+
+
+filename = "reports/reports.json"
+
+with open(filename, "r") as f:
+    data = json.load(f)
+
+for function in constraints:
+
+    def_func = constraints[function]['def_func']
+
+    search_space = constraints[function]['isoline_space']
+
+    design_space = constraints[function]['design_space']
+
+    minimum = constraints[function]['minimum']
+
+    defs = def_func()
+
+    function_function = defs['function_function']
+
+    if defs['dimension'] == 2:
+
+        print(function)
+
+        x = np.linspace(search_space[0], search_space[1], 500)
+
+        y = np.linspace(search_space[0], search_space[1], 500)
+
+        X, Y = np.meshgrid(x, y)
+
+        Z = function_function(*[X, Y])
+
+        levels = np.linspace(np.min(Z), np.max(Z), 100)
+
+        plt.close('all')
+
+        plt.contour(X, Y, Z, levels=levels, linewidths=[0.3])
+
+        for alg_name in algorithms:
+
+            best_fit = data[function][alg_name]["design_space"]["best_fit"]["best_fit_data"]
+
+            #: x, y
+
+            points = np.array(best_fit["points"])
+
+            x = points[:, 0]
+            y = points[:, 1]
+            z = np.array(best_fit["function_values"])
+
+            plt.plot(x, y, label=alg_name, linewidth=0.6)
+
+        plt.title(function_names[function])
+
+        plt.xlabel("X axis")
+
+        plt.ylabel("Y axis")
+
+        plt.legend()
+
+        plt.grid()
+
+        plt.savefig("images/" + function + ".jpg", dpi=600)

### 2022-12-11 latextablemaker.py

@@ -1,0 +1,78 @@
+"""
+Computational Work 01 - Fundamentals of optimization
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+Reports
+"""
+
+import numpy as np
+import pandas as pd
+import json
+
+from Solvers import *
+
+filename = "reports/reports.json"
+
+with open(filename, "r") as f:
+    data = json.load(f)
+
+for function in constraints:
+
+    print(function)
+
+    def_func = constraints[function]['def_func']
+
+    search_space = constraints[function]['search_space']
+
+    design_space = constraints[function]['design_space']
+
+    minimum = constraints[function]['minimum']
+
+    defs = def_func()
+
+    function_values = []
+
+    best_fits = []
+
+    column_names = ["Algorithm", "Minimal", "Maximum", "Mean", "Median"]
+
+    best_fits_column_names = ["Algorithm", "Solution", "Iterations", "Function Evaluations", "Function Value"]
+
+    for alg_name in algorithms:
+
+        function_values_data = data[function][alg_name]["design_space"]["overall"]["function_values"]
+
+        best_fit_data = data[function][alg_name]["design_space"]["best_fit"]["best_fit_data"]
+
+        function_values.append([alg_name,
+                                function_values_data["fmin"],
+                                function_values_data["fmax"],
+                                function_values_data["favg"],
+                                function_values_data["fmedian"]])
+
+        best_fits.append([alg_name,
+                          ",".join([str(x) for x in best_fit_data["optimal_point"]]),
+                          best_fit_data["iterations"],
+                          best_fit_data["function_evaluations"],
+                          best_fit_data["optimal_function_value"]])
+
+    # function_data = np.array(function_values)
+
+    df = pd.DataFrame(function_values, columns=column_names)
+
+    content = df.to_latex(index=False)
+
+    with open("latex/" + function + "_function_values.tex", "w") as f:
+        f.write(content)
+
+    # best_fit_data = np.array(best_fits)
+
+    df = pd.DataFrame(best_fits, columns=best_fits_column_names)
+
+    content = df.to_latex(index=False)
+
+    with open("latex/" + function + "_best_fits.tex", "w") as f:
+        f.write(content)

### 2022-12-11 reports.py

@@ -1,0 +1,206 @@
+"""
+Computational Work 01 - Fundamentals of optimization
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+Reports
+"""
+
+import numpy as np
+import json
+
+from Solvers import *
+
+
+def min_max_avg_std(data):
+    """
+    Computes min, max, avg and std from results
+    :param data: the results data
+    :return: min, max, avg, std, first_quantile and third_quantile values
+    """
+    fmin = 0
+    fmax = 0
+    favg = 0
+    fmedian = 0
+    fstd = 0
+
+    if len(data) > 0:
+        fmin = float(np.min(data))
+        fmax = float(np.max(data))
+        favg = float(np.mean(data))
+        fmedian = float(np.median(data))
+        fstd = float(np.std(data))
+
+    return {"fmin": fmin,
+            "fmax": fmax,
+            "favg": favg,
+            "fmedian": fmedian,
+            "fstd": fstd}
+
+
+def extract_data(data):
+    """
+    Data extraction
+    :param data: the results data
+    :param convergence: the convergence class (good, poor, divergence)
+    :return: the extracted data
+    """
+    extracted_data = dict()
+    extracted_data["good"] = {"data": [], "elapsed_time": []}
+    extracted_data["poor"] = {"data": [], "elapsed_time": []}
+    extracted_data["divergence"] = {"data": [], "elapsed_time": []}
+    for i in range(0, len(data['runs']['data'])):
+        node = data['runs']['data'][i]
+        extracted_data[node['convergence']]["data"].append(node)
+        extracted_data[node['convergence']]["elapsed_time"].append(data["elapsed_time"][i])
+
+    return extracted_data
+
+
+def extract_parameter(data, parameter):
+    """
+    Extract parameter from data
+    :param data: the result data
+    :param parameter: the parameter
+    :return: the parameter values
+    """
+    parameter_values = list()
+    for i in range(0, len(data)):
+        parameter_values.append(float(data[i][parameter]))
+    return parameter_values
+
+
+def sortFunc(e):
+    return e[1]
+
+
[…]

### 2022-12-11 run.sh

@@ -1,0 +1,10 @@
+
+python3 app.py
+
+python3 cleandata.py
+
+python3 reports.py
+
+python3 latextablemaker.py
+
+python3 isolines.py

### 2022-12-11 paper/new/CW01.tex
Working on Article

@@
 
-\title{List of exercises 01\\
-	Fundamentals of optimization}
+\title{Quasi-Newton Methods Comparision using Ackley, Beale, Booth, Matyas, Rastrigin and RosenBrock Functions}
 \author{
-	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}}
-	\IEEEauthorblockA{\IEEEauthorrefmark{1}augusto.adams@ufpr.br}
+	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3}, Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}
+	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143 - augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403 -  caiomizerkowski@gmail.com} \IEEEauthorblockA{\IEEEauthorrefmark{3}GRR20172197 - christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957 - eduardo.reis02@gmail.com}
 }
+
+\markboth
+{Adams \headeretal: Quasi-Newton Methods Comparision using Ackley, Beale, Booth, Matyas, Rastrigin and RosenBrock Functions}
+{Adams \headeretal: Quasi-Newton Methods Comparision using Ackley, Beale, Booth, Matyas, Rastrigin and RosenBrock Functions}
 
@@
 \begin{abstract}
-	This document is submitted as a partial requirement for	evaluation of the discipline of \textit{Evolutionary Computation and Inteligence of Swarms(TE-943)} of the Electrical Engineering Course, with emphasis in Embedded Systems, of the Electrical Engineering Department at the Federal University of Paraná.
+This paper discusses briefly four popular algorithms to solve optimization/minimization problems, beloginging to Quasi-Newton class: \textit{Davidon–Fletcher–Powell} (DFP), \textit{Broyden–Fletcher–Goldfarb–Shanno} (BFGS), limited memory BFGS and \textit{Levenberg-Marquardt Algorithm} (LMA).
+These algorithms are implemented in \textit{Python language}, version 3.10 and uses \textit{SymPy}, \textit{SciPy} and \textit{NumPy} libraries.
+One of them, \textit{BFGS}, is implemented natively on the  \textit{SciPy} library and the rest are implemented by hand to provide useful insights about the inner operation of the algorithms.
+The results are, however, very corrent with a few exceptions.
 \end{abstract}
 
-\begin{IEEEkeywords}Optimization Problem; Linear Programming; Non-linear Programming;\end{IEEEkeywords}
+\begin{IEEEkeywords}Optimization Problem; Linear Programming; Non-linear Programming; Quasi-Newton Algorithms\end{IEEEkeywords}
 
-\section{Question 01}
+\section{Introduction}
 
-\textbf{\textit{Given the design vector: $\vec{X} = \left\{ \mathbf{x}_{1}, \mathbf{x}_{2}, \mathbf{x}_{3}, \hdots \mathbf{x}_{n}\right\}^T$, match the following terms and descriptions:}}
+\section{Methodology}
 
-\begin{multicols}{2}
+\section{Results}
 
-	$(a)$ Free feasible point
+\subsection{Ackley Function}
 
-	$(b)$ Free infeasible point
+\input{latex/ackley_best_fits.tex}
 
-	$(c)$ Bound feasible point
-
-	$(d)$ Bound infeasible point
-
-	$(e)$ Active constraints
-
-	\columnbreak
-
-	$(e)$ $g_j(\vec{X}) = 0$
-
-	$(c)$ Some $g_j(\vec{X}) = 0$ and other $g_j(\vec{X}) < 0$
-
-	$(d)$ Some $g_j(\vec{X}) = 0$ and other $g_j(\vec{X}) \geq 0$
-
-	$(b)$ Some $g_j(\vec{X})>0$ and other $g_j(\vec{X}) < 0$
-
-	$(a)$ All $g_j(\vec{X}) < 0$
-\end{multicols}
-
-From the book \textit{``Engineering Optimization - Theory and Practice''} (Rao, 2019):
-
-\begin{quotation}
-	Consider an optimization problem with only inequality constraints $g_j (\vec{\mathbf{X}}) \leq 0$.
-The set of values of $\vec{\mathbf{X}}$ that satisfy the equation $g_j(\vec{\mathbf{X}}) = 0$ forms a hypersurface in the design space and is called a constraint surface.
-Note that this is an $\left(n - 1\right)$-dimensional subspace, where $n$ is the number of design variables.
-The constraint surface divides the design space into two regions: one in which $g_j (\vec{\mathbf{X}}) \le 0$ and the other in which $g_j (\vec{\mathbf{X}}) > 0$.
-Thus, the points lying on the hypersurface will satisfy the constraint $g_j (\vec{\mathbf{X}})$ critically, whereas the points lying in the region where $g_j (\vec{\mathbf{X}}) > 0$ are infeasible or unacceptable, and the points lying in the region where $g_j (\vec{\mathbf{X}}) < 0$ are feasible or acceptable.
-The collection of all the constraint surfaces $g_j (\vec{\mathbf{X}}) = 0, j = 1, 2, .
-.
-.
-,m$ which separates the acceptable region is called the \textit{composite constraint surface}.
-
-	A design point that lies on one or more than one constraint surface is called a \textit{bound point}, and the associated constraint is called an\textit{ active constraint}.
-Design points that do not lie on any constraint surface are known as \textit{free points}.
-Depending on whether a particular design point belongs to the \textit{acceptable} or \textit{unacceptable} region, it can be identified as one of the following four types:
-
-	\begin{enumerate}
-		\item \textit{Free and acceptable point}
-		\item \textit{Free and unacceptable point}
-		\item \textit{Bound and acceptable point}
-		\item \textit{Bound and unacceptable point}
-	\end{enumerate}
-
-\end{quotation}
-
-\section{Question 02}
-\textit{\textbf{How do you solve a maximization problem as a minimization problem?}}
-
-\textit{Answer:} The point $\hat{\mathbf{x}}$ that maximizes $f(\mathbf{x})$ minimizes $-f(\mathbf{x})$, thus to solve a maximization problem as a minimization problem is to solve for the negative objective function.
-
-From the book \textit{``Engineering Optimization - Theory and Practice''}  (Rao, 2019):
-
-\begin{quotation}
-	It can be seen from \textit{Figure 1.1} that if a point $\hat{\mathbf{x}}$ corresponds to the minimum value of function $f (\mathbf{x})$, the same point also corresponds to the maximum value of the negative of the function, $-f (\mathbf{x})$.
-Thus, without loss of generality, optimization can be taken to mean minimization, since the maximum of a function can be found by seeking the minimum of the negative of the same function.
-\end{quotation}
-
-From the Book \textit{``Practical Mathematical Optimization''} (Synman and Wilke, 2018):
-
-\begin{quotation}
-	The maximization problem: $max\{f(\mathbf{x})\}$ can be cast in the standard form by observing that $max\{f(\mathbf{x})\}$ = $-min\{-f(\mathbf{x})\}$.
-Therefore in applying a minimization algorithm set $F(\mathbf{x}) = -f (\mathbf{x})$.
-Also if the inequality constraints are given in the non-standard form:	$g_j (\mathbf{x}) \geq 0$, then set $\hat{g}_j (\mathbf{x}) = -g_j (\mathbf{x})$.
-In standard form the problem then becomes:
-	\begin{center}
-		minimize $F(\mathbf{x})$ such that $\hat{g}_j (\mathbf{x}) \leq 0$.
-	\end{center}
-
-	Once the minimizer $\hat{\mathbf{x}}$ is obtained, the maximum value of the original maximization problem is given by $-F(\hat{\mathbf{x}})$.
-\end{quotation}
-
-\section{Question 03}
-
-\textbf{\textit{What is the difference between linear and nonlinear	programming problems?}}
-
-\textit{Answer:} The major difference between linear and nonlinear programming problems is the function type of objective function and constraints.
-In the \textit{Linear Programming Problem} (\textbf{\textit{LP}}), both objective function and constraints are linear, that is, the objective function and constraints are of zero or first order.
-In the case of \textit{Nonlinear Programming Problem} (\textbf{\textit{NLP}}), any of objective function or constraints are nonlinear functions, that is, are of second or higher order or have exotic functions (trigonometrical functions, exponential functions, etc).
-
-From the book \textit{``Engineering Optimization - Theory and Practice''}  (Rao, 2019):
-
-\begin{quotation}
-	\textbf{\textit{Linear Programming Problem}} If the objective function and all the constraints are linear functions of the design variables, the mathematical programming problem is called a \textit{Linear Programming Problem} (\textbf{\textit{LP}}).
-
-	\textbf{\textit{Nonlinear Programming Problem}} If any of the functions among the objective and
-	constraint functions in Eq. (1.1) is nonlinear, the problem is called an \textit{NLP problem}.
-	This is the most general programming problem and all other problems can be considered as special cases of the \textit{NLP problem}.
-
-\end{quotation}
-
-\section{Question 04}
-
-\textbf{\textit{What is the difference between design variables and	preassigned parameters?}}
-
-\textit{Answer:}
-
-\begin{itemize}
-	\item \textit{\textbf{Preassigned parameters:}} fixed values or quantities of the problem;
-	\item \textit{\textbf{Design Variables:}} other values or quantities of the problem, usually called \textit{design} or \textit{decision} variables.
-As the names says, obviously they can vary to accomodate the optimal result for the problem.
-\end{itemize}
-
-From the book \textit{``Engineering Optimization - Theory and Practice''}  (Rao, 2019):
-\begin{quotation}
-Any engineering system or component is defined by a set of quantities, some of which are viewed as variables during the design process.
-In general, certain quantities are usually fixed at the outset and these are called preassigned parameters.
-All the other quantities are treated as variables in the design process and are called design or decision variables $\mathbf{x}_i$ , $i = 1, 2, \hdots , n$.
-The design variables are collectively represented as a design vector $\vec{X} = \left\{ \mathbf{x}_{1} , \mathbf{x}_{2} , \hdots , \mathbf{x}_{n} \right\}^{T}$.
-As an example, consider the design of the gear pair, characterized by its face width $b$, number of teeth $T_1$ and $T_2$ , center distance $d$, pressure angle $\phi$, tooth profile, and material.
-If center distance $d$, pressure angle $\phi$, tooth profile, and material of the gears are fixed in advance, these quantities can be called preassigned parameters.
-The remaining quantities can be collectively represented by a design vector $X = \left\{ \mathbf{x}_1 , \mathbf{x}_2 , \mathbf{x}_3 \right\}^{T} = \left\{ b, T_1 , T_2 \right\}^{T}$ .
-If there are no restrictions on the choice of $b$, $T_1$ , and $T_2$ , any set of three numbers will constitute a design for the gear pair.
-If an $n$-dimensional Cartesian space with each coordinate axis representing a design variable $\mathbf{x}_i$ $(i = 1, 2, \hdots , n)$ is considered, the space is called the design variable space or simply design space.
-Each point in the $n$-dimensional design space is called a design point and represents either a possible or an impossible solution to the design problem.
-
-\end{quotation}
-
-\section{Question 05}
-
-\textbf{\textit{What is the difference between a bound point and a free point in the design space?}}
-
-\textit{Answer:} a bounding point is a design point that lies on one or more constraints, a free point is a design point that does not lie on any constraint.
-
-From the book \textit{``Engineering Optimization - Theory and Practice''} (Rao, 2019):
-
-\begin{quotation}
-
-	A design point that lies on one or more than one constraint surface is called a \textit{bound point}, and the associated constraint is called an\textit{ active constraint}.
-Design points that do not lie on any constraint surface are known as \textit{free points}.
-
-\end{quotation}
-
-\section{Question 06}
-
-\textbf{\textit{What are the differences between zero, first and second order optimization methods?}}
-
-\textit{Answer:} the terms zero, first and second order refers to the nth-derivative used by the method.
-
-\begin{itemize}
-	\item \textbf{\textit{Zero order methods:}} employs the objective function $f$ directly.
-Examples of zero order methods are Nelder-Mead simplex (direct search),  Powell conjugate directions and Optimization metaheuristics;
-	\subitem From the Book \textit{``Practical Mathematical Optimization''} (Synman and Wilke, 2018):
-		\begin{quotation}
-			These methods are called such because they neither use first order nor second order derivative information, but only function values, i.e. only zero order derivative information.
-
-			Zero order methods are of the earliest methods and many of them	are based on rough and ready ideas with few theoretical background.	Although these ad hoc methods are, as one may expect, much slower and computationally much more expensive than the higher order methods, they are usually reliable and easy to program.
-One of the most
-			successful of these methods is the \textit{downhill simplex method} of Nelder and Mead (1965), also known as Nelder-Mead.
-
-		\end{quotation}
-
-	\item \textbf{\textit{First order methods:}} employs at least the first derivative $f$ (first order information).
-It approximates $f$ as a plane.
-Examples of first order methods are Steepest descent methods, Nonlinear conjugate gradients methods and Broyden-Fletcher-Goldfarb-Shanno algorithms (BFGS).
-
-	\subitem From the Book \textit{``Practical Mathematical Optimization''} (Synman and Wilke, 2018):
-		\begin{quotation}
-			Line search descent methods (see Section 2.1.1), that use the gradient vector $\nabla f(\mathbf{x})$  to determine the search direction for each iteration, are called first order methods because they employ first order partial derivatives of $f(\mathbf{x})$ to compute the search direction at the current iterate.
-The simplest and most famous of these methods is the method of steepest	descent, first proposed by Cauchy in 1847.
-		\end{quotation}
-
-	\item \textbf{\textit{Second order methods:}} employs at least the second derivative of $f$ (second order information).
-It approximates $f$ as a quadratic form.
-Examples of second order method are Newton’s method, Newton conjugate gradient and Quasi-Newton method.
-		\subitem From the Book \textit{``Practical Mathematical Optimization''} (Synman and Wilke, 2018):
-
-		\begin{quotation}
-			These methods are based on Newton’s method (see Section 1.5.4.1) for solving $\nabla f (\mathbf{x}) = 0$ iteratively: Given $\mathbf{x}_0$ , then $\mathbf{x}_i = \mathbf{x}_{i-1} - H^{-1} (\mathbf{x}_{i-1})\nabla f (\mathbf{x}_{i-1} )$, $i = 1, 2, \hdots $
-			The main characteristics of this method are:
-
-			\begin{itemize}
-				\item In the neighbourhood of the solution it may converge very fast.
-In fact, it has the very desirous property of being quadratically	convergent if it converges.
-Unfortunately convergence is not guaranteed and it may sometimes diverge, even from close to the solution.
-				\item The implementation of the method requires that $H(\mathbf{x})$  be evaluated at each step.
-				\item To obtain the Newton step, $\Delta = \mathbf{x}_i - \mathbf{x}_{i-1}$ it is also necessary to solve a $n \times n$ linear system $H(\mathbf{x})\Delta = -\nabla f (\mathbf{x})$ at each iteration.
-This is computationally very expensive for large $n$, since an order $n^3$ multiplication operations are required to solve the system numerically.
-			\end{itemize}
-
-		\end{quotation}
-		$H(\mathbf{x})$ is the \textit{Hessian} matrix or the second derivative of $f(\mathbf{x})$.
-\end{itemize}
-
-\section{Question 07}
-\textbf{\textit{Considering an optimization global problem given by $min\{f(\mathbf{x})\}$, define global minimum, strong local minimum, weak local minimum, weak global minimum, strong global minimum, and	saddle points.}}
-
-\begin{itemize}
-	\item \textbf{\textit{Global Minimum (Synman and Wilke, 2018):}} $\hat{\mathbf{x}}$ is a \textit{global minimum} over the set $X$ if $f (\mathbf{x}) \geq f(\hat{\mathbf{x}})$ for all $x \in X \subset \mathbb{R} ^ n $.
-	\item \textbf{\textit{Strong and Weak Global Minima (Arora, 2016):}} A function $f(\mathbf{x})$ of $n$ variables has a \textit{global (absolute) minimum} at $\hat{\mathbf{x}}$ if 
-		\begin{equation}
-			f(\mathbf{x}) \geq f(\hat{\mathbf{x}})
-			\label{ineq01}
-		\end{equation}
-	for all $\mathbf{x}$ in the feasible design space $S$.
-If strict inequality holds for all $\mathbf{x}$ other than $\hat{\mathbf{x}}$ in Inequality \ref{ineq01}, then  $\hat{\mathbf{x}}$ is called a \textit{strong (strict) global minimum}; otherwise it is called a \textit{weak global minimum}.
-	\item \textbf{\textit{Strong and Weak Local Minima (Arora, 2016):}} A function $f(\mathbf{x})$ of $n$ variables has a \textit{local (relative) minimum}	at $\hat{\mathbf{x}}$ if Inequality \ref{ineq01} holds for all $\mathbf{x}$ in a small neighborhood $N$ of $\hat{\mathbf{x}}$ in the feasible design space $S$.
-If strict inequality holds, then $\hat{\mathbf{x}}$ is called a \textit{strong (strict) local minimum}; otherwise it is called a \textit{weak local minimum}.
-	\item \textbf{\textit{Saddle Points (Rao, 2019):}} In the case of a function of two variables, $f (x, y)$, the \textit{Hessian} matrix may be neither positive nor negative definite at a point $(\hat{x}, \hat{y})$ at which
-	\begin{equation}
-		\frac{\partial f}{\partial x} = \frac{\partial f}{\partial y} = 0
-		\label{saddlecond}
-	\end{equation}
-	In such a case, the point $(\hat{x}, \hat{y})$ is called a \textit{saddle point}. The characteristic of a saddle
-	point is that it corresponds to a relative minimum or maximum of $f(x, y)$ with respect to one variable, say, $x$ (the other variable being fixed at $y = \hat{y}$) and a relative maximum or minimum of $f(x, y)$ with respect to the second variable $y$ (the other variable being	fixed at $x = \hat{x}$).
-\end{itemize}
-
-\section{Question 08}
-\textbf{\textit{Considering a constrained optimization problem, define Lagrange multiplier and Karush-Kuhn-Tucker (KKT) conditions.}}
-
-\begin{itemize}
-	\item \textbf{\textit{Lagrange Multiplier (Figments of my deranged mind about my Calculus Course, 2017 - Prof.
-Viviana Cocco Mariani; Rao, 2019; Synman and Wilke, 2018; Arora, 2016):}} An optimization problem is given in the form:
-
-	\begin{equation}
-		\begin{split}
-		\text{minimize}\ f(\hat{\mathbf{x}})\\
-		\text{such that}\ g(\hat{\mathbf{x}}) = 0
-		\end{split}
-		\label{optimizationproblem01}
-	\end{equation}
-
-	It is possible to write the problem as:
-	\begin{equation}
-		\mathcal{L}(\hat{\mathbf{x}},\hat{\lambda}) = f(\hat{\mathbf{x}}) - \hat{\lambda}^T g(\hat{\mathbf{x}})
-	\end{equation}
-
-	Where $\mathcal{L}(\hat{\mathbf{x}},\hat{\lambda})$ is called the \textit{Lagrangian Function}, a linear combination of  $f(\hat{\mathbf{x}})$ and $g(\hat{\mathbf{x}})$.
-The $\hat{\lambda}$ factor is called the \textit{Lagrange Multiplier}.
-If there is a $\hat{\mathbf{x}}$ which is the optimization problem solution, then there exists a unique Lagrange multiplier $\hat{\lambda}$ such that $\nabla f(\hat{\mathbf{x}}) = \hat{\lambda}^{T}\nabla g(\hat{\mathbf{x}})$.
-	\\
-	The condition $\nabla f(\hat{\mathbf{x}}) = \hat{\lambda}^{T}\nabla g(\hat{\mathbf{x}})$ implies that any direction perpendicular to all gradients of the constraints is also perpendicular to the gradient of the function.
-In other words, the directional derivative of the function is 0 in every feasible direction.
-
-	\item \textit{\textbf{Karush-Kuhn-Tucker conditions (Synman and Wilke, 2018): }} considering the optimization problem  in the form:
-	 	\begin{equation}
-	 	\begin{split}
-	 		\text{minimize}\ f(\hat{\mathbf{x}})\\
-	 		\text{such that}\ g_j(\hat{\mathbf{x}}) \leq 0, \ j = 1, 2, \hdots , m
-	 	\end{split}
-	 	\label{optimizationproblem02}
-	 \end{equation}
-
- 	and the Lagrangian function defined as:
-
- 	\begin{equation}
- 		\mathcal{L}(\hat{\mathbf{x}},\hat{\lambda}) = f(\hat{\mathbf{x}}) - \sum_{j=1}^{m} \hat{\lambda}_j g_j(\hat{\mathbf{x}})
- 	\end{equation}
-
-	  and assuming the existence of Lagrange multiplier $\hat{\lambda}$ , then at the point $\hat{x}$ , corresponding to the solution of the optimization problem, the following conditions must be satisfied:
-
-	\begin{equation}
-		\begin{split}
-			\frac{\partial f}{\partial x_i} (\hat{\mathbf{x}}) - \sum_{j=1}^{m} \hat{\lambda}_j \frac{\partial g_j}{\partial x_i} (\hat{\mathbf{x}}) = 0 \ i = 1, 2, \hdots, n\\
-			g_j(\hat{\mathbf{x}}) \leq 0, \  i = 1, 2, \hdots, m\\
-			\hat{\lambda}_j g_j(\hat{\mathbf{x}}) = 0, \  i = 1, 2, \hdots, m\\
-			\hat{\lambda}_j \geq 0, \  i = 1, 2, \hdots, m
-		\end{split}
-	\end{equation}
-	Which are the \textit{Karush-Kuhn-Tucker conditions}.
-It can be shown, that the KKT conditions also constitute sufficient conditions (those that imply that) for $\hat{x}$ to be a constrained minimum, if $f(\mathbf{x})$ and the $g_j(\mathbf{x})$	are all convex functions.
-\end{itemize}
+\input{latex/ackley_function_values.tex}
 

### 2022-12-13 latex/ackley_best_fits.tex
Added build to main latex file

\begin{table}
\centering
\caption{Best Fits For Ackley Function}
\label{solutions:ackley}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &     36 &      108 &      0.00 \\
 bfgs & $S_{2}$ &     42 &      129 &      0.00 \\
lbfgs & $S_{3}$ &     37 &      389 &      0.00 \\
  lma & $S_{4}$ &     38 &      320 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

### 2022-12-13 latex/ackley_best_solutions.tex
Added build to main latex file

\begin{table}
\centering
\caption{Detailed Solutions For Ackley Function}
\label{detailedsolutions:ackley}
\begin{tabular}{lrrrr}
\toprule
 Coord. &  $S_{1}$ &  $S_{2}$ &  $S_{3}$ &  $S_{4}$ \\
\midrule
$x_{1}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
$x_{2}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
\bottomrule
\end{tabular}
\end{table}

### 2022-12-13 latex/ackley_convergence.tex
Added build to main latex file

\begin{table}
\centering
\caption{Convergence Report For Ackley Function}
\label{convergence:ackley}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &   100 &     0 &       0 &    100 \\
 bfgs &   100 &     0 &       0 &    100 \\
lbfgs &   100 &     0 &       0 &    100 \\
  lma &   100 &     0 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

### 2022-12-13 latex/ackley_function_values.tex
Added build to main latex file

\begin{table}
\centering
\caption{Statistical Information about function values For Ackley Function}
\label{function_values:ackley}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Min &  Max &  Mean &  Median \\
\midrule
  dfp & 0.00 & 0.00 &  0.00 &    0.00 \\
 bfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
lbfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
  lma & 0.00 & 0.00 &  0.00 &    0.00 \\
\bottomrule
\end{tabular}
\end{table}

### 2022-12-13 latex/beale_convergence.tex
Added build to main latex file

\begin{table}
\centering
\caption{Convergence Report For Beale Function}
\label{convergence:beale}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &    53 &    25 &      22 &    100 \\
 bfgs &    75 &     0 &      25 &    100 \\
lbfgs &    80 &     0 &      20 &    100 \\
  lma &    42 &    37 &      21 &    100 \\
\bottomrule
\end{tabular}
\end{table}

### 2022-12-13 latex/beale_function_values.tex
Added build to main latex file

\begin{table}
\centering
\caption{Statistical Information about function values For Beale Function}
\label{function_values:beale}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Min &   Max &  Mean &  Median \\
\midrule
  dfp & 0.00 &  3.84 &  0.27 &    0.00 \\
 bfgs & 0.00 &  0.45 &  0.11 &    0.00 \\
lbfgs & 0.00 &  7.31 &  0.36 &    0.00 \\
  lma & 0.00 & 14.20 &  5.35 &    0.45 \\
\bottomrule
\end{tabular}
\end{table}

### 2022-12-13 latex/booth_best_fits.tex
Added build to main latex file

\begin{table}
\centering
\caption{Best Fits For Booth Function}
\label{solutions:booth}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &      4 &        6 &      0.00 \\
 bfgs & $S_{2}$ &      2 &        5 &      0.00 \\
lbfgs & $S_{3}$ &      5 &       21 &      0.00 \\
  lma & $S_{4}$ &     10 &       11 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

### 2022-12-13 latex/header.tex
Added build to main latex file

--- 2022-12-11 paper/new/CW01.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+\documentclass{ieeeaccess}
 \usepackage{cite}
 \usepackage{amsmath,amssymb,amsfonts}
-\usepackage{mathtools}
-\usepackage{algpseudocode}
-\usepackage{algorithm}
-\usepackage{algorithmicx}
-\usepackage{microtype}
-\usepackage{float}
-\usepackage{adjustbox}
-\usepackage{booktabs,makecell,tabularx}
+\usepackage{algorithmic}
 \usepackage{graphicx}
 \usepackage{textcomp}
-\usepackage{verbatim}
-\usepackage{xcolor}
-\usepackage{graphics} % for pdf, bitmapped graphics files
-\usepackage{epsfig} % for postscript graphics files
-\usepackage{mathptmx} % assumes new font selection scheme installed
-\usepackage{multicol}
-\usepackage[english]{babel}
-\usepackage[T1]{fontenc}
-
+\usepackage{booktabs}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\newcommand\norm[1]{\left\Vert#1\right\Vert}
 \begin{document}
-
+\history{Unpublished, First Preview}
+\doi{Unpublished/NoDOIInformation}
 \title{Quasi-Newton Methods Comparision using Ackley, Beale, Booth, Matyas, Rastrigin and RosenBrock Functions}
 \author{
-	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3}, Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}
-	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143 - augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403 -  caiomizerkowski@gmail.com} \IEEEauthorblockA{\IEEEauthorrefmark{3}GRR20172197 - christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957 - eduardo.reis02@gmail.com}
+	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}}
+    \IEEEauthorblockN{Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}}
+    \IEEEauthorblockN{Christian Piltz Araújo\IEEEauthorrefmark{3}}
+    \IEEEauthorblockN{Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}
+	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br}
+	\IEEEauthorblockA{\IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com}
+	\IEEEauthorblockA{\IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br}
+	\IEEEauthorblockA{\IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
 }
@@
 
-\maketitle
-
+\corresp{Corresponding author: Augusto Mathias Adams (e-mail: augusto.adams@ufpr.br).}
 \begin{abstract}
@@
 One of them, \textit{BFGS}, is implemented natively on the  \textit{SciPy} library and the rest are implemented by hand to provide useful insights about the inner operation of the algorithms.
-The results are, however, very corrent with a few exceptions.
+The results are, however, very surprising with a few exceptions: when the initial solution is placed in a region near the global minimum, almost all algorithms converges very quickly, so, a study was made to limit the initial solution to  these regions.
+With exception of
 \end{abstract}
 
-\begin{IEEEkeywords}Optimization Problem; Linear Programming; Non-linear Programming; Quasi-Newton Algorithms\end{IEEEkeywords}
+\begin{keywords} 
+Optimization Methods, Quasi-Newton, Non-linear Programming
+\end{keywords}
+
+\titlepgskip=-15pt
+
+\maketitle
 
 \section{Introduction}
-
-\section{Methodology}
-
-\section{Results}
-
-\subsection{Ackley Function}
-
-\input{latex/ackley_best_fits.tex}
-
-\input{latex/ackley_function_values.tex}
-
-\end{document}
+\label{sec:introduction}

### 2022-12-13 latex/rastrigin2d_convergence.tex
Added build to main latex file

\begin{table}
\centering
\caption{Convergence Report For Rastrigin Function}
\label{convergence:rastrigin2d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &   100 &     0 &       0 &    100 \\
 bfgs &   100 &     0 &       0 &    100 \\
lbfgs &    99 &     1 &       0 &    100 \\
  lma &   100 &     0 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

### 2022-12-13 latex/rosenbrock2d_convergence.tex
Added build to main latex file

\begin{table}
\centering
\caption{Convergence Report For Rosenbrock Function}
\label{convergence:rosenbrock2d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &    74 &    26 &       0 &    100 \\
 bfgs &   100 &     0 &       0 &    100 \\
lbfgs &   100 &     0 &       0 &    100 \\
  lma &   100 &     0 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

### 2022-12-13 paper/new/article.tex
Added build to main latex file

\documentclass{ieeeaccess}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{booktabs}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\history{Unpublished, First Preview}
\doi{Unpublished/NoDOIInformation}
\title{Quasi-Newton Methods Comparision using Ackley, Beale, Booth, Matyas, Rastrigin and RosenBrock Functions}
\author{
	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}}
    \IEEEauthorblockN{Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}}
    \IEEEauthorblockN{Christian Piltz Araújo\IEEEauthorrefmark{3}}
    \IEEEauthorblockN{Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}
	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br}
	\IEEEauthorblockA{\IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com}
	\IEEEauthorblockA{\IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br}
	\IEEEauthorblockA{\IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
}

\markboth
{Adams \headeretal: Quasi-Newton Methods Comparision using Ackley, Beale, Booth, Matyas, Rastrigin and RosenBrock Functions}
{Adams \headeretal: Quasi-Newton Methods Comparision using Ackley, Beale, Booth, Matyas, Rastrigin and RosenBrock Functions}

\corresp{Corresponding author: Augusto Mathias Adams (e-mail: augusto.adams@ufpr.br).}
\begin{abstract}
This paper discusses briefly four popular algorithms to solve optimization/minimization problems, beloginging to Quasi-Newton class: \textit{Davidon–Fletcher–Powell} (DFP), \textit{Broyden–Fletcher–Goldfarb–Shanno} (BFGS), limited memory BFGS and \textit{Levenberg-Marquardt Algorithm} (LMA). These algorithms are implemented in \textit{Python language}, version 3.10 and uses \textit{SymPy}, \textit{SciPy} and \textit{NumPy} libraries. One of them, \textit{BFGS}, is implemented natively on the  \textit{SciPy} library and the rest are implemented by hand to provide useful insights about the inner operation of the algorithms. The results are, however, very surprising with a few exceptions: when the initial solution is placed in a region near the global minimum, almost all algorithms converges very quickly, so, a study was made to limit the initial solution to  these regions. With exception of 
\end{abstract}

\begin{keywords} 
Optimization Methods, Quasi-Newton, Non-linear Programming
\end{keywords}

\titlepgskip=-15pt

\maketitle

\section{Introduction}
\label{sec:introduction}
\section{2D Function versions}
\label{functions2D}

\subsection{Ackley Function}
\label{ackley2D}

\subsubsection{Convergence Analysis}
\label{convergenceackley2D}

Introductory text goes here...
\begin{table}
\centering
\caption{Convergence Report For Ackley Function}
\label{convergence:ackley}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &   100 &     0 &       0 &    100 \\
 bfgs &   100 &     0 &       0 &    100 \\
lbfgs &   100 &     0 &       0 &    100 \\
  lma &   100 &     0 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Statistical Analysis of The Solutions}
\label{statisticalanalysisackley2D}

Introductory text goes here...
\begin{table}
\centering
\caption{Statistical Information about function values For Ackley Function}
\label{function_values:ackley}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Min &  Max &  Mean &  Median \\
\midrule
  dfp & 0.00 & 0.00 &  0.00 &    0.00 \\
 bfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
lbfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
  lma & 0.00 & 0.00 &  0.00 &    0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Best Fits}
\label{bestfitsackley2D}

Introductory text goes here...
\begin{table}
\centering
\caption{Best Fits For Ackley Function}
\label{solutions:ackley}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &     36 &      108 &      0.00 \\
 bfgs & $S_{2}$ &     42 &      129 &      0.00 \\
lbfgs & $S_{3}$ &     37 &      389 &      0.00 \\
  lma & $S_{4}$ &     38 &      320 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\begin{table}
\centering
\caption{Detailed Solutions For Ackley Function}
\label{detailedsolutions:ackley}
\begin{tabular}{lrrrr}
\toprule
 Coord. &  $S_{1}$ &  $S_{2}$ &  $S_{3}$ &  $S_{4}$ \\
\midrule
$x_{1}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
$x_{2}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Isolines and Convergence line}
\label{isolinesackley2D}

Introductory text goes here...
\begin{figure}[h]
\centering
\includegraphics[scale=0.5]{images/ackley.jpg}
\caption{Isolines and convergence line for Ackley Function}
\label{fig:ackley}
\end{figure}

Comments goes here...
\subsection{Beale Function}
\label{beale2D}

\subsubsection{Convergence Analysis}
\label{convergencebeale2D}

Introductory text goes here...
\begin{table}
\centering
\caption{Convergence Report For Beale Function}
\label{convergence:beale}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &    53 &    25 &      22 &    100 \\
 bfgs &    75 &     0 &      25 &    100 \\
lbfgs &    80 &     0 &      20 &    100 \\
  lma &    42 &    37 &      21 &    100 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Statistical Analysis of The Solutions}
\label{statisticalanalysisbeale2D}

Introductory text goes here...
\begin{table}
\centering
\caption{Statistical Information about function values For Beale Function}
\label{function_values:beale}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Min &   Max &  Mean &  Median \\
\midrule
  dfp & 0.00 &  3.84 &  0.27 &    0.00 \\
 bfgs & 0.00 &  0.45 &  0.11 &    0.00 \\
lbfgs & 0.00 &  7.31 &  0.36 &    0.00 \\
  lma & 0.00 & 14.20 &  5.35 &    0.45 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Best Fits}
\label{bestfitsbeale2D}

Introductory text goes here...
\begin{table}
\centering
\caption{Best Fits For Beale Function}
\label{solutions:beale}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &      8 &       10 &      0.00 \\
 bfgs & $S_{2}$ &     15 &       18 &      0.00 \\
lbfgs & $S_{3}$ &     14 &       50 &      0.00 \\
  lma & $S_{4}$ &     12 &       13 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\begin{table}
\centering
\caption{Detailed Solutions For Beale Function}
\label{detailedsolutions:beale}
\begin{tabular}{lrrrr}
\toprule
 Coord. &  $S_{1}$ &  $S_{2}$ &  $S_{3}$ &  $S_{4}$ \\
\midrule
$x_{1}$ &     3.00 &     3.00 &     3.00 &     3.00 \\
$x_{2}$ &     0.50 &     0.50 &     0.50 &     0.50 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Isolines and Convergence line}
\label{isolinesbeale2D}

Introductory text goes here...
\begin{figure}[h]
\centering
\includegraphics[scale=0.5]{images/beale.jpg}
\caption{Isolines and convergence line for Beale Function}
\label{fig:beale}
\end{figure}

Comments goes here...
\subsection{Booth Function}
\label{booth2D}

\subsubsection{Convergence Analysis}
\label{convergencebooth2D}

Introductory text goes here...
\begin{table}
\centering
\caption{Convergence Report For Booth Function}
\label{convergence:booth}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &   100 &     0 &       0 &    100 \\
 bfgs &   100 &     0 &       0 &    100 \\
lbfgs &   100 &     0 &       0 &    100 \\
  lma &   100 &     0 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Statistical Analysis of The Solutions}
\label{statisticalanalysisbooth2D}

Introductory text goes here...
\begin{table}
\centering
\caption{Statistical Information about function values For Booth Function}
\label{function_values:booth}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Min &  Max &  Mean &  Median \\
\midrule
  dfp & 0.00 & 0.00 &  0.00 &    0.00 \\
 bfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
lbfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
  lma & 0.00 & 0.00 &  0.00 &    0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Best Fits}
\label{bestfitsbooth2D}

Introductory text goes here...
\begin{table}
\centering
\caption{Best Fits For Booth Function}
\label{solutions:booth}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &      4 &        6 &      0.00 \\
 bfgs & $S_{2}$ &      2 &        5 &      0.00 \\
lbfgs & $S_{3}$ &      5 &       21 &      0.00 \\
  lma & $S_{4}$ &     10 &       11 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\begin{table}
\centering
\caption{Detailed Solutions For Booth Function}
\label{detailedsolutions:booth}
\begin{tabular}{lrrrr}
\toprule
 Coord. &  $S_{1}$ &  $S_{2}$ &  $S_{3}$ &  $S_{4}$ \\
\midrule
$x_{1}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{2}$ &     3.00 &     3.00 &     3.00 &     3.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Isolines and Convergence line}
\label{isolinesbooth2D}

Introductory text goes here...
\begin{figure}[h]
\centering
\includegraphics[scale=0.5]{images/booth.jpg}
\caption{Isolines and convergence line for Booth Function}
\label{fig:booth}
\end{figure}

Comments goes here...
\subsection{Matyas Function}
\label{matyas2D}

\subsubsection{Convergence Analysis}
\label{convergencematyas2D}

Introductory text goes here...
\begin{table}
\centering
\caption{Convergence Report For Matyas Function}
\label{convergence:matyas}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &   100 &     0 &       0 &    100 \\
 bfgs &   100 &     0 &       0 &    100 \\
lbfgs &   100 &     0 &       0 &    100 \\
  lma &   100 &     0 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Statistical Analysis of The Solutions}
\label{statisticalanalysismatyas2D}

Introductory text goes here...
\begin{table}
\centering
\caption{Statistical Information about function values For Matyas Function}
\label{function_values:matyas}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Min &  Max &  Mean &  Median \\
\midrule
  dfp & 0.00 & 0.00 &  0.00 &    0.00 \\
 bfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
lbfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
  lma & 0.00 & 0.00 &  0.00 &    0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Best Fits}
\label{bestfitsmatyas2D}

Introductory text goes here...
\begin{table}
\centering
\caption{Best Fits For Matyas Function}
\label{solutions:matyas}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &      7 &       10 &      0.00 \\
 bfgs & $S_{2}$ &      7 &       10 &      0.00 \\
lbfgs & $S_{3}$ &      4 &       16 &      0.00 \\
  lma & $S_{4}$ &     14 &       15 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\begin{table}
\centering
\caption{Detailed Solutions For Matyas Function}
\label{detailedsolutions:matyas}
\begin{tabular}{lrrrr}
\toprule
 Coord. &  $S_{1}$ &  $S_{2}$ &  $S_{3}$ &  $S_{4}$ \\
\midrule
$x_{1}$ &     0.00 &    -0.00 &    -0.00 &     0.00 \\
$x_{2}$ &     0.00 &    -0.00 &     0.00 &     0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Isolines and Convergence line}
\label{isolinesmatyas2D}

Introductory text goes here...
\begin{figure}[h]
\centering
\includegraphics[scale=0.5]{images/matyas.jpg}
\caption{Isolines and convergence line for Matyas Function}
\label{fig:matyas}
\end{figure}

Comments goes here...
\subsection{Rastrigin Function}
\label{rastrigin2d2D}

\subsubsection{Convergence Analysis}
\label{convergencerastrigin2d2D}

Introductory text goes here...
\begin{table}
\centering
\caption{Convergence Report For Rastrigin Function}
\label{convergence:rastrigin2d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &   100 &     0 &       0 &    100 \\
 bfgs &   100 &     0 &       0 &    100 \\
lbfgs &    99 &     1 &       0 &    100 \\
  lma &   100 &     0 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Statistical Analysis of The Solutions}
\label{statisticalanalysisrastrigin2d2D}

Introductory text goes here...
\begin{table}
\centering
\caption{Statistical Information about function values For Rastrigin Function}
\label{function_values:rastrigin2d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Min &  Max &  Mean &  Median \\
\midrule
  dfp & 0.00 & 0.00 &  0.00 &    0.00 \\
 bfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
lbfgs & 0.00 & 1.99 &  0.02 &    0.00 \\
  lma & 0.00 & 0.00 &  0.00 &    0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Best Fits}
\label{bestfitsrastrigin2d2D}

Introductory text goes here...
\begin{table}
\centering
\caption{Best Fits For Rastrigin Function}
\label{solutions:rastrigin2d}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &      6 &       11 &      0.00 \\
 bfgs & $S_{2}$ &      8 &       49 &      0.00 \\
lbfgs & $S_{3}$ &      5 &      133 &      0.00 \\
  lma & $S_{4}$ &      4 &        5 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\begin{table}
\centering
\caption{Detailed Solutions For Rastrigin Function}
\label{detailedsolutions:rastrigin2d}
\begin{tabular}{lrrrr}
\toprule
 Coord. &  $S_{1}$ &  $S_{2}$ &  $S_{3}$ &  $S_{4}$ \\
\midrule
$x_{1}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
$x_{2}$ &     0.00 &    -0.00 &    -0.00 &     0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Isolines and Convergence line}
\label{isolinesrastrigin2d2D}

Introductory text goes here...
\begin{figure}[h]
\centering
\includegraphics[scale=0.5]{images/rastrigin2d.jpg}
\caption{Isolines and convergence line for Rastrigin Function}
\label{fig:rastrigin2d}
\end{figure}

Comments goes here...
\subsection{Rosenbrock Function}
\label{rosenbrock2d2D}

\subsubsection{Convergence Analysis}
\label{convergencerosenbrock2d2D}

Introductory text goes here...
\begin{table}
\centering
\caption{Convergence Report For Rosenbrock Function}
\label{convergence:rosenbrock2d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &    74 &    26 &       0 &    100 \\
 bfgs &   100 &     0 &       0 &    100 \\
lbfgs &   100 &     0 &       0 &    100 \\
  lma &   100 &     0 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Statistical Analysis of The Solutions}
\label{statisticalanalysisrosenbrock2d2D}

Introductory text goes here...
\begin{table}
\centering
\caption{Statistical Information about function values For Rosenbrock Function}
\label{function_values:rosenbrock2d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Min &  Max &  Mean &  Median \\
\midrule
  dfp & 0.00 & 1.33 &  0.04 &    0.00 \\
 bfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
lbfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
  lma & 0.00 & 0.00 &  0.00 &    0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Best Fits}
\label{bestfitsrosenbrock2d2D}

Introductory text goes here...
\begin{table}
\centering
\caption{Best Fits For Rosenbrock Function}
\label{solutions:rosenbrock2d}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &     24 &       31 &      0.00 \\
 bfgs & $S_{2}$ &     30 &       43 &      0.00 \\
lbfgs & $S_{3}$ &     27 &       76 &      0.00 \\
  lma & $S_{4}$ &     16 &       18 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\begin{table}
\centering
\caption{Detailed Solutions For Rosenbrock Function}
\label{detailedsolutions:rosenbrock2d}
\begin{tabular}{lrrrr}
\toprule
 Coord. &  $S_{1}$ &  $S_{2}$ &  $S_{3}$ &  $S_{4}$ \\
\midrule
$x_{1}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{2}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Isolines and Convergence line}
\label{isolinesrosenbrock2d2D}

Introductory text goes here...
\begin{figure}[h]
\centering
\includegraphics[scale=0.5]{images/rosenbrock2d.jpg}
\caption{Isolines and convergence line for Rosenbrock Function}
\label{fig:rosenbrock2d}
\end{figure}

Comments goes here...

\section{4D Function versions}
\label{functions4D}

\subsection{Rastrigin Function}
\label{rastrigin4d4D}

\subsubsection{Convergence Analysis}
\label{convergencerastrigin4d4D}

Introductory text goes here...
\begin{table}
\centering
\caption{Convergence Report For Rastrigin Function}
\label{convergence:rastrigin4d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &   100 &     0 &       0 &    100 \\
 bfgs &   100 &     0 &       0 &    100 \\
lbfgs &   100 &     0 &       0 &    100 \\
  lma &   100 &     0 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Statistical Analysis of The Solutions}
\label{statisticalanalysisrastrigin4d4D}

Introductory text goes here...
\begin{table}
\centering
\caption{Statistical Information about function values For Rastrigin Function}
\label{function_values:rastrigin4d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Min &  Max &  Mean &  Median \\
\midrule
  dfp & 0.00 & 0.00 &  0.00 &    0.00 \\
 bfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
lbfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
  lma & 0.00 & 0.00 &  0.00 &    0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Best Fits}
\label{bestfitsrastrigin4d4D}

Introductory text goes here...
\begin{table}
\centering
\caption{Best Fits For Rastrigin Function}
\label{solutions:rastrigin4d}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &     10 &       21 &      0.00 \\
 bfgs & $S_{2}$ &     11 &       61 &      0.00 \\
lbfgs & $S_{3}$ &      5 &      133 &      0.00 \\
  lma & $S_{4}$ &      4 &        5 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\begin{table}
\centering
\caption{Detailed Solutions For Rastrigin Function}
\label{detailedsolutions:rastrigin4d}
\begin{tabular}{lrrrr}
\toprule
 Coord. &  $S_{1}$ &  $S_{2}$ &  $S_{3}$ &  $S_{4}$ \\
\midrule
$x_{1}$ &     0.00 &     0.00 &     0.00 &     0.00 \\
$x_{2}$ &    -0.00 &    -0.00 &     0.00 &     0.00 \\
$x_{3}$ &    -0.00 &    -0.00 &     0.00 &    -0.00 \\
$x_{4}$ &    -0.00 &    -0.00 &     0.00 &     0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsection{Rosenbrock Function}
\label{rosenbrock4d4D}

\subsubsection{Convergence Analysis}
\label{convergencerosenbrock4d4D}

Introductory text goes here...
\begin{table}
\centering
\caption{Convergence Report For Rosenbrock Function}
\label{convergence:rosenbrock4d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &    46 &    54 &       0 &    100 \\
 bfgs &    90 &    10 &       0 &    100 \\
lbfgs &    89 &    11 &       0 &    100 \\
  lma &    91 &     9 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Statistical Analysis of The Solutions}
\label{statisticalanalysisrosenbrock4d4D}

Introductory text goes here...
\begin{table}
\centering
\caption{Statistical Information about function values For Rosenbrock Function}
\label{function_values:rosenbrock4d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Min &  Max &  Mean &  Median \\
\midrule
  dfp & 0.00 & 3.71 &  0.60 &    0.00 \\
 bfgs & 0.00 & 3.70 &  0.37 &    0.00 \\
lbfgs & 0.00 & 3.70 &  0.41 &    0.00 \\
  lma & 0.00 & 3.70 &  0.33 &    0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Best Fits}
\label{bestfitsrosenbrock4d4D}

Introductory text goes here...
\begin{table}
\centering
\caption{Best Fits For Rosenbrock Function}
\label{solutions:rosenbrock4d}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &     44 &       49 &      0.00 \\
 bfgs & $S_{2}$ &     29 &       35 &      0.00 \\
lbfgs & $S_{3}$ &     45 &      134 &      0.00 \\
  lma & $S_{4}$ &     18 &       20 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\begin{table}
\centering
\caption{Detailed Solutions For Rosenbrock Function}
\label{detailedsolutions:rosenbrock4d}
\begin{tabular}{lrrrr}
\toprule
 Coord. &  $S_{1}$ &  $S_{2}$ &  $S_{3}$ &  $S_{4}$ \\
\midrule
$x_{1}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{2}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{3}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{4}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...

\section{30D Function versions}
\label{functions30D}

\subsection{Rastrigin Function}
\label{rastrigin30d30D}

\subsubsection{Convergence Analysis}
\label{convergencerastrigin30d30D}

Introductory text goes here...
\begin{table}
\centering
\caption{Convergence Report For Rastrigin Function}
\label{convergence:rastrigin30d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &   100 &     0 &       0 &    100 \\
 bfgs &   100 &     0 &       0 &    100 \\
lbfgs &   100 &     0 &       0 &    100 \\
  lma &   100 &     0 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Statistical Analysis of The Solutions}
\label{statisticalanalysisrastrigin30d30D}

Introductory text goes here...
\begin{table}
\centering
\caption{Statistical Information about function values For Rastrigin Function}
\label{function_values:rastrigin30d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Min &  Max &  Mean &  Median \\
\midrule
  dfp & 0.00 & 0.00 &  0.00 &    0.00 \\
 bfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
lbfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
  lma & 0.00 & 0.00 &  0.00 &    0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Best Fits}
\label{bestfitsrastrigin30d30D}

Introductory text goes here...
\begin{table}
\centering
\caption{Best Fits For Rastrigin Function}
\label{solutions:rastrigin30d}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &      8 &       14 &      0.00 \\
 bfgs & $S_{2}$ &      9 &       54 &      0.00 \\
lbfgs & $S_{3}$ &      6 &      135 &      0.00 \\
  lma & $S_{4}$ &      4 &        5 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\begin{table}
\centering
\caption{Detailed Solutions For Rastrigin Function}
\label{detailedsolutions:rastrigin30d}
\begin{tabular}{lrrrr}
\toprule
  Coord. &  $S_{1}$ &  $S_{2}$ &  $S_{3}$ &  $S_{4}$ \\
\midrule
 $x_{1}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
 $x_{2}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
 $x_{3}$ &    -0.00 &     0.00 &    -0.00 &    -0.00 \\
 $x_{4}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
 $x_{5}$ &     0.00 &    -0.00 &    -0.00 &    -0.00 \\
 $x_{6}$ &     0.00 &    -0.00 &    -0.00 &    -0.00 \\
 $x_{7}$ &     0.00 &    -0.00 &     0.00 &     0.00 \\
 $x_{8}$ &     0.00 &    -0.00 &    -0.00 &    -0.00 \\
 $x_{9}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
$x_{10}$ &    -0.00 &     0.00 &     0.00 &    -0.00 \\
$x_{11}$ &     0.00 &    -0.00 &     0.00 &     0.00 \\
$x_{12}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
$x_{13}$ &     0.00 &    -0.00 &    -0.00 &    -0.00 \\
$x_{14}$ &     0.00 &    -0.00 &     0.00 &     0.00 \\
$x_{15}$ &     0.00 &    -0.00 &    -0.00 &    -0.00 \\
$x_{16}$ &     0.00 &    -0.00 &    -0.00 &    -0.00 \\
$x_{17}$ &    -0.00 &     0.00 &    -0.00 &    -0.00 \\
$x_{18}$ &     0.00 &    -0.00 &    -0.00 &    -0.00 \\
$x_{19}$ &    -0.00 &     0.00 &    -0.00 &    -0.00 \\
$x_{20}$ &    -0.00 &     0.00 &    -0.00 &    -0.00 \\
$x_{21}$ &     0.00 &    -0.00 &     0.00 &     0.00 \\
$x_{22}$ &    -0.00 &     0.00 &    -0.00 &    -0.00 \\
$x_{23}$ &     0.00 &    -0.00 &    -0.00 &    -0.00 \\
$x_{24}$ &    -0.00 &     0.00 &    -0.00 &     0.00 \\
$x_{25}$ &    -0.00 &     0.00 &    -0.00 &     0.00 \\
$x_{26}$ &     0.00 &    -0.00 &     0.00 &     0.00 \\
$x_{27}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
$x_{28}$ &    -0.00 &     0.00 &    -0.00 &    -0.00 \\
$x_{29}$ &    -0.00 &     0.00 &    -0.00 &    -0.00 \\
$x_{30}$ &     0.00 &    -0.00 &    -0.00 &     0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsection{Rosenbrock Function}
\label{rosenbrock30d30D}

\subsubsection{Convergence Analysis}
\label{convergencerosenbrock30d30D}

Introductory text goes here...
\begin{table}
\centering
\caption{Convergence Report For Rosenbrock Function}
\label{convergence:rosenbrock30d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Good &  Poor &  Diver. &  Total \\
\midrule
  dfp &     1 &    99 &       0 &    100 \\
 bfgs &    80 &    20 &       0 &    100 \\
lbfgs &    95 &     5 &       0 &    100 \\
  lma &    88 &    12 &       0 &    100 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Statistical Analysis of The Solutions}
\label{statisticalanalysisrosenbrock30d30D}

Introductory text goes here...
\begin{table}
\centering
\caption{Statistical Information about function values For Rosenbrock Function}
\label{function_values:rosenbrock30d}
\begin{tabular}{lrrrr}
\toprule
 Alg. &  Min &   Max &  Mean &  Median \\
\midrule
  dfp & 0.00 & 29.25 & 13.10 &   12.58 \\
 bfgs & 0.00 &  3.99 &  0.80 &    0.00 \\
lbfgs & 0.00 &  3.99 &  0.20 &    0.00 \\
  lma & 0.00 &  3.99 &  0.48 &    0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\subsubsection{Best Fits}
\label{bestfitsrosenbrock30d30D}

Introductory text goes here...
\begin{table}
\centering
\caption{Best Fits For Rosenbrock Function}
\label{solutions:rosenbrock30d}
\begin{tabular}{llrrr}
\toprule
 Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
\midrule
  dfp & $S_{1}$ &   2967 &     2990 &      0.00 \\
 bfgs & $S_{2}$ &    236 &      252 &      0.00 \\
lbfgs & $S_{3}$ &    164 &      406 &      0.00 \\
  lma & $S_{4}$ &     53 &      131 &      0.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...
\begin{table}
\centering
\caption{Detailed Solutions For Rosenbrock Function}
\label{detailedsolutions:rosenbrock30d}
\begin{tabular}{lrrrr}
\toprule
  Coord. &  $S_{1}$ &  $S_{2}$ &  $S_{3}$ &  $S_{4}$ \\
\midrule
 $x_{1}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
 $x_{2}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
 $x_{3}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
 $x_{4}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
 $x_{5}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
 $x_{6}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
 $x_{7}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
 $x_{8}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
 $x_{9}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{10}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{11}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{12}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{13}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{14}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{15}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{16}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{17}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{18}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{19}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{20}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{21}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{22}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{23}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{24}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{25}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{26}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{27}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{28}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{29}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
$x_{30}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
\bottomrule
\end{tabular}
\end{table}

Comments goes here...

\EOD

\end{document}

### 2022-12-13 Solvers/__init__.py

@@ -77,3 +77,8 @@ algorithms = {"dfp": dfp,
               "bfgs": bfgs,
               "lbfgs": lbfgs,
               "lma": lma}
+
+algorithms_names = {"dfp": "DFP",
+                    "bfgs": "BFGS",
+                    "lbfgs": "LBFGS",
+                    "lma": "LMA"}

### 2022-12-13 build_main_latex_file.py

@@ -1,0 +1,104 @@
+"""
+Computational Work 01 - Fundamentals of optimization
+Authors: Augusto Mathias Adams - augusto.adams@ufpr.br - GRR20172143
+         Caio Phillipe Mizerkowski - caiomizerkowski@gmail.com - GRR20166403
+         Christian Piltz Araújo - christian0294@yahoo.com.br - GRR20172197
+         Vinícius Eduardo dos Reis - eduardo.reis02@gmail.com - GRR20175957
+
+Main Article Skeleton Building
+"""
+
+from Solvers import *
+
+header_file = "latex/header.tex"
+
+footer_file = "latex/footer.tex"
+
+content = dict()
+
+content[2] = "\section{2D Function versions}\n\label{functions2D}\n\n"
+
+content[4] = "\section{4D Function versions}\n\label{functions4D}\n\n"
+
+content[30] = "\section{30D Function versions}\n\label{functions30D}\n\n"
+
+for function in constraints:
+
+    def_func = constraints[function]['def_func']
+
+    defs = def_func()
+
+    functionString = "{:s}{:d}D".format(function, defs['dimension'])
+
+    functionName = function_names[function]
+
+    content[defs['dimension']] += "\subsection{" + \
+                                  functionName + \
+                                  "}\n\label{" + \
+                                  functionString + "}\n\n"
+
+    content[
+        defs['dimension']] += "\subsubsection{Convergence Analysis}\n\label{" + "convergence" + functionString + "}\n\n"
+
+    content[defs['dimension']] += "\nIntroductory text goes here...\n"
+
+    with open("latex/" + function + "_convergence.tex", "r") as f:
+        content[defs['dimension']] += f.read() + "\n"
+
+    content[defs['dimension']] += "\nComments goes here...\n"
+
+    content[defs[
+        'dimension']] += "\subsubsection{Statistical Analysis of The Solutions}\n\label{" + "statisticalanalysis" + functionString + "}\n\n"
+
+    content[defs['dimension']] += "\nIntroductory text goes here...\n"
+
+    with open("latex/" + function + "_function_values.tex", "r") as f:
+        content[defs['dimension']] += f.read() + "\n"
+
+    content[defs['dimension']] += "\nComments goes here...\n"
+
+    content[defs['dimension']] += "\subsubsection{Best Fits}\n\label{" + "bestfits" + functionString + "}\n\n"
+
+    content[defs['dimension']] += "\nIntroductory text goes here...\n"
+
[…]

### 2022-12-13 isolines.py

@@ -49,7 +49,7 @@ for function in constraints:
 
         plt.close('all')
 
-        plt.contour(X, Y, Z, levels=levels, linewidths=[0.3])
+        plt.contour(X, Y, Z, levels=levels, linewidths=[0.5])
 
         for alg_name in algorithms:
 
@@ -63,7 +63,7 @@ for function in constraints:
             y = points[:, 1]
             z = np.array(best_fit["function_values"])
 
-            plt.plot(x, y, label=alg_name, linewidth=0.6)
+            plt.plot(x, y, label=alg_name, linewidth=1)
 
         plt.title(function_names[function])
 

### 2022-12-13 latextablemaker.py

@@ -37,15 +37,43 @@ for function in constraints:
 
     best_fits = []
 
-    column_names = ["Algorithm", "Minimal", "Maximum", "Mean", "Median"]
+    column_names = ["Alg.", "Min", "Max", "Mean", "Median"]
 
-    best_fits_column_names = ["Algorithm", "Solution", "Iterations", "Function Evaluations", "Function Value"]
+    best_fits_column_names = ["Alg.", "Sol.", "Iter.", "F. Eval", "F. Value"]
+
+    solutions_rows = ['$x_{%s}$' % x for x in range(1, defs['dimension']+1)]
+
+    solution_names = list()
+
+    solution_names.append("Coord.")
+
+    solutions = list()
+
+    solutions.append(solutions_rows)
+
+    convergence = list()
+
+    convergence_names = ["Alg.", "Good", "Poor", "Diver.", "Total"]
+
+    index = 1
 
     for alg_name in algorithms:
+
+        good = data[function][alg_name]["design_space"]["good"]['runs']
+
+        poor = data[function][alg_name]["design_space"]["poor"]['runs']
+
+        divergence = data[function][alg_name]["design_space"]["divergence"]['runs']
+
+        overall = data[function][alg_name]["design_space"]["overall"]['runs']
+
+        convergence.append([alg_name, good, poor, divergence, overall])
 
         function_values_data = data[function][alg_name]["design_space"]["overall"]["function_values"]
 
         best_fit_data = data[function][alg_name]["design_space"]["best_fit"]["best_fit_data"]
+
+        solutions.append(best_fit_data["optimal_point"])
 
         function_values.append([alg_name,
                                 function_values_data["fmin"],
@@ -54,25 +82,62 @@ for function in constraints:
                                 function_values_data["fmedian"]])
 
         best_fits.append([alg_name,
-                          ",".join([str(x) for x in best_fit_data["optimal_point"]]),
+                          '$S_{%s}$' % index,
                           best_fit_data["iterations"],
                           best_fit_data["function_evaluations"],
                           best_fit_data["optimal_function_value"]])
 
-    # function_data = np.array(function_values)
+        solution_names.append('$S_{%s}$' % index)
 
-    df = pd.DataFrame(function_values, columns=column_names)
+        index += 1
 
-    content = df.to_latex(index=False)
+    solutions = list(map(list, zip(*solutions)))
+
+    df = pd.DataFrame(function_values,
+                      columns=column_names)
+
+    content = df.to_latex(index=False,
[…]

### 2022-12-13 reports.py

@@ -137,6 +137,12 @@ for function in constraints:
 
             data = extract_data(old_data)
 
+            # convergence_class
+            results[function][alg_name][search_space]['good']['runs'] = len(data['good']['data'])
+            results[function][alg_name][search_space]['poor']['runs'] = len(data['poor']['data'])
+            results[function][alg_name][search_space]['divergence']['runs'] = len(data['divergence']['data'])
+            results[function][alg_name][search_space]['overall']['runs'] = len(old_data['runs']['data'])
+
             #: time elapsed
             results[function][alg_name][search_space]['good']['elapsed_time'] = min_max_avg_std(
                 data['good']['elapsed_time'])

### 2022-12-14 latex/ackley_best_fits.tex
Rewritting latex files

@@
-\begin{table}
+The best solutions of all algorithms for Ackley Function, obtained using the minimal
+distance of the solution, are shown in Table~\ref{solutions:ackley}:
+
+\begin{table}[H]
 \centering
@@
 \end{table}
+
+The Ackley function has a narrow space around the optimal solution and,
+altough specially LMA is of rapid convergence, it iterated 38 times to find
+the optimal value, probably because it walked around the solution
+before reach it. All algorithms were very slow to converge and the most expensive
+are LMA and LBFGS.
+
+Altough the column F. Value points to the the same value, this is a rounded value
+and the real values are os order $10^{-22} \approx 10^{-14}$.

### 2022-12-14 latex/ackley_best_solutions.tex
Rewritting latex files

@@
-\begin{table}
+The best solutions of all algorithms for Ackley Function, indicated as
+$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:ackley}, are shown
+in Table~\ref{detailedsolutions:ackley}:
+
+\begin{table}[H]
 \centering
@@
 \end{table}
+
+The Table~\ref{detailedsolutions:ackley} shows the same solution to all algorithms, because the values are so small
+and were rounded to fit on the Table. The differences of the optimal point are of order $10^{-14}$ to $10^{-22}$,
+for the LMA, DFP, LBFGS and BFGS algorithms, respectively.

### 2022-12-14 latex/ackley_convergence.tex
Rewritting latex files

@@
-\begin{table}
+The convergence report for the Ackley Function is shown in Table~\ref{convergence:ackley}:
+
+\begin{table}[H]
 \centering
@@
 \end{table}
+
+All algorithms converged 100 times, using 100 different initial solutions,
+for a constrained search space of .$[-0.05, 0.05]$. This search space is around
+the optimal solution to avoid wrong convergence to a local minimum.

### 2022-12-14 latex/ackley_function_values.tex
Rewritting latex files

@@
-\begin{table}
+The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:ackley}:
+
+\begin{table}[H]
 \centering
@@
 \end{table}
+
+The values again are rounded. The matter is the mdian value: it informs us the result that
+we are like to obtain when running any algorithm to solve for minimum. As it seems, for all
+algorithms is expected to find the minimun of Ackley Function.

### 2022-12-14 latex/beale_best_fits.tex
Added build to main latex file
Rewritting latex files

@@
+The best solutions of all algorithms for Beale Function, obtained using the minimal
+distance of the solution, are shown in Table~\ref{solutions:beale}:
+
+\begin{table}[H]
+\centering
+\caption{Best Fits For Beale Function}
+\label{solutions:beale}
 \begin{tabular}{llrrr}
 \toprule
-Algorithm &                               Solution &  Iterations &  Function Evaluations &  Function Value \\
+ Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
 \midrule
-      dfp &  2.9999999997259486,0.4999999999232928 &           8 &                    10 &    1.378756e-20 \\
-     bfgs &   3.000000000000004,0.5000000000000007 &          15 &                    18 &    8.125884e-30 \\
-    lbfgs &  3.0000000003576988,0.5000000000625404 &          14 &                    50 &    3.625854e-20 \\
-      lma & 2.9999997171743287,0.49999992960730744 &          12 &                    13 &    1.280491e-14 \\
+  dfp & $S_{1}$ &      8 &       10 &      0.00 \\
+ bfgs & $S_{2}$ &     15 &       18 &      0.00 \\
+lbfgs & $S_{3}$ &     14 &       50 &      0.00 \\
+  lma & $S_{4}$ &     12 &       13 &      0.00 \\
 \bottomrule
 \end{tabular}
+\end{table}
+
+The Beale function has a very large search space around the optimal solution and
+it had a reasonable number of iterations for each algorithm. The DFP method, superseeded by BFGS,
+is surprisingly rapid to find the solution. The LMA, known to be fast, had a reasonable performance.
+BFGS/LBFGS performed as expected.
+
+Altough the column F. Value points to the the same value, this is a rounded value
+and the real values are os order $10^{-22} \approx 10^{-14}$.

### 2022-12-14 latex/beale_best_solutions.tex
Added build to main latex file
Rewritting latex files

--- 2022-12-13 latex/ackley_best_solutions.tex
@@
-\begin{table}
+The best solutions of all algorithms for Beale Function, indicated as
+$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:beale}, are shown
+in Table~\ref{detailedsolutions:beale}:
+
+\begin{table}[H]
 \centering
-\caption{Detailed Solutions For Ackley Function}
-\label{detailedsolutions:ackley}
+\caption{Detailed Solutions For Beale Function}
+\label{detailedsolutions:beale}
 \begin{tabular}{lrrrr}
@@
 \midrule
-$x_{1}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
-$x_{2}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
+$x_{1}$ &     3.00 &     3.00 &     3.00 &     3.00 \\
+$x_{2}$ &     0.50 &     0.50 &     0.50 &     0.50 \\
 \bottomrule
@@
 \end{table}
+
+The optimal solution for Beale Function is $[3, 0.5]$ and the rounded values
+of Table~\ref{detailedsolutions:beale} points to the same value. The error of
+these values are of order $10^{-13}$ os less.

### 2022-12-14 latex/beale_convergence.tex
Rewritting latex files

@@
-\begin{table}
+The convergence report for the Beale Function is shown in Table~\ref{convergence:beale}:
+
+\begin{table}[H]
 \centering
@@
 \end{table}
+
+The Table~\ref{convergence:beale} show that not any algorithm
+is capable to solve any problem. LMA had the worst performance
+in good convergence, followed by DFP, BGFS and LBGFS. LBFGS has
+a performance of 80\% in convergence.

### 2022-12-14 latex/beale_function_values.tex
Rewritting latex files

@@
-\begin{table}
+The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:beale}:
+
+\begin{table}[H]
 \centering
@@
 \end{table}
+
+LMA again had the worst performance. It is the only algorithm that, altiugh has some solutions in
+poor convergence, that has a median greater than zero. LBFGS and DFP seems quite radical in terms
+of convergence, while having a median of zero its mean values are greater than zero an its maximal
+value are noticeable. The larger mean value of LMA reinforces the notion of divergence in this case
+and signifies that the algorithm don't fit very well for BEale Fnction minimum.

### 2022-12-14 latex/header.tex
Rewritting latex files

--- 2022-12-11 paper/new/CW01.tex
@@
 \usepackage{multicol}
+\usepackage{float}
 \usepackage[english]{babel}
 \usepackage[T1]{fontenc}
-
+\usepackage{booktabs}
+\restylefloat{table}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\newcommand\norm[1]{\left\Vert#1\right\Vert}
 \begin{document}
-
 \title{Quasi-Newton Methods Comparision using Ackley, Beale, Booth, Matyas, Rastrigin and RosenBrock Functions}
 \author{
-	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3}, Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}
-	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143 - augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403 -  caiomizerkowski@gmail.com} \IEEEauthorblockA{\IEEEauthorrefmark{3}GRR20172197 - christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957 - eduardo.reis02@gmail.com}
+	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3} and Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}\\
+	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com,\\ \IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
 }
-
-\markboth
-{Adams \headeretal: Quasi-Newton Methods Comparision using Ackley, Beale, Booth, Matyas, Rastrigin and RosenBrock Functions}
-{Adams \headeretal: Quasi-Newton Methods Comparision using Ackley, Beale, Booth, Matyas, Rastrigin and RosenBrock Functions}
 
@@
 \begin{abstract}
-This paper discusses briefly four popular algorithms to solve optimization/minimization problems, beloginging to Quasi-Newton class: \textit{Davidon–Fletcher–Powell} (DFP), \textit{Broyden–Fletcher–Goldfarb–Shanno} (BFGS), limited memory BFGS and \textit{Levenberg-Marquardt Algorithm} (LMA).
+	This paper discusses briefly four popular algorithms to solve optimization/minimization problems, beloginging to Quasi-Newton class: \textit{Davidon–Fletcher–Powell} (DFP), \textit{Broyden–Fletcher–Goldfarb–Shanno} (BFGS), \textit{limited memory BFGS} and \textit{Levenberg-Marquardt Algorithm} (LMA).
 These algorithms are implemented in \textit{Python language}, version 3.10 and uses \textit{SymPy}, \textit{SciPy} and \textit{NumPy} libraries.
 One of them, \textit{BFGS}, is implemented natively on the  \textit{SciPy} library and the rest are implemented by hand to provide useful insights about the inner operation of the algorithms.
-The results are, however, very corrent with a few exceptions.
+The results are, however, very surprising with a few exceptions: when the initial solution is placed in a region near the global minimum, almost all algorithms converges very quickly and the convergence becomes unpredictable when the initial solution is placed randomly in the search space.
 \end{abstract}
 
-\begin{IEEEkeywords}Optimization Problem; Linear Programming; Non-linear Programming; Quasi-Newton Algorithms\end{IEEEkeywords}
+\begin{IEEEkeywords}
+	Optimization Methods, Quasi-Newton, Second Order Optimization,  Non-linear Programming
+\end{IEEEkeywords}
 
 \section{Introduction}
+\label{sec:introduction}
 
-\section{Methodology}
+Quasi-Newton methods are methods used to find zeros or local maxima and minima of functions, as a viable alternative to Newton's method.
+They are generally used if the Jacobian or Hessian is not available or is too expensive to compute at each iteration.
+Strictly speaking, Newton's method requires the Jacobian to look for zeros, or the Hessian to find extrema, while quasi-Newton methods estimate the Jacobian or Hessian to perform such tasks.
 
-\section{Results}
+In this paper, three popular alternatives of true \textit{Quasi-Newton} methods are evaluated to find function minima: \textit{Davidon–Fletcher–Powell} (DFP), \textit{Broyden–Fletcher–Goldfarb–Shanno} (BFGS) and \textit{limited memory BFGS} (LBFGS).
+The fourth method, the \textit{Levenberg-Marquardt Algorithm} (LMA) is a hybrid method that makes use of a weighting procedure between the steepest descent algorithm and Newton's method to obtain advantages from both methods.
 
-\subsection{Ackley Function}
+The four methods were implemented using the Python language, based on the SciPy, NumPy and SimPy packages.
+The SciPy package already contains standard procedures for numerical optimization and uses the NumPy package for its internal operations.
+The SymPy package is used to assemble the test functions and is very convenient for differentiation of functions.
+The LBGFS, DFP and LMA methods, although they have native versions within the SciPy package, were implemented manually following SciPy conventions because the native versions do not support data collection of iterations and/or expect different parameters from the original proposal, such as LMA.
+The description of the manually implemented algorithms can be seen in the book Engineering Optimization by Singiresu Rao, Fifth Edition, except for LBFGS.
+The LBFGS algorithm was taken from GitHUB, in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.
 
-\input{latex/ackley_best_fits.tex}
+All algorithms were tested using the following parameters:
 
-\input{latex/ackley_function_values.tex}
+\begin{itemize}
+	\item \textit{Number of initial Solutions:} 100
+	\item \textit{Máximum Iterations:} 4000
+	\item \textit{Tolerance (Convergence Criterion): } $1 \times 10^{-9}$
+\end{itemize}
 
-\end{document}
+The initial solutions of all function were taken near the global minimum to avoid wrong convergence to a local minimum, since these algorithms don't differentiate a local minimum from a global minimum.
+It is assumed that the global minimum is a \textit{strong global minimum}, that is, a unique minimal point.
+For LMA, it is assumed that the initial step is fixed and does not take in consideration any information about the function/problem.
+All algorithms are unsconstrained and, while the initial solution is probably near the optimal solution, there's much room for divergence.
+
+The algorithms were evaluated using the folowing criteria:
+
+\begin{itemize}
+	\item \textit{Convergence: } the convergence of an algorithm is classified as good, por and divergence.
+	\subitem \textit{Good convergence: } the final solution is really near the optimal solution within the max iterations;
+	\subitem \textit{Poor convergence: } the final solution is far from the optimal solution for any reason;
+	\subitem \textit{Divergence: }  the final solution is out of the funtion's search space;
+	\item \textit{Statistical Parameters about the solutions:} Mean and Median of the solutions are analysed to provide insights about the algorithms;
+	\item Iterations to converge, function evaluations and function values.
+\end{itemize}

### 2022-12-14 paper/new/article.tex
Rewritting latex files

@@
-\documentclass{ieeeaccess}
+\documentclass[conference]{IEEEtran}
+\IEEEoverridecommandlockouts
+% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
 \usepackage{cite}
 \usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
+\usepackage{mathtools}
+\usepackage{algpseudocode}
+\usepackage{algorithm}
+\usepackage{algorithmicx}
+\usepackage{microtype}
+\usepackage{float}
+\usepackage{adjustbox}
+\usepackage{booktabs,makecell,tabularx}
 \usepackage{graphicx}
 \usepackage{textcomp}
+\usepackage{verbatim}
+\usepackage{xcolor}
+\usepackage{graphics} % for pdf, bitmapped graphics files
+\usepackage{epsfig} % for postscript graphics files
+\usepackage{mathptmx} % assumes new font selection scheme installed
+\usepackage{multicol}
+\usepackage{float}
+\usepackage[english]{babel}
+\usepackage[T1]{fontenc}
 \usepackage{booktabs}
+\restylefloat{table}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \begin{document}
-\history{Unpublished, First Preview}
-\doi{Unpublished/NoDOIInformation}
 \title{Quasi-Newton Methods Comparision using Ackley, Beale, Booth, Matyas, Rastrigin and RosenBrock Functions}
 \author{
-	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}}
-    \IEEEauthorblockN{Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}}
-    \IEEEauthorblockN{Christian Piltz Araújo\IEEEauthorrefmark{3}}
-    \IEEEauthorblockN{Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}
-	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br}
-	\IEEEauthorblockA{\IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com}
-	\IEEEauthorblockA{\IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br}
-	\IEEEauthorblockA{\IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
+	\IEEEauthorblockN{Augusto Mathias Adams\IEEEauthorrefmark{1}, Caio Phillipe Mizerkowski\IEEEauthorrefmark{2}, Christian Piltz Araújo\IEEEauthorrefmark{3} and Vinicius Eduardo dos Reis\IEEEauthorrefmark{4}}\\
+	\IEEEauthorblockA{\IEEEauthorrefmark{1}GRR20172143, augusto.adams@ufpr.br, \IEEEauthorrefmark{2}GRR20166403, caiomizerkowski@gmail.com,\\ \IEEEauthorrefmark{3}GRR20172197, christian0294@yahoo.com.br, \IEEEauthorrefmark{4}GRR20175957, eduardo.reis02@gmail.com}
 }
 
-\markboth
-{Adams \headeretal: Quasi-Newton Methods Comparision using Ackley, Beale, Booth, Matyas, Rastrigin and RosenBrock Functions}
-{Adams \headeretal: Quasi-Newton Methods Comparision using Ackley, Beale, Booth, Matyas, Rastrigin and RosenBrock Functions}
-
-\corresp{Corresponding author: Augusto Mathias Adams (e-mail: augusto.adams@ufpr.br).}
+\maketitle
+
 \begin{abstract}
-This paper discusses briefly four popular algorithms to solve optimization/minimization problems, beloginging to Quasi-Newton class: \textit{Davidon–Fletcher–Powell} (DFP), \textit{Broyden–Fletcher–Goldfarb–Shanno} (BFGS), limited memory BFGS and \textit{Levenberg-Marquardt Algorithm} (LMA).
+	This paper discusses briefly four popular algorithms to solve optimization/minimization problems, beloginging to Quasi-Newton class: \textit{Davidon–Fletcher–Powell} (DFP), \textit{Broyden–Fletcher–Goldfarb–Shanno} (BFGS), \textit{limited memory BFGS} and \textit{Levenberg-Marquardt Algorithm} (LMA).
 These algorithms are implemented in \textit{Python language}, version 3.10 and uses \textit{SymPy}, \textit{SciPy} and \textit{NumPy} libraries.
 One of them, \textit{BFGS}, is implemented natively on the  \textit{SciPy} library and the rest are implemented by hand to provide useful insights about the inner operation of the algorithms.
-The results are, however, very surprising with a few exceptions: when the initial solution is placed in a region near the global minimum, almost all algorithms converges very quickly, so, a study was made to limit the initial solution to  these regions.
-With exception of
+The results are, however, very surprising with a few exceptions: when the initial solution is placed in a region near the global minimum, almost all algorithms converges very quickly and the convergence becomes unpredictable when the initial solution is placed randomly in the search space.
 \end{abstract}
 
-\begin{keywords} 
-Optimization Methods, Quasi-Newton, Non-linear Programming
-\end{keywords}
-
-\titlepgskip=-15pt
-
-\maketitle
+\begin{IEEEkeywords}
+	Optimization Methods, Quasi-Newton, Second Order Optimization,  Non-linear Programming
+\end{IEEEkeywords}
 
@@
 \label{sec:introduction}
+
+Quasi-Newton methods are methods used to find zeros or local maxima and minima of functions, as a viable alternative to Newton's method.
+They are generally used if the Jacobian or Hessian is not available or is too expensive to compute at each iteration.
+Strictly speaking, Newton's method requires the Jacobian to look for zeros, or the Hessian to find extrema, while quasi-Newton methods estimate the Jacobian or Hessian to perform such tasks.
+
+In this paper, three popular alternatives of true \textit{Quasi-Newton} methods are evaluated to find function minima: \textit{Davidon–Fletcher–Powell} (DFP), \textit{Broyden–Fletcher–Goldfarb–Shanno} (BFGS) and \textit{limited memory BFGS} (LBFGS).
+The fourth method, the \textit{Levenberg-Marquardt Algorithm} (LMA) is a hybrid method that makes use of a weighting procedure between the steepest descent algorithm and Newton's method to obtain advantages from both methods.
+
+The four methods were implemented using the Python language, based on the SciPy, NumPy and SimPy packages.
+The SciPy package already contains standard procedures for numerical optimization and uses the NumPy package for its internal operations.
+The SymPy package is used to assemble the test functions and is very convenient for differentiation of functions.
+The LBGFS, DFP and LMA methods, although they have native versions within the SciPy package, were implemented manually following SciPy conventions because the native versions do not support data collection of iterations and/or expect different parameters from the original proposal, such as LMA.
+The description of the manually implemented algorithms can be seen in the book Engineering Optimization by Singiresu Rao, Fifth Edition, except for LBFGS.
+The LBFGS algorithm was taken from GitHUB, in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.
+
+All algorithms were tested using the following parameters:
+
+\begin{itemize}
+	\item \textit{Number of initial Solutions:} 100
+	\item \textit{Máximum Iterations:} 4000
+	\item \textit{Tolerance (Convergence Criterion): } $1 \times 10^{-9}$
+\end{itemize}
+
+The initial solutions of all function were taken near the global minimum to avoid wrong convergence to a local minimum, since these algorithms don't differentiate a local minimum from a global minimum.
+It is assumed that the global minimum is a \textit{strong global minimum}, that is, a unique minimal point.
+For LMA, it is assumed that the initial step is fixed and does not take in consideration any information about the function/problem.
+All algorithms are unsconstrained and, while the initial solution is probably near the optimal solution, there's much room for divergence.
+
+The algorithms were evaluated using the folowing criteria:
+
+\begin{itemize}
+	\item \textit{Convergence: } the convergence of an algorithm is classified as good, por and divergence.
+	\subitem \textit{Good convergence: } the final solution is really near the optimal solution within the max iterations;
+	\subitem \textit{Poor convergence: } the final solution is far from the optimal solution for any reason;
+	\subitem \textit{Divergence: }  the final solution is out of the funtion's search space;
+	\item \textit{Statistical Parameters about the solutions:} Mean and Median of the solutions are analysed to provide insights about the algorithms;
+	\item Iterations to converge, function evaluations and function values.
+\end{itemize}
+
 \section{2D Function versions}
@@
 
-Introductory text goes here...
-\begin{table}
+The convergence report for the Ackley Function is shown in Table~\ref{convergence:ackley}:
+
+\begin{table}[H]
 \centering
@@
 
-Comments goes here...
+All algorithms converged 100 times, using 100 different initial solutions,
+for a constrained search space of .$[-0.05, 0.05]$. This search space is around
+the optimal solution to avoid wrong convergence to a local minimum.
+
 \subsubsection{Statistical Analysis of The Solutions}
@@
 
-Introductory text goes here...
-\begin{table}
+The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:ackley}:
+
+\begin{table}[H]
 \centering
@@
 
-Comments goes here...
+The values again are rounded. The matter is the mdian value: it informs us the result that
+we are like to obtain when running any algorithm to solve for minimum. As it seems, for all
+algorithms is expected to find the minimun of Ackley Function.
+
 \subsubsection{Best Fits}
@@
 
-Introductory text goes here...
-\begin{table}
+The best solutions of all algorithms for Ackley Function, obtained using the minimal
+distance of the solution, are shown in Table~\ref{solutions:ackley}:
+
+\begin{table}[H]
 \centering
@@
 
-Comments goes here...
-\begin{table}
+The Ackley function has a narrow space around the optimal solution and,
+altough specially LMA is of rapid convergence, it iterated 38 times to find
+the optimal value, probably because it walked around the solution
+before reach it. All algorithms were very slow to converge and the most expensive
+are LMA and LBFGS.
+
+Altough the column F. Value points to the the same value, this is a rounded value
+and the real values are os order $10^{-22} \approx 10^{-14}$.
+
+The best solutions of all algorithms for Ackley Function, indicated as
+$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:ackley}, are shown
+in Table~\ref{detailedsolutions:ackley}:
+
+\begin{table}[H]
 \centering
@@
 
-Comments goes here...
+The Table~\ref{detailedsolutions:ackley} shows the same solution to all algorithms, because the values are so small
+and were rounded to fit on the Table. The differences of the optimal point are of order $10^{-14}$ to $10^{-22}$,
+for the LMA, DFP, LBFGS and BFGS algorithms, respectively.
+
 \subsubsection{Isolines and Convergence line}
@@
 
-Introductory text goes here...
-\begin{figure}[h]
-\centering
-\includegraphics[scale=0.5]{images/ackley.jpg}
+\begin{figure}[H]
+\centering
 \caption{Isolines and convergence line for Ackley Function}
 \label{fig:ackley}
+\includegraphics[scale=0.5]{images/ackley.jpg}
 \end{figure}
-
-Comments goes here...
 \subsection{Beale Function}
@@
 
-Introductory text goes here...
-\begin{table}
+The convergence report for the Beale Function is shown in Table~\ref{convergence:beale}:
+
+\begin{table}[H]
 \centering
@@
 
-Comments goes here...
+The Table~\ref{convergence:beale} show that not any algorithm
+is capable to solve any problem. LMA had the worst performance
+in good convergence, followed by DFP, BGFS and LBGFS. LBFGS has
+a performance of 80\% in convergence.
+
 \subsubsection{Statistical Analysis of The Solutions}
@@
 
-Introductory text goes here...
-\begin{table}
+The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:beale}:
+
+\begin{table}[H]
 \centering
@@
 
-Comments goes here...
+LMA again had the worst performance. It is the only algorithm that, altiugh has some solutions in
+poor convergence, that has a median greater than zero. LBFGS and DFP seems quite radical in terms
+of convergence, while having a median of zero its mean values are greater than zero an its maximal
+value are noticeable. The larger mean value of LMA reinforces the notion of divergence in this case
+and signifies that the algorithm don't fit very well for BEale Fnction minimum.
+
 \subsubsection{Best Fits}
@@
 
-Introductory text goes here...
-\begin{table}
+The best solutions of all algorithms for Beale Function, obtained using the minimal
+distance of the solution, are shown in Table~\ref{solutions:beale}:
+
+\begin{table}[H]
 \centering
@@
 
-Comments goes here...
-\begin{table}
+The Ackley function has a very large search space around the optimal solution and
+it had a reasonable number of iterations for each algorithm. The DFP method, superseeded by BFGS,
+is surprisingly rapid to find the solution. The LMA, known to be fast, had a reasonable performance.
+BFGS/LBFGS performed as expected.
+
+Altough the column F. Value points to the the same value, this is a rounded value
+and the real values are os order $10^{-22} \approx 10^{-14}$.
+
+The best solutions of all algorithms for Beale Function, indicated as
+$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:beale}, are shown
+in Table~\ref{detailedsolutions:beale}:
+
+\begin{table}[H]
 \centering
@@
 
-Comments goes here...
+The optimal solution for Beale Function is $[3, 0.5]$ and the rounded values
+of Table~\ref{detailedsolutions:beale} points to the same value. The error of
+these values are of order $10^{-13}$ os less.
+
 \subsubsection{Isolines and Convergence line}
@@
 
-Introductory text goes here...
-\begin{figure}[h]
-\centering
-\includegraphics[scale=0.5]{images/beale.jpg}
+\begin{figure}[H]
+\centering
 \caption{Isolines and convergence line for Beale Function}
 \label{fig:beale}
+\includegraphics[scale=0.5]{images/beale.jpg}
 \end{figure}
-
-Comments goes here...
 \subsection{Booth Function}
@@
 
-Introductory text goes here...
-\begin{table}
+\begin{table}[H]
 \centering
@@
 
-Comments goes here...
 \subsubsection{Statistical Analysis of The Solutions}
@@
 
-Comments goes here...
 \subsubsection{Best Fits}
@@
 
-Comments goes here...
-\begin{table}
+\begin{table}[H]
 \centering
@@
 
-Comments goes here...
 \subsubsection{Isolines and Convergence line}
@@
 
-Introductory text goes here...
-\begin{figure}[h]
-\centering
-\includegraphics[scale=0.5]{images/booth.jpg}
+\begin{figure}[H]
+\centering
 \caption{Isolines and convergence line for Booth Function}
 \label{fig:booth}
+\includegraphics[scale=0.5]{images/booth.jpg}
 \end{figure}
-
-Comments goes here...
 \subsection{Matyas Function}
@@
 
-Introductory text goes here...
-\begin{figure}[h]
-\centering
-\includegraphics[scale=0.5]{images/matyas.jpg}
+\begin{figure}[H]
+\centering
 \caption{Isolines and convergence line for Matyas Function}
 \label{fig:matyas}
+\includegraphics[scale=0.5]{images/matyas.jpg}
 \end{figure}
-
-Comments goes here...
 \subsection{Rastrigin Function}
@@
 
-Introductory text goes here...
-\begin{figure}[h]
-\centering
-\includegraphics[scale=0.5]{images/rastrigin2d.jpg}
+\begin{figure}[H]
+\centering
 \caption{Isolines and convergence line for Rastrigin Function}
 \label{fig:rastrigin2d}
+\includegraphics[scale=0.5]{images/rastrigin2d.jpg}
 \end{figure}
-
-Comments goes here...
 \subsection{Rosenbrock Function}
@@
 
-Introductory text goes here...
-\begin{figure}[h]
-\centering
-\includegraphics[scale=0.5]{images/rosenbrock2d.jpg}
+\begin{figure}[H]
+\centering
 \caption{Isolines and convergence line for Rosenbrock Function}
 \label{fig:rosenbrock2d}
+\includegraphics[scale=0.5]{images/rosenbrock2d.jpg}
 \end{figure}
-
-Comments goes here...
 
@@
 
-Comments goes here...
 \subsection{Rosenbrock Function}
@@
 
-Comments goes here...
-
 \section{30D Function versions}
@@
 
-Comments goes here...
-
-\EOD
-
 \end{document}

### 2022-12-14 build_main_latex_file.py

@@ -40,36 +40,22 @@ for function in constraints:
     content[
         defs['dimension']] += "\subsubsection{Convergence Analysis}\n\label{" + "convergence" + functionString + "}\n\n"
 
-    content[defs['dimension']] += "\nIntroductory text goes here...\n"
-
     with open("latex/" + function + "_convergence.tex", "r") as f:
         content[defs['dimension']] += f.read() + "\n"
-
-    content[defs['dimension']] += "\nComments goes here...\n"
 
     content[defs[
         'dimension']] += "\subsubsection{Statistical Analysis of The Solutions}\n\label{" + "statisticalanalysis" + functionString + "}\n\n"
 
-    content[defs['dimension']] += "\nIntroductory text goes here...\n"
-
     with open("latex/" + function + "_function_values.tex", "r") as f:
         content[defs['dimension']] += f.read() + "\n"
 
-    content[defs['dimension']] += "\nComments goes here...\n"
-
     content[defs['dimension']] += "\subsubsection{Best Fits}\n\label{" + "bestfits" + functionString + "}\n\n"
-
-    content[defs['dimension']] += "\nIntroductory text goes here...\n"
 
     with open("latex/" + function + "_best_fits.tex", "r") as f:
         content[defs['dimension']] += f.read() + "\n"
 
-    content[defs['dimension']] += "\nComments goes here...\n"
-
     with open("latex/" + function + "_best_solutions.tex", "r") as f:
         content[defs['dimension']] += f.read() + "\n"
-
-    content[defs['dimension']] += "\nComments goes here...\n"
 
     if defs['dimension'] == 2:
         # isolines
@@ -77,17 +63,13 @@ for function in constraints:
         content[defs[
             'dimension']] += "\subsubsection{Isolines and Convergence line}\n\label{" + "isolines" + functionString + "}\n\n"
 
-        content[defs['dimension']] += "\nIntroductory text goes here...\n"
-
-        content[defs['dimension']] += """\\begin{figure}[h]
+        content[defs['dimension']] += """\\begin{figure}[H]
 \\centering
-\\includegraphics[scale=0.5]{images/""" + function + """.jpg}
 \\caption{Isolines and convergence line for """ + functionName + """}
 \\label{fig:""" + function + """}
+\\includegraphics[scale=0.5]{images/""" + function + """.jpg}
 \\end{figure}
 """
-
-        content[defs['dimension']] += "\nComments goes here...\n"
 
 with open(header_file, "r") as f:
     header = f.read()

### 2022-12-15 paper/new/article.tex
Work on article

@@
 \begin{abstract}
-	This paper discusses briefly four popular algorithms to solve optimization/minimization problems, beloginging to Quasi-Newton class: \textit{Davidon–Fletcher–Powell} (DFP), \textit{Broyden–Fletcher–Goldfarb–Shanno} (BFGS), \textit{limited memory BFGS} and \textit{Levenberg-Marquardt Algorithm} (LMA).
-These algorithms are implemented in \textit{Python language}, version 3.10 and uses \textit{SymPy}, \textit{SciPy} and \textit{NumPy} libraries.
-One of them, \textit{BFGS}, is implemented natively on the  \textit{SciPy} library and the rest are implemented by hand to provide useful insights about the inner operation of the algorithms.
-The results are, however, very surprising with a few exceptions: when the initial solution is placed in a region near the global minimum, almost all algorithms converges very quickly and the convergence becomes unpredictable when the initial solution is placed randomly in the search space.
+	This paper discusses briefly four popular algorithms to solve optimization/minimization problems, beloginging to Quasi-Newton class: \textit{Davidon–Fletcher–Powel
+
+		 is placed in a region near the global minimum, almost all algorithms converges very quickly and the convergence becomes unpredictable when the initial solution is placed randomly in the search space.
 \end{abstract}

### 2022-12-19 paper/new/article.tex
Work update

--- 2022-12-14 paper/new/article.tex
@@
 
-\begin{figure}[H]
+The isolines of Ackley Function and convergence lines for all algorithms are shown in Figure~\ref{fig:ackley}:\begin{figure}[H]
 \centering
@@
 \end{figure}
-\subsection{Beale Function}
+The isolines for Ackley Function shows that there are at least 4 pitfalls near ther optimal solution, so, the search space needs to be reduced to \$[-0.05, 0.05]\$ to avoid wrong convergence.
+All the algorithms converges quite smoothly following a straight line\subsection{Beale Function}
 \label{beale2D}
@@
 
-The Ackley function has a very large search space around the optimal solution and
+The Beale function has a very large search space around the optimal solution and
 it had a reasonable number of iterations for each algorithm. The DFP method, superseeded by BFGS,
@@
 
-\begin{figure}[H]
+The isolines of Beale Function and convergence lines for all algorithms are shown i Figure~\ref{fig:beale}:\begin{figure}[H]
 \centering
@@
 \end{figure}
-\subsection{Booth Function}
+The isolines for Beale Function shows that there are a large plateau near the solution.
+For an unknown reason the best algorithm had 80\% of performance at its best.
+Quasi-Newton algorithms suffers to converge when the gradient is less significant.\subsection{Booth Function}
 \label{booth2D}
@@
 
+The best solutions of all algorithms for Booth Function, obtained using the minimal
+distance of the solution, are shown in Table~\ref{solutions:booth}:
 \begin{table}[H]
@@
 \end{table}
+
+Altough the column F. Value points to the the same value, this is a rounded value
+and the real values are os order $10^{-22} \approx 10^{-14}$.
 

### 2022-12-19 Solvers/common.py

@@ -93,6 +93,7 @@ def generate_random_sequence(seed, lmin, lmax, n):
 Objective function, gradient and hessian analytical and estimation procedures
 """
 
+
 def evaluate_objective_function(f, xvec, stats):
     """
     Function Evaluation
@@ -136,4 +137,3 @@ def compute_hessian(hessF, x, stats):
         stats['hessian_function_calls'] = 0
     stats['hessian_function_calls'] += 1
     return np.array(hessF(*x))
-

### 2022-12-19 build_main_latex_file.py

@@ -14,6 +14,19 @@ header_file = "latex/header.tex"
 
 footer_file = "latex/footer.tex"
 
+image_comments = {'ackley': ["The isolines of Ackley Function and convergence lines for all algorithms "
+                             "are shown in Figure~\\ref{fig:ackley}:",
+                            "The isolines for Ackley Function shows that there are at least 4 pitfalls"
+                            " near ther optimal solution, so, the search space needs to be reduced to "
+                            "\$[-0.05, 0.05]\$ to avoid wrong convergence. All the algorithms converges "
+                            "quite smoothly following a straight line"],
+                  "beale": ["The isolines of Beale Function and convergence lines for all algorithms "
+                             "are shown i Figure~\\ref{fig:beale}:",
+                            "The isolines for Beale Function shows that there are a large plateau near "
+                            "the solution. For an unknown reason the best algorithm had 80\% of performance"
+                            " at its best. Quasi-Newton algorithms suffers to converge when the gradient is"
+                            " less significant."]}
+
 content = dict()
 
 content[2] = "\section{2D Function versions}\n\label{functions2D}\n\n"
@@ -63,6 +76,12 @@ for function in constraints:
         content[defs[
             'dimension']] += "\subsubsection{Isolines and Convergence line}\n\label{" + "isolines" + functionString + "}\n\n"
 
+        if function in image_comments:
+            content[defs[
+                'dimension']] += image_comments[function][0]
+
+
+
         content[defs['dimension']] += """\\begin{figure}[H]
 \\centering
 \\caption{Isolines and convergence line for """ + functionName + """}
@@ -70,6 +89,10 @@ for function in constraints:
 \\includegraphics[scale=0.5]{images/""" + function + """.jpg}
 \\end{figure}
 """
+
+        if function in image_comments:
+            content[defs[
+                'dimension']] += image_comments[function][1]
 
 with open(header_file, "r") as f:
     header = f.read()

### 2022-12-19 latex/ackley_best_fits.tex
Initial Versioning of Article and Latex Builder

--- 2022-12-13 latex/ackley_best_fits.tex
@@
 \end{table}
+
+The Ackley function has a narrow space around the optimal solution and,
+although specially LMA is of rapid convergence, it iterated 38 times to find
+the optimal value. All algorithms were very slow to converge and the most expensive
+are LMA and LBFGS.
+
+Although the column F. Value points to the the same value, this is a rounded value
+and the real values are of order $10^{-22} \approx 10^{-14}$.

### 2022-12-19 latex/ackley_convergence.tex
Initial Versioning of Article and Latex Builder

@@
 All algorithms converged 100 times, using 100 different initial solutions,
-for a constrained search space of .$[-0.05, 0.05]$. This search space is around
-the optimal solution to avoid wrong convergence to a local minimum.
+for a constrained search space of $\left[-0.05, 0.05\right]$ . This search space is around
+the optimal solution to avoid wrong convergence to a local minimum. In this search space,
+Ackley Function has a well defined valley that has the solution as its center, as is shown in
+Section~\ref{isolinesackley2D}.

### 2022-12-19 latex/beale_best_fits.tex
Initial Versioning of Article and Latex Builder

@@
 it had a reasonable number of iterations for each algorithm. The DFP method, superseeded by BFGS,
-is surprisingly rapid to find the solution. The LMA, known to be fast, had a reasonable performance.
+is surprisingly fast to find the solution. The LMA, known to be fast, had a reasonable performance.
 BFGS/LBFGS performed as expected.
 
-Altough the column F. Value points to the the same value, this is a rounded value
-and the real values are os order $10^{-22} \approx 10^{-14}$.
+Although the column F. Value points to the the same value, this is a rounded value
+and the real values are of order $10^{-22} \approx 10^{-14}$.

### 2022-12-19 latex/beale_function_values.tex
Initial Versioning of Article and Latex Builder

@@
 
-LMA again had the worst performance. It is the only algorithm that, altiugh has some solutions in
+LMA again had the worst performance. It is the only algorithm that, although has some solutions in
 poor convergence, that has a median greater than zero. LBFGS and DFP seems quite radical in terms
@@
 value are noticeable. The larger mean value of LMA reinforces the notion of divergence in this case
-and signifies that the algorithm don't fit very well for BEale Fnction minimum.
+and signifies that the algorithm don't fit very well for the Beale Function minimum.

### 2022-12-19 latex/booth_best_solutions.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

--- 2022-12-13 latex/ackley_best_solutions.tex
@@
-\begin{table}
+The best solutions of all algorithms for Beale Function, indicated as
+$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:booth}, are shown
+in Table~\ref{detailedsolutions:booth}:
+
+\begin{table}[H]
 \centering
-\caption{Detailed Solutions For Ackley Function}
-\label{detailedsolutions:ackley}
+\caption{Detailed Solutions For Booth Function}
+\label{detailedsolutions:booth}
 \begin{tabular}{lrrrr}
@@
 \midrule
-$x_{1}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
-$x_{2}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
+$x_{1}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
+$x_{2}$ &     3.00 &     3.00 &     3.00 &     3.00 \\
 \bottomrule
@@
 \end{table}
+
+The optimal solution for Booth Function is $\left[1, 3\right]$ and the rounded values
+of Table~\ref{detailedsolutions:booth} points to the same value. The error of
+these values are of order $10^{-13}$ os less.

### 2022-12-19 latex/booth_convergence.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

--- 2022-12-13 latex/ackley_convergence.tex
@@
-\begin{table}
+The convergence report for the Booth Function is shown in Table~\ref{convergence:booth}:
+
+\begin{table}[H]
 \centering
-\caption{Convergence Report For Ackley Function}
-\label{convergence:ackley}
+\caption{Convergence Report For Booth Function}
+\label{convergence:booth}
 \begin{tabular}{lrrrr}
@@
 \end{table}
+
+All algorithms converged 100 times, using 100 different initial solutions,
+for a constrained search space of $\left[0, 4\right]$ . This search space is around
+the optimal solution to avoid wrong convergence to a local minimum. In this search space,
+Booth Function has a well defined valley that has the solution as its center, as it is shown
+in Section~\ref{isolinesbooth2D}.

### 2022-12-19 latex/booth_function_values.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

--- 2022-12-13 latex/ackley_function_values.tex
@@
-\begin{table}
+The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:beale}:
+
+\begin{table}[H]
 \centering
-\caption{Statistical Information about function values For Ackley Function}
-\label{function_values:ackley}
+\caption{Statistical Information about function values For Booth Function}
+\label{function_values:booth}
 \begin{tabular}{lrrrr}
@@
 \end{table}
+
+The values again are rounded. The median informs us that, for all
+algorithms is expected to find the minimun of Booth Function.

### 2022-12-19 latex/header.tex
Initial Versioning of Article and Latex Builder

@@
 \begin{itemize}
-	\item \textit{Convergence: } the convergence of an algorithm is classified as good, por and divergence.
+	\item \textit{Convergence: } the convergence of an algorithm is classified as \textit{good}, \textit{poor} and \textit{divergence}.
 	\subitem \textit{Good convergence: } the final solution is really near the optimal solution within the max iterations;
 	\subitem \textit{Poor convergence: } the final solution is far from the optimal solution for any reason;
-	\subitem \textit{Divergence: }  the final solution is out of the funtion's search space;
+	\subitem \textit{Divergence: }  the final solution is out of the function's search space;
 	\item \textit{Statistical Parameters about the solutions:} Mean and Median of the solutions are analysed to provide insights about the algorithms;

### 2022-12-19 latex/matyas_best_fits.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

@@
+The best solutions of all algorithms for Booth Function, obtained using the minimal
+distance of the solution, are shown in Table~\ref{solutions:matyas}:
+
+\begin{table}[H]
+\centering
+\caption{Best Fits For Matyas Function}
+\label{solutions:matyas}
 \begin{tabular}{llrrr}
 \toprule
-Algorithm &                                        Solution &  Iterations &  Function Evaluations &  Function Value \\
+ Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
 \midrule
-      dfp &   1.7926757117875478e-11,1.7863785568107216e-11 &           7 &                    10 &    1.281062e-23 \\
-     bfgs & -4.0285184756435043e-19,-4.0615726129211233e-19 &           7 &                    10 &    6.547689e-39 \\
-    lbfgs &   -3.837208328860697e-15,4.6629367034256575e-15 &           4 &                    16 &    1.806993e-29 \\
-      lma &   3.5389027698051246e-06,3.5389027799876804e-06 &          14 &                    15 &    5.009533e-13 \\
+  dfp & $S_{1}$ &      7 &       10 &      0.00 \\
+ bfgs & $S_{2}$ &      7 &       10 &      0.00 \\
+lbfgs & $S_{3}$ &      4 &       16 &      0.00 \\
+  lma & $S_{4}$ &     14 &       15 &      0.00 \\
 \bottomrule
 \end{tabular}
+\end{table}
+
+The algorithms DFP, BFGS and LBFGS have comparable performances, while LMA
+is the most expensive of all.
+
+Although the column F. Value points to the the same value, this is a rounded value
+and the real values are os order $10^{-22} \approx 10^{-14}$.

### 2022-12-19 latex/matyas_best_solutions.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

--- 2022-12-13 latex/ackley_best_solutions.tex
@@
-\begin{table}
+The best solutions of all algorithms for Matyas Function, indicated as
+$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:matyas}, are shown
+in Table~\ref{detailedsolutions:matyas}:
+
+\begin{table}[H]
 \centering
-\caption{Detailed Solutions For Ackley Function}
-\label{detailedsolutions:ackley}
+\caption{Detailed Solutions For Matyas Function}
+\label{detailedsolutions:matyas}
 \begin{tabular}{lrrrr}
@@
 \midrule
-$x_{1}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
-$x_{2}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
+$x_{1}$ &     0.00 &    -0.00 &    -0.00 &     0.00 \\
+$x_{2}$ &     0.00 &    -0.00 &     0.00 &     0.00 \\
 \bottomrule
@@
 \end{table}
+
+The optimal solution for Matyas Function is $\left[0, 0\right]$ and the rounded values
+of Table~\ref{detailedsolutions:matyas} points to the same value. The error of
+these values are of order $10^{-13}$ os less.

### 2022-12-19 latex/matyas_convergence.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

--- 2022-12-13 latex/ackley_convergence.tex
@@
-\begin{table}
+The convergence report for the Matyas Function is shown in Table~\ref{convergence:matyas}:
+
+\begin{table}[H]
 \centering
-\caption{Convergence Report For Ackley Function}
-\label{convergence:ackley}
+\caption{Convergence Report For Matyas Function}
+\label{convergence:matyas}
 \begin{tabular}{lrrrr}
@@
 \end{table}
+
+All algorithms converged 100 times, using 100 different initial solutions,
+for a search space of $\left[-10, 10\right]$ . In this search space,
+Matyas Function has a well defined valley that has the solution as its
+center, as it is shown in Section~\ref{isolinesmatyas2D}.

### 2022-12-19 latex/rastrigin2d_best_fits.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

@@
+The best solutions of all algorithms for Rastrigin Function, obtained using the minimal
+distance of the solution, are shown in Table~\ref{solutions:rastrigin2d}:
+
+\begin{table}[H]
+\centering
+\caption{Best Fits For Rastrigin Function}
+\label{solutions:rastrigin2d}
 \begin{tabular}{llrrr}
 \toprule
-Algorithm &                                       Solution &  Iterations &  Function Evaluations &  Function Value \\
+ Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
 \midrule
-      dfp & -1.3945825916973396e-12,1.3762564161053067e-12 &           6 &                    11 &             0.0 \\
-     bfgs &  4.190758074827946e-12,-2.1862133845293774e-11 &           8 &                    49 &             0.0 \\
-    lbfgs &  8.784224615873606e-12,-3.6460273411768743e-11 &           5 &                   133 &             0.0 \\
-      lma &  2.6660763338975985e-10,1.5611908894664897e-09 &           4 &                     5 &             0.0 \\
+  dfp & $S_{1}$ &      6 &       11 &      0.00 \\
+ bfgs & $S_{2}$ &      8 &       49 &      0.00 \\
+lbfgs & $S_{3}$ &      5 &      133 &      0.00 \\
+  lma & $S_{4}$ &      4 &        5 &      0.00 \\
 \bottomrule
 \end{tabular}
+\end{table}
+
+LMA is the less expensive algorithm to solve Rastrigin in 2 dimensions, while LBFGS
+is the most expensive of all. Although it has one more iteration than LMA, it evaluates
+the objective function much more times than BFGS, the second most expensive algorithm.
+
+Although the column F. Value points to the the same value, this is a rounded value
+and the real values are os order $10^{-22} \approx 10^{-14}$.

### 2022-12-19 latex/rastrigin2d_best_solutions.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

--- 2022-12-13 latex/ackley_best_solutions.tex
@@
-\begin{table}
+The best solutions of all algorithms for Rastrigin Function, indicated as
+$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:rastrigin2d}, are shown
+in Table~\ref{detailedsolutions:rastrigin2d}:
+
+\begin{table}[H]
 \centering
-\caption{Detailed Solutions For Ackley Function}
-\label{detailedsolutions:ackley}
+\caption{Detailed Solutions For Rastrigin Function}
+\label{detailedsolutions:rastrigin2d}
 \begin{tabular}{lrrrr}
@@
 $x_{1}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
-$x_{2}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
+$x_{2}$ &     0.00 &    -0.00 &    -0.00 &     0.00 \\
 \bottomrule
@@
 \end{table}
+
+The Table~\ref{detailedsolutions:rastrigin2d} shows the same solution to all algorithms, because the values are so small
+and were rounded to fit on the Table. The differences of the optimal point are of order $10^{-14}$ to $10^{-22}$,
+for the LMA, DFP, LBFGS and BFGS algorithms, respectively.

### 2022-12-19 latex/rastrigin2d_convergence.tex
Rewritting latex files
Initial Versioning of Article and Latex Builder

@@
-\begin{table}
+The convergence report for the Rastrigin Function in 2 dimensions is shown in Table~\ref{convergence:rastrigin2d}:
+
+\begin{table}[H]
 \centering
@@
 \end{table}
+
+It is quite sure that all algorithms has good convergence for any algorithm for a
+constrained search space of $\left[-0.15, 0.15\right]$. This search space is around
+the optimal solution to avoid wrong convergence to a local minimum. In this search space,
+Rastrigin Function has a well defined valley that has the solution as its center, as is shown in
+Section~\ref{isolinesrastrigin2D}.

### 2022-12-19 latex/rastrigin2d_function_values.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

@@
+The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:rastrigin2d}:
+
+\begin{table}[H]
+\centering
+\caption{Statistical Information about function values For Rastrigin Function}
+\label{function_values:rastrigin2d}
 \begin{tabular}{lrrrr}
 \toprule
-Algorithm &  Minimal &      Maximum &         Mean &       Median \\
+ Alg. &  Min &  Max &  Mean &  Median \\
 \midrule
-      dfp &      0.0 & 1.492140e-13 & 1.186606e-14 & 0.000000e+00 \\
-     bfgs &      0.0 & 0.000000e+00 & 0.000000e+00 & 0.000000e+00 \\
-    lbfgs &      0.0 & 1.989918e+00 & 1.989918e-02 & 0.000000e+00 \\
-      lma &      0.0 & 3.552714e-15 & 1.882938e-15 & 3.552714e-15 \\
+  dfp & 0.00 & 0.00 &  0.00 &    0.00 \\
+ bfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
+lbfgs & 0.00 & 1.99 &  0.02 &    0.00 \\
+  lma & 0.00 & 0.00 &  0.00 &    0.00 \\
 \bottomrule
 \end{tabular}
+\end{table}
+
+The values again are rounded. The median informs us that, for all
+algorithms is expected to find the minimun of Rastrigin Function.
+Although the mean of LBFGS algorithm is greater than zero, it is expected
+to converge mora than diverge in the function constrained search space.

### 2022-12-19 latex/rastrigin30d_best_fits.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

--- 2022-12-11 latex/rastrigin2d_best_fits.tex
@@
+The best solutions of all algorithms for Rastrigin Function, obtained using the minimal
+distance of the solution, are shown in Table~\ref{solutions:rastrigin30d}:
+
+\begin{table}[H]
+\centering
+\caption{Best Fits For Rastrigin Function}
+\label{solutions:rastrigin30d}
 \begin{tabular}{llrrr}
 \toprule
-Algorithm &                                       Solution &  Iterations &  Function Evaluations &  Function Value \\
+ Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
 \midrule
-      dfp & -1.3945825916973396e-12,1.3762564161053067e-12 &           6 &                    11 &             0.0 \\
-     bfgs &  4.190758074827946e-12,-2.1862133845293774e-11 &           8 &                    49 &             0.0 \\
-    lbfgs &  8.784224615873606e-12,-3.6460273411768743e-11 &           5 &                   133 &             0.0 \\
-      lma &  2.6660763338975985e-10,1.5611908894664897e-09 &           4 &                     5 &             0.0 \\
+  dfp & $S_{1}$ &      8 &       14 &      0.00 \\
+ bfgs & $S_{2}$ &      9 &       54 &      0.00 \\
+lbfgs & $S_{3}$ &      6 &      135 &      0.00 \\
+  lma & $S_{4}$ &      4 &        5 &      0.00 \\
 \bottomrule
 \end{tabular}
+\end{table}
+
+LMA is the less expensive algorithm to solve Rastrigin in 30 dimensions, while LBFGS
+is the most expensive of all. Although it has one more iteration than LMA, it evaluates
+the objective function twice than BFGS, the second most expensive algorithm.
+
+Although the column F. Value points to the the same value, this is a rounded value
+and the real values are os order $10^{-22} \approx 10^{-14}$.

### 2022-12-19 latex/rastrigin30d_convergence.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

--- 2022-12-13 latex/ackley_convergence.tex
@@
-\begin{table}
+The convergence report for the Rastrigin Function in 2 dimensions is shown in Table~\ref{convergence:rastrigin30d}:
+
+\begin{table}[H]
 \centering
-\caption{Convergence Report For Ackley Function}
-\label{convergence:ackley}
+\caption{Convergence Report For Rastrigin Function}
+\label{convergence:rastrigin30d}
 \begin{tabular}{lrrrr}
@@
 \end{table}
+
+It is quite sure that all algorithms has good convergence for a
+constrained search space of $\left[-0.15, 0.15\right]$. This search space is around
+the optimal solution to avoid wrong convergence to a local minimum. In this search space,
+Rastrigin Function has a well defined valley that has the solution as its center.

### 2022-12-19 latex/rastrigin4d_best_fits.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

@@
+The best solutions of all algorithms for Rastrigin Function, obtained using the minimal
+distance of the solution, are shown in Table~\ref{solutions:rastrigin4d}:
+
+\begin{table}[H]
+\centering
+\caption{Best Fits For Rastrigin Function}
+\label{solutions:rastrigin4d}
 \begin{tabular}{llrrr}
 \toprule
-Algorithm &                                           Solution &  Iterations &  Function Evaluations &  Function Value \\
+ Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
 \midrule
-      dfp & 7.824099927923849e-11,-2.1366231163644037e-10,-... &          10 &                    21 &             0.0 \\
-     bfgs & 5.405272390841542e-12,-2.7239120065655507e-11,-... &          11 &                    61 &             0.0 \\
-    lbfgs & 1.471102762075013e-10,1.9145855829354901e-10,8.... &           5 &                   133 &             0.0 \\
-      lma & 2.6660763338975985e-10,1.5611908894664897e-09,-... &           4 &                     5 &             0.0 \\
+  dfp & $S_{1}$ &     10 &       21 &      0.00 \\
+ bfgs & $S_{2}$ &     11 &       61 &      0.00 \\
+lbfgs & $S_{3}$ &      5 &      133 &      0.00 \\
+  lma & $S_{4}$ &      4 &        5 &      0.00 \\
 \bottomrule
 \end{tabular}
+\end{table}
+
+LMA is the less expensive algorithm to solve Rastrigin in 4 dimensions, while LBFGS
+is the most expensive of all. Although it has one more iteration than LMA, it evaluates
+the objective function twice than BFGS, the second most expensive algorithm.
+
+Although the column F. Value points to the the same value, this is a rounded value
+and the real values are os order $10^{-22} \approx 10^{-14}$.

### 2022-12-19 latex/rastrigin4d_best_solutions.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

--- 2022-12-13 latex/ackley_best_solutions.tex
@@
-\begin{table}
+The best solutions of all algorithms for Rastrigin Function, indicated as
+$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:rastrigin4d}, are shown
+in Table~\ref{detailedsolutions:rastrigin4d}:
+
+\begin{table}[H]
 \centering
-\caption{Detailed Solutions For Ackley Function}
-\label{detailedsolutions:ackley}
+\caption{Detailed Solutions For Rastrigin Function}
+\label{detailedsolutions:rastrigin4d}
 \begin{tabular}{lrrrr}
@@
 \midrule
-$x_{1}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
-$x_{2}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
+$x_{1}$ &     0.00 &     0.00 &     0.00 &     0.00 \\
+$x_{2}$ &    -0.00 &    -0.00 &     0.00 &     0.00 \\
+$x_{3}$ &    -0.00 &    -0.00 &     0.00 &    -0.00 \\
+$x_{4}$ &    -0.00 &    -0.00 &     0.00 &     0.00 \\
 \bottomrule
@@
 \end{table}
+
+The Table~\ref{detailedsolutions:rastrigin4d} shows the same solution to all algorithms, because the values are so small
+and were rounded to fit on the Table. The differences of the optimal point are of order $10^{-14}$ to $10^{-22}$,
+for the LMA, DFP, LBFGS and BFGS algorithms, respectively.

### 2022-12-19 latex/rastrigin4d_convergence.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

--- 2022-12-13 latex/ackley_convergence.tex
@@
-\begin{table}
+The convergence report for the Rastrigin Function in 4 dimensions is shown in Table~\ref{convergence:rastrigin4d}:
+
+\begin{table}[H]
 \centering
-\caption{Convergence Report For Ackley Function}
-\label{convergence:ackley}
+\caption{Convergence Report For Rastrigin Function}
+\label{convergence:rastrigin4d}
 \begin{tabular}{lrrrr}
@@
 \end{table}
+
+It is quite sure that all algorithms has good convergence for any algorithm for a
+constrained search space of $\left[-0.15, 0.15\right]$. This search space is around
+the optimal solution to avoid wrong convergence to a local minimum. In this search space,
+Rastrigin Function has a well defined valley that has the solution as its center.

### 2022-12-19 latex/rosenbrock2d_best_fits.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

@@
+The best solutions of all algorithms for Rosenbrock Function, obtained using the minimal
+distance of the solution, are shown in Table~\ref{solutions:rosenbrock2d}:
+
+\begin{table}[H]
+\centering
+\caption{Best Fits For Rosenbrock Function}
+\label{solutions:rosenbrock2d}
 \begin{tabular}{llrrr}
 \toprule
-Algorithm &                              Solution &  Iterations &  Function Evaluations &  Function Value \\
+ Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
 \midrule
-      dfp & 0.9999999999008999,0.9999999997978861 &          24 &                    31 &    1.135257e-20 \\
-     bfgs &                1.0,0.9999999999999999 &          30 &                    43 &    1.232595e-30 \\
-    lbfgs & 0.9999999994699225,0.9999999989299816 &          27 &                    76 &    2.907107e-19 \\
-      lma & 0.9999999979097256,0.9999999958107717 &          16 &                    18 &    4.376780e-18 \\
+  dfp & $S_{1}$ &     24 &       31 &      0.00 \\
+ bfgs & $S_{2}$ &     30 &       43 &      0.00 \\
+lbfgs & $S_{3}$ &     27 &       76 &      0.00 \\
+  lma & $S_{4}$ &     16 &       18 &      0.00 \\
 \bottomrule
 \end{tabular}
+\end{table}
+
+LMA is the less expensive algorithm to solve Rosenbrock Function in 2 dimensions, while LBFGS
+is the most expensive of all. Although it has comparable iterations with DFP nd BFGS, it evaluates
+the objective function twice as much of BFGS, the second most expensive algorithm.
+
+Although the column F. Value points to the the same value, this is a rounded value
+and the real values are os order $10^{-22} \approx 10^{-14}$.

### 2022-12-19 latex/rosenbrock2d_best_solutions.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

--- 2022-12-13 latex/ackley_best_solutions.tex
@@
-\begin{table}
+The best solutions of all algorithms for Rosenbrock Function, indicated as
+$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:rosenbrock2d}, are shown
+in Table~\ref{detailedsolutions:rosenbrock2d}:
+
+\begin{table}[H]
 \centering
-\caption{Detailed Solutions For Ackley Function}
-\label{detailedsolutions:ackley}
+\caption{Detailed Solutions For Rosenbrock Function}
+\label{detailedsolutions:rosenbrock2d}
 \begin{tabular}{lrrrr}
@@
 \midrule
-$x_{1}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
-$x_{2}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
+$x_{1}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
+$x_{2}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
 \bottomrule
@@
 \end{table}
+
+The optimal point of Rosenbrock function in 2 dimensions is correctly pointed to $\left[1, 1\right]$. The Table~\ref{detailedsolutions:rosenbrock2d}
+shows the same solution to all algorithms, because the values are so small and were rounded to fit on the Table. The differences of
+the optimal point are of order $10^{-14}$ to $10^{-22}$, for the LMA, DFP, LBFGS and BFGS algorithms, respectively.

### 2022-12-19 latex/rosenbrock2d_convergence.tex
Rewritting latex files
Initial Versioning of Article and Latex Builder

@@
-\begin{table}
+The convergence report for the Rosenbrock Function in 30 dimensions is shown in Table~\ref{convergence:rosenbrock2d}:
+
+\begin{table}[H]
 \centering
@@
 \end{table}
+
+Except for DFP, Rosenbrock has good convergence for any algorithm for a constrained search space
+of $\left[-1.5, 1.5\right]$. Although the Rosenbrock Function has only the global minimum in a
+search space of $\left[-10, 10\right]$, it has a large banana shaped plateau near the optimal
+solution, as it is shown in Section~\ref{isolinesrosenbrock2D}. The search space constraint serves
+only to limit the number of iterations of each algorithm. The large search space tends to make the algorithm
+walks too much to find the solution and tends to exceed the maximum iterations defined in the evaluation
+criteria shown in Section~\ref{sec:introduction}.

### 2022-12-19 latex/rosenbrock2d_function_values.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

@@
+The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:rosenbrock2d}:
+
+\begin{table}[H]
+\centering
+\caption{Statistical Information about function values For Rosenbrock Function}
+\label{function_values:rosenbrock2d}
 \begin{tabular}{lrrrr}
 \toprule
-Algorithm &      Minimal &      Maximum &         Mean &       Median \\
+ Alg. &  Min &  Max &  Mean &  Median \\
 \midrule
-      dfp & 1.135257e-20 & 1.330822e+00 & 3.883331e-02 & 1.008079e-13 \\
-     bfgs & 1.232595e-30 & 5.420407e-20 & 1.520616e-21 & 3.568745e-24 \\
-    lbfgs & 2.907107e-19 & 6.027957e-11 & 1.010571e-12 & 1.481586e-15 \\
-      lma & 4.376780e-18 & 1.308671e-10 & 7.473415e-12 & 8.945853e-13 \\
+  dfp & 0.00 & 1.33 &  0.04 &    0.00 \\
+ bfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
+lbfgs & 0.00 & 0.00 &  0.00 &    0.00 \\
+  lma & 0.00 & 0.00 &  0.00 &    0.00 \\
 \bottomrule
 \end{tabular}
+\end{table}
+
+The values again are rounded. The median informs us that, for all
+algorithms is expected to find the minimun of Rosenbrock Function.
+Although the mean of DFP algorithm is greater than zero, it is expected
+to converge more than diverge in the function constrained search space.

### 2022-12-19 latex/rosenbrock30d_best_fits.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

@@
+T
+he best solutions of all algorithms for Rosenbrock Function, obtained using the minimal
+distance of the solution, are shown in Table~\ref{solutions:rosenbrock4d}:
+
+\begin{table}[H]
+\centering
+\caption{Best Fits For Rosenbrock Function}
+\label{solutions:rosenbrock30d}
 \begin{tabular}{llrrr}
 \toprule
-Algorithm &                                           Solution &  Iterations &  Function Evaluations &  Function Value \\
+ Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
 \midrule
-      dfp & 1.000000001426901,1.0000000035108567,1.00000000... &        2767 &                  2790 &    2.303328e-14 \\
-     bfgs & 1.0000000000000022,1.0,0.9999999999999846,0.999... &         207 &                   231 &    2.745279e-23 \\
-    lbfgs & 1.0000000005707574,1.0000000006791032,1.0000000... &         160 &                   389 &    4.773145e-16 \\
-      lma & 1.0,0.9999999999999999,0.9999999999999999,0.999... &          53 &                   131 &    1.018105e-16 \\
+  dfp & $S_{1}$ &   2967 &     2990 &      0.00 \\
+ bfgs & $S_{2}$ &    236 &      252 &      0.00 \\
+lbfgs & $S_{3}$ &    164 &      406 &      0.00 \\
+  lma & $S_{4}$ &     53 &      131 &      0.00 \\
 \bottomrule
 \end{tabular}
+\end{table}
+
+LMA is the less expensive algorithm to solve Rosenbrock Function in 30 dimensions, while DFP
+is the most expensive of all.
+
+Although the column F. Value points to the the same value, this is a rounded value
+and the real values are os order $10^{-22} \approx 10^{-14}$.

### 2022-12-19 latex/rosenbrock30d_convergence.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

--- 2022-12-13 latex/rosenbrock2d_convergence.tex
@@
-\begin{table}
+The convergence report for the Rosenbrock Function in 30 dimensions is shown in Table~\ref{convergence:rosenbrock30d}:
+
+\begin{table}[H]
 \centering
 \caption{Convergence Report For Rosenbrock Function}
-\label{convergence:rosenbrock2d}
+\label{convergence:rosenbrock30d}
 \begin{tabular}{lrrrr}
@@
 \midrule
-  dfp &    74 &    26 &       0 &    100 \\
- bfgs &   100 &     0 &       0 &    100 \\
-lbfgs &   100 &     0 &       0 &    100 \\
-  lma &   100 &     0 &       0 &    100 \\
+  dfp &     1 &    99 &       0 &    100 \\
+ bfgs &    80 &    20 &       0 &    100 \\
+lbfgs &    95 &     5 &       0 &    100 \\
+  lma &    88 &    12 &       0 &    100 \\
 \bottomrule
@@
 \end{table}
+
+DFP has poor convergence properties for the Rosenbrock Function with more than 2 dimensions.
+The rest have quite the same profile regarding convergence. It is important to note that
+although all algorithms does not converge for the presented initial solutions, it does not
+diverge at all. Because of the stop criterion of all algorithms, which is the function gradient value,
+and the banana shaped valley (plateau) that Rosenbrock function has, we have this behaviour.

### 2022-12-19 latex/rosenbrock30d_function_values.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

@@
+The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:rosenbrock30d}:
+
+\begin{table}[H]
+\centering
+\caption{Statistical Information about function values For Rosenbrock Function}
+\label{function_values:rosenbrock30d}
 \begin{tabular}{lrrrr}
 \toprule
-Algorithm &      Minimal &   Maximum &      Mean &       Median \\
+ Alg. &  Min &   Max &  Mean &  Median \\
 \midrule
-      dfp & 2.303328e-14 & 29.257503 & 13.357326 & 1.307731e+01 \\
-     bfgs & 2.745279e-23 &  3.986624 &  0.797325 & 6.316386e-22 \\
-    lbfgs & 4.773145e-16 &  3.986624 &  0.199331 & 4.316852e-14 \\
-      lma & 1.018105e-16 &  3.986624 &  0.478395 & 2.761710e-13 \\
+  dfp & 0.00 & 29.25 & 13.10 &   12.58 \\
+ bfgs & 0.00 &  3.99 &  0.80 &    0.00 \\
+lbfgs & 0.00 &  3.99 &  0.20 &    0.00 \\
+  lma & 0.00 &  3.99 &  0.48 &    0.00 \\
 \bottomrule
 \end{tabular}
+\end{table}
+
+The median value informs us that all algorithms are like to find the solution
+for Rosenbrock Function in 4 dimesions. The cases of poor convergence that all algorithms
+have are reflected in the mean value. Looking at the Maximum value, it is noted that the mean value is
+quite the same percentage shown in Table~\ref{convergence:rosenbrock30d}.

### 2022-12-19 latex/rosenbrock4d_best_fits.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

@@
+The best solutions of all algorithms for Rosenbrock Function, obtained using the minimal
+distance of the solution, are shown in Table~\ref{solutions:rosenbrock4d}:
+
+\begin{table}[H]
+\centering
+\caption{Best Fits For Rosenbrock Function}
+\label{solutions:rosenbrock4d}
 \begin{tabular}{llrrr}
 \toprule
-Algorithm &                                           Solution &  Iterations &  Function Evaluations &  Function Value \\
+ Alg. &    Sol. &  Iter. &  F. Eval &  F. Value \\
 \midrule
-      dfp & 0.9999999966340929,0.9999999907960823,0.9999999... &         292 &                   301 &    3.610838e-15 \\
-     bfgs & 1.0000000000000053,1.0000000000000098,1.0000000... &          29 &                    35 &    6.042675e-28 \\
-    lbfgs & 0.999999999931242,0.999999999845467,0.999999999... &          45 &                   134 &    1.861496e-19 \\
-      lma & 0.9999999999421001,0.9999999998839636,0.9999999... &          18 &                    20 &    7.114597e-20 \\
+  dfp & $S_{1}$ &     44 &       49 &      0.00 \\
+ bfgs & $S_{2}$ &     29 &       35 &      0.00 \\
+lbfgs & $S_{3}$ &     45 &      134 &      0.00 \\
+  lma & $S_{4}$ &     18 &       20 &      0.00 \\
 \bottomrule
 \end{tabular}
+\end{table}
+
+LMA is the less expensive algorithm to solve Rosenbrock Function in 4 dimensions, while LBFGS
+is the most expensive of all. Although it has comparable iterations with DFP nd BFGS, it evaluates
+the objective function twice as much of BFGS, the second most expensive algorithm.
+
+Although the column F. Value points to the the same value, this is a rounded value
+and the real values are os order $10^{-22} \approx 10^{-14}$.

### 2022-12-19 latex/rosenbrock4d_best_solutions.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

--- 2022-12-13 latex/ackley_best_solutions.tex
@@
-\begin{table}
+The best solutions of all algorithms for Rosenbrock Function, indicated as
+$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:rosenbrock4d}, are shown
+in Table~\ref{detailedsolutions:rosenbrock4d}:
+
+\begin{table}[H]
 \centering
-\caption{Detailed Solutions For Ackley Function}
-\label{detailedsolutions:ackley}
+\caption{Detailed Solutions For Rosenbrock Function}
+\label{detailedsolutions:rosenbrock4d}
 \begin{tabular}{lrrrr}
@@
 \midrule
-$x_{1}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
-$x_{2}$ &    -0.00 &     0.00 &     0.00 &     0.00 \\
+$x_{1}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
+$x_{2}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
+$x_{3}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
+$x_{4}$ &     1.00 &     1.00 &     1.00 &     1.00 \\
 \bottomrule
@@
 \end{table}
+
+The optimal point of Rosenbrock function in 4 dimensions is correctly pointed to $\left[1, 1, 1, 1\right]$. The Table~\ref{detailedsolutions:rosenbrock4d}
+shows the same solution to all algorithms, because the values are so small and were rounded to fit on the Table. The differences of
+the optimal point are of order $10^{-14}$ to $10^{-22}$, for the LMA, DFP, LBFGS and BFGS algorithms, respectively.

### 2022-12-19 latex/rosenbrock4d_convergence.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

--- 2022-12-13 latex/rosenbrock2d_convergence.tex
@@
-\begin{table}
+The convergence report for the Rosenbrock Function in 30 dimensions is shown in Table~\ref{convergence:rosenbrock4d}:
+
+\begin{table}[H]
 \centering
 \caption{Convergence Report For Rosenbrock Function}
-\label{convergence:rosenbrock2d}
+\label{convergence:rosenbrock4d}
 \begin{tabular}{lrrrr}
@@
 \midrule
-  dfp &    74 &    26 &       0 &    100 \\
- bfgs &   100 &     0 &       0 &    100 \\
-lbfgs &   100 &     0 &       0 &    100 \\
-  lma &   100 &     0 &       0 &    100 \\
+  dfp &    46 &    54 &       0 &    100 \\
+ bfgs &    90 &    10 &       0 &    100 \\
+lbfgs &    89 &    11 &       0 &    100 \\
+  lma &    91 &     9 &       0 &    100 \\
 \bottomrule

### 2022-12-19 latex/rosenbrock4d_function_values.tex
Added build to main latex file
Rewritting latex files
Initial Versioning of Article and Latex Builder

@@
+The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:rosenbrock4d}:
+
+\begin{table}[H]
+\centering
+\caption{Statistical Information about function values For Rosenbrock Function}
+\label{function_values:rosenbrock4d}
 \begin{tabular}{lrrrr}
 \toprule
-Algorithm &      Minimal &  Maximum &     Mean &       Median \\
+ Alg. &  Min &  Max &  Mean &  Median \\
 \midrule
-      dfp & 3.610838e-15 & 3.707671 & 0.601430 & 1.338231e-03 \\
-     bfgs & 6.042675e-28 & 3.701429 & 0.370143 & 1.679398e-23 \\
-    lbfgs & 1.861496e-19 & 3.701429 & 0.407157 & 2.624568e-15 \\
-      lma & 7.114597e-20 & 3.701429 & 0.333129 & 1.322880e-13 \\
+  dfp & 0.00 & 3.71 &  0.60 &    0.00 \\
+ bfgs & 0.00 & 3.70 &  0.37 &    0.00 \\
+lbfgs & 0.00 & 3.70 &  0.41 &    0.00 \\
+  lma & 0.00 & 3.70 &  0.33 &    0.00 \\
 \bottomrule
 \end{tabular}
+\end{table}
+
+The median value informs us that all algorithms are like to find the solution
+for Rosenbrock Function in 4 dimesions. The cases of poor convergence that all algorithms
+have are reflected in the mean value. Looking at the Maximum value, it is noted that the mean value is
+quite the same percentage shown in Table~\ref{convergence:rosenbrock4d}.

### 2022-12-19 paper/new/article.tex
Initial Versioning of Article and Latex Builder

--- 2022-12-19 paper/new/article.tex
@@
 \usepackage[T1]{fontenc}
-\usepackage{booktabs}
 \restylefloat{table}
@@
 All algorithms converged 100 times, using 100 different initial solutions,
-for a constrained search space of .$[-0.05, 0.05]$. This search space is around
-the optimal solution to avoid wrong convergence to a local minimum.
+for a constrained search space of $\left[-0.05, 0.05\right]$ . This search space is around
+the optimal solution to avoid wrong convergence to a local minimum. In this search space,
+Ackley Function has a well defined valley that has the solution as its center, as is shown in
+Section~\ref{isolinesackley2D}.
 
@@
 
-The values again are rounded. The matter is the mdian value: it informs us the result that
-we are like to obtain when running any algorithm to solve for minimum. As it seems, for all
+The values again are rounded. The matter is the median value: it informs us the result that
+we are like to obtain when running any algorithm to solve for a minimum. As it seems, for all
 algorithms is expected to find the minimun of Ackley Function.
@@
 The Ackley function has a narrow space around the optimal solution and,
-altough specially LMA is of rapid convergence, it iterated 38 times to find
-the optimal value, probably because it walked around the solution
-before reach it. All algorithms were very slow to converge and the most expensive
+although specially LMA is of rapid convergence, it iterated 38 times to find
+the optimal value. All algorithms were very slow to converge and the most expensive
 are LMA and LBFGS.
 
-Altough the column F. Value points to the the same value, this is a rounded value
-and the real values are os order $10^{-22} \approx 10^{-14}$.
+Although the column F. Value points to the the same value, this is a rounded value
+and the real values are of order $10^{-22} \approx 10^{-14}$.
 
@@
 \end{figure}
-The isolines for Ackley Function shows that there are at least 4 pitfalls near ther optimal solution, so, the search space needs to be reduced to \$[-0.05, 0.05]\$ to avoid wrong convergence.
+The isolines for Ackley Function shows that there are at least 4 pitfalls near the optimal solution, so, the search space needs to be reduced to $[-0.05, 0.05]$ to avoid wrong convergence.
 All the algorithms converges quite smoothly following a straight line\subsection{Beale Function}
@@
 
+The Beale Function seems to have a plateau near the solution, as
+it is shown in Section~\ref{isolinesbeale2D}.
+
 \subsubsection{Statistical Analysis of The Solutions}
@@
 value are noticeable. The larger mean value of LMA reinforces the notion of divergence in this case
-and signifies that the algorithm don't fit very well for BEale Fnction minimum.
+and signifies that the algorithm don't fit very well for the Beale Function minimum.
 
@@
 it had a reasonable number of iterations for each algorithm. The DFP method, superseeded by BFGS,
-is surprisingly rapid to find the solution. The LMA, known to be fast, had a reasonable performance.
+is surprisingly fast to find the solution. The LMA, known to be fast, had a reasonable performance.
 BFGS/LBFGS performed as expected.
 
-Altough the column F. Value points to the the same value, this is a rounded value
-and the real values are os order $10^{-22} \approx 10^{-14}$.
+Although the column F. Value points to the the same value, this is a rounded value
+and the real values are of order $10^{-22} \approx 10^{-14}$.
 
@@
 
-The optimal solution for Beale Function is $[3, 0.5]$ and the rounded values
+The optimal solution for Beale Function is $\left[3, 0.5\right]$ and the rounded values
 of Table~\ref{detailedsolutions:beale} points to the same value. The error of
@@
 The isolines for Beale Function shows that there are a large plateau near the solution.
-For an unknown reason the best algorithm had 80\% of performance at its best.
+For this reason we believe that the best algorithm had 80\% of performance at its best.
 Quasi-Newton algorithms suffers to converge when the gradient is less significant.\subsection{Booth Function}
@@
 \label{convergencebooth2D}
+
+The convergence report for the Booth Function is shown in Table~\ref{convergence:booth}:
 
@@
 
+All algorithms converged 100 times, using 100 different initial solutions,
+for a constrained search space of $\left[0, 4\right]$ . This search space is around
+the optimal solution to avoid wrong convergence to a local minimum. In this search space,
+Booth Function has a well defined valley that has the solution as its center, as it is shown
+in Section~\ref{isolinesbooth2D}.
+
 \subsubsection{Statistical Analysis of The Solutions}
 \label{statisticalanalysisbooth2D}
+
+The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:beale}:
 
@@
 
+The values again are rounded. The median informs us that, for all
+algorithms is expected to find the minimun of Booth Function.
+
 \subsubsection{Best Fits}
@@
 distance of the solution, are shown in Table~\ref{solutions:booth}:
+
 \begin{table}[H]
@@
 
-Altough the column F. Value points to the the same value, this is a rounded value
+Although the column F. Value points to the the same value, this is a rounded value
 and the real values are os order $10^{-22} \approx 10^{-14}$.
+
+The best solutions of all algorithms for Beale Function, indicated as
+$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:booth}, are shown
+in Table~\ref{detailedsolutions:booth}:
 
@@
 
+The optimal solution for Booth Function is $\left[1, 3\right]$ and the rounded values
+of Table~\ref{detailedsolutions:booth} points to the same value. The error of
+these values are of order $10^{-13}$ os less.
 \subsubsection{Isolines and Convergence line}
@@
 
-\begin{figure}[H]
+The isolines of Booth Function and convergence lines for all algorithms are shown i Figure~\ref{fig:booth}:\begin{figure}[H]
 \centering
@@
 \end{figure}
-\subsection{Matyas Function}
+The Figure~\ref{fig:booth} shows that Booth Function has a well defined valley near $[1, 3]$. \subsection{Matyas Function}
 \label{matyas2D}
@@
 \label{convergencematyas2D}
+
+The convergence report for the Matyas Function is shown in Table~\ref{convergence:matyas}:
 
@@
 
+All algorithms converged 100 times, using 100 different initial solutions,
+for a search space of $\left[-10, 10\right]$ . In this search space,
+Matyas Function has a well defined valley that has the solution as its
+center, as it is shown in Section~\ref{isolinesmatyas2D}.
+
 \subsubsection{Statistical Analysis of The Solutions}
 \label{statisticalanalysismatyas2D}
+
+The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:matyas}:
 
@@
 
+The values again are rounded. The median informs us that, for all
+algorithms is expected to find the minimun of Matyas Function.
 \subsubsection{Best Fits}
 \label{bestfitsmatyas2D}
+
+The best solutions of all algorithms for Booth Function, obtained using the minimal
+distance of the solution, are shown in Table~\ref{solutions:matyas}:
 
@@
 
+The algorithms DFP, BFGS and LBFGS have comparable performances, while LMA
+is the most expensive of all.
+
+Although the column F. Value points to the the same value, this is a rounded value
+and the real values are os order $10^{-22} \approx 10^{-14}$.
+
+The best solutions of all algorithms for Matyas Function, indicated as
+$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:matyas}, are shown
+in Table~\ref{detailedsolutions:matyas}:
+
 \begin{table}[H]
@@
 
+The optimal solution for Matyas Function is $\left[0, 0\right]$ and the rounded values
+of Table~\ref{detailedsolutions:matyas} points to the same value. The error of
+these values are of order $10^{-13}$ os less.
 \subsubsection{Isolines and Convergence line}
@@
 
-\begin{figure}[H]
+The isolines of Matyas Function and convergence lines for all algorithms are shown i Figure~\ref{fig:matyas}:\begin{figure}[H]
 \centering
@@
 \end{figure}
-\subsection{Rastrigin Function}
+The Figure~\ref{fig:matyas} shows that Matyas Function has a well defined valley near $[0, 0]$. \subsection{Rastrigin Function}
 \label{rastrigin2d2D}
@@
 \label{convergencerastrigin2d2D}
+
+The convergence report for the Rastrigin Function in 2 dimensions is shown in Table~\ref{convergence:rastrigin2d}:
 
@@
 
+It is quite sure that all algorithms has good convergence for any algorithm for a
+constrained search space of $\left[-0.15, 0.15\right]$. This search space is around
+the optimal solution to avoid wrong convergence to a local minimum. In this search space,
+Rastrigin Function has a well defined valley that has the solution as its center, as is shown in
+Section~\ref{isolinesrastrigin2D}.
+
 \subsubsection{Statistical Analysis of The Solutions}
 \label{statisticalanalysisrastrigin2d2D}
+
+The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:rastrigin2d}:
 
@@
 
+The values again are rounded. The median informs us that, for all
+algorithms is expected to find the minimun of Rastrigin Function.
+Although the mean of LBFGS algorithm is greater than zero, it is expected
+to converge mora than diverge in the function constrained search space.
 \subsubsection{Best Fits}
 \label{bestfitsrastrigin2d2D}
+
+The best solutions of all algorithms for Rastrigin Function, obtained using the minimal
+distance of the solution, are shown in Table~\ref{solutions:rastrigin2d}:
 
@@
 
+LMA is the less expensive algorithm to solve Rastrigin in 2 dimensions, while LBFGS
+is the most expensive of all. Although it has one more iteration than LMA, it evaluates
+the objective function much more times than BFGS, the second most expensive algorithm.
+
+Although the column F. Value points to the the same value, this is a rounded value
+and the real values are os order $10^{-22} \approx 10^{-14}$.
+
+The best solutions of all algorithms for Rastrigin Function, indicated as
+$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:rastrigin2d}, are shown
+in Table~\ref{detailedsolutions:rastrigin2d}:
+
 \begin{table}[H]
@@
 
+The Table~\ref{detailedsolutions:rastrigin2d} shows the same solution to all algorithms, because the values are so small
+and were rounded to fit on the Table. The differences of the optimal point are of order $10^{-14}$ to $10^{-22}$,
+for the LMA, DFP, LBFGS and BFGS algorithms, respectively.
+
 \subsubsection{Isolines and Convergence line}
@@
 
-\begin{figure}[H]
+The isolines of Rastrigin Function for 2 dimensions and convergence lines for all algorithms are shown in Figure~\ref{fig:rastrigin2d}:\begin{figure}[H]
 \centering
@@
 \end{figure}
-\subsection{Rosenbrock Function}
+The isolines for Rastrigin Function shows that there are at least 2 pitfalls near the optimal solution, so, the search space needs to be reduced to $[-0.15, 0.15]$ to avoid wrong convergence.
+All the algorithms, except BFGS, converges quite smoothly following a straight line\subsection{Rosenbrock Function}
 \label{rosenbrock2d2D}
@@
 \label{convergencerosenbrock2d2D}
+
+The convergence report for the Rosenbrock Function in 30 dimensions is shown in Table~\ref{convergence:rosenbrock2d}:
 
@@
 
+Except for DFP, Rosenbrock has good convergence for any algorithm for a constrained search space
+of $\left[-1.5, 1.5\right]$. Although the Rosenbrock Function has only the global minimum in a
+search space of $\left[-10, 10\right]$, it has a large banana shaped plateau near the optimal
+solution, as it is shown in Section~\ref{isolinesrosenbrock2D}. The search space constraint serves
+only to limit the number of iterations of each algorithm. The large search space tends to make the algorithm
+walks too much to find the solution and tends to exceed the maximum iterations defined in the evaluation
+criteria shown in Section~\ref{sec:introduction}.
+
 \subsubsection{Statistical Analysis of The Solutions}
 \label{statisticalanalysisrosenbrock2d2D}
+
+The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:rosenbrock2d}:
 
@@
 
+The values again are rounded. The median informs us that, for all
+algorithms is expected to find the minimun of Rosenbrock Function.
+Although the mean of DFP algorithm is greater than zero, it is expected
+to converge more than diverge in the function constrained search space.
 \subsubsection{Best Fits}
 \label{bestfitsrosenbrock2d2D}
+
+The best solutions of all algorithms for Rosenbrock Function, obtained using the minimal
+distance of the solution, are shown in Table~\ref{solutions:rosenbrock2d}:
 
@@
 
+LMA is the less expensive algorithm to solve Rosenbrock Function in 2 dimensions, while LBFGS
+is the most expensive of all. Although it has comparable iterations with DFP nd BFGS, it evaluates
+the objective function twice as much of BFGS, the second most expensive algorithm.
+
+Although the column F. Value points to the the same value, this is a rounded value
+and the real values are os order $10^{-22} \approx 10^{-14}$.
+
+The best solutions of all algorithms for Rosenbrock Function, indicated as
+$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:rosenbrock2d}, are shown
+in Table~\ref{detailedsolutions:rosenbrock2d}:
+
 \begin{table}[H]
@@
 
+The optimal point of Rosenbrock function in 2 dimensions is correctly pointed to $\left[1, 1\right]$. The Table~\ref{detailedsolutions:rosenbrock2d}
+shows the same solution to all algorithms, because the values are so small and were rounded to fit on the Table. The differences of
+the optimal point are of order $10^{-14}$ to $10^{-22}$, for the LMA, DFP, LBFGS and BFGS algorithms, respectively.
+
 \subsubsection{Isolines and Convergence line}
@@
 
-\begin{figure}[H]
+The isolines of Rosenbrock Function for 2 dimensions and convergence lines for all algorithms are shown in Figure~\ref{fig:rosenbrock2d}:\begin{figure}[H]
 \centering
@@
 \end{figure}
-
+The isolines for Rosenbrock Function shows an interesting behaviour  near the optimal solution: the banana shape seems to force all algorithms to choose $x_{2}$ axis to solve first, and then solve for $x_{1}$ axis.
+The $x_{2}$ axis has probably the most significant derivative for an arbitrary point, so, when the algorithm walks around for solution, it first find the valley and then walks around the valley to find its minumum
 \section{4D Function versions}
@@
 \label{convergencerastrigin4d4D}
+
+The convergence report for the Rastrigin Function in 4 dimensions is shown in Table~\ref{convergence:rastrigin4d}:
 
@@
 
+It is quite sure that all algorithms has good convergence for any algorithm for a
+constrained search space of $\left[-0.15, 0.15\right]$. This search space is around
+the optimal solution to avoid wrong convergence to a local minimum. In this search space,
+Rastrigin Function has a well defined valley that has the solution as its center.
 \subsubsection{Statistical Analysis of The Solutions}
 \label{statisticalanalysisrastrigin4d4D}
+
+The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:rastrigin4d}:
 
@@
 
+The values again are rounded. The median informs us that, for all
+algorithms is expected to find the minimun of Rastrigin Function.
 \subsubsection{Best Fits}
 \label{bestfitsrastrigin4d4D}
+
+The best solutions of all algorithms for Rastrigin Function, obtained using the minimal
+distance of the solution, are shown in Table~\ref{solutions:rastrigin4d}:
 
@@
 
+LMA is the less expensive algorithm to solve Rastrigin in 4 dimensions, while LBFGS
+is the most expensive of all. Although it has one more iteration than LMA, it evaluates
+the objective function twice than BFGS, the second most expensive algorithm.
+
+Although the column F. Value points to the the same value, this is a rounded value
+and the real values are os order $10^{-22} \approx 10^{-14}$.
+
+The best solutions of all algorithms for Rastrigin Function, indicated as
+$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:rastrigin4d}, are shown
+in Table~\ref{detailedsolutions:rastrigin4d}:
+
 \begin{table}[H]
@@
 
+The Table~\ref{detailedsolutions:rastrigin4d} shows the same solution to all algorithms, because the values are so small
+and were rounded to fit on the Table. The differences of the optimal point are of order $10^{-14}$ to $10^{-22}$,
+for the LMA, DFP, LBFGS and BFGS algorithms, respectively.
+
 \subsection{Rosenbrock Function}
@@
 \label{convergencerosenbrock4d4D}
+
+The convergence report for the Rosenbrock Function in 30 dimensions is shown in Table~\ref{convergence:rosenbrock4d}:
 
@@
 
+DFP has poor convergence properties for the Rosenbrock Function with more than 2 dimensions.
+The rest have quite the same profile regarding convergence. It is important to note that
+although all algorithms does not converge for the presented initial solutions, it does not
+diverge at all. Because of the stop criterion of all algorithms, which is the function gradient value,
+and the banana shaped valley (plateau) that Rosenbrock function has, we have this behaviour.
 \subsubsection{Statistical Analysis of The Solutions}
 \label{statisticalanalysisrosenbrock4d4D}
+
+The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:rosenbrock4d}:
 
@@
 
+The median value informs us that all algorithms are like to find the solution
+for Rosenbrock Function in 4 dimesions. The cases of poor convergence that all algorithms
+have are reflected in the mean value. Looking at the Maximum value, it is noted that the mean value is
+quite the same percentage shown in Table~\ref{convergence:rosenbrock4d}.
+
 \subsubsection{Best Fits}
 \label{bestfitsrosenbrock4d4D}
+
+The best solutions of all algorithms for Rosenbrock Function, obtained using the minimal
+distance of the solution, are shown in Table~\ref{solutions:rosenbrock4d}:
 
@@
 
+LMA is the less expensive algorithm to solve Rosenbrock Function in 4 dimensions, while LBFGS
+is the most expensive of all. Although it has comparable iterations with DFP nd BFGS, it evaluates
+the objective function twice as much of BFGS, the second most expensive algorithm.
+
+Although the column F. Value points to the the same value, this is a rounded value
+and the real values are os order $10^{-22} \approx 10^{-14}$.
+
+The best solutions of all algorithms for Rosenbrock Function, indicated as
+$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:rosenbrock4d}, are shown
+in Table~\ref{detailedsolutions:rosenbrock4d}:
+
 \begin{table}[H]
@@
 
+The optimal point of Rosenbrock function in 4 dimensions is correctly pointed to $\left[1, 1, 1, 1\right]$. The Table~\ref{detailedsolutions:rosenbrock4d}
+shows the same solution to all algorithms, because the values are so small and were rounded to fit on the Table. The differences of
+the optimal point are of order $10^{-14}$ to $10^{-22}$, for the LMA, DFP, LBFGS and BFGS algorithms, respectively.
+
 \section{30D Function versions}
@@
 \label{convergencerastrigin30d30D}
+
+The convergence report for the Rastrigin Function in 2 dimensions is shown in Table~\ref{convergence:rastrigin30d}:
 
@@
 
+It is quite sure that all algorithms has good convergence for a
+constrained search space of $\left[-0.15, 0.15\right]$. This search space is around
+the optimal solution to avoid wrong convergence to a local minimum. In this search space,
+Rastrigin Function has a well defined valley that has the solution as its center.
 \subsubsection{Statistical Analysis of The Solutions}
 \label{statisticalanalysisrastrigin30d30D}
+
+The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:rastrigin30d}:
 
@@
 
+The values again are rounded. The median informs us that, for all
+algorithms is expected to find the minimun of Rastrigin Function.
 \subsubsection{Best Fits}
 \label{bestfitsrastrigin30d30D}
+
+The best solutions of all algorithms for Rastrigin Function, obtained using the minimal
+distance of the solution, are shown in Table~\ref{solutions:rastrigin30d}:
 
@@
 \end{table}
+
+LMA is the less expensive algorithm to solve Rastrigin in 30 dimensions, while LBFGS
+is the most expensive of all. Although it has one more iteration than LMA, it evaluates
+the objective function twice than BFGS, the second most expensive algorithm.
+
+Although the column F. Value points to the the same value, this is a rounded value
+and the real values are os order $10^{-22} \approx 10^{-14}$.
+
+The best solutions of all algorithms for Rastrigin Function, indicated as
+$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:rastrigin30d}, are shown
+in Table~\ref{detailedsolutions:rastrigin30d}:
 
@@
 
+The Table~\ref{detailedsolutions:rastrigin30d} shows the same solution to all algorithms, because the values are so small
+and were rounded to fit on the Table. The differences of the optimal point are of order $10^{-14}$ to $10^{-22}$,
+for the LMA, DFP, LBFGS and BFGS algorithms, respectively.
+
 \subsection{Rosenbrock Function}
@@
 \label{convergencerosenbrock30d30D}
+
+The convergence report for the Rosenbrock Function in 30 dimensions is shown in Table~\ref{convergence:rosenbrock30d}:
 
@@
 
+DFP has poor convergence properties for the Rosenbrock Function with more than 2 dimensions.
+The rest have quite the same profile regarding convergence. It is important to note that
+although all algorithms does not converge for the presented initial solutions, it does not
+diverge at all. Because of the stop criterion of all algorithms, which is the function gradient value,
+and the banana shaped valley (plateau) that Rosenbrock function has, we have this behaviour.
 \subsubsection{Statistical Analysis of The Solutions}
 \label{statisticalanalysisrosenbrock30d30D}
+
+The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:rosenbrock30d}:
 
@@
 
+The median value informs us that all algorithms are like to find the solution
+for Rosenbrock Function in 4 dimesions. The cases of poor convergence that all algorithms
+have are reflected in the mean value. Looking at the Maximum value, it is noted that the mean value is
+quite the same percentage shown in Table~\ref{convergence:rosenbrock30d}.
+
 \subsubsection{Best Fits}
 \label{bestfitsrosenbrock30d30D}
+
+T
+he best solutions of all algorithms for Rosenbrock Function, obtained using the minimal
+distance of the solution, are shown in Table~\ref{solutions:rosenbrock4d}:
 
@@
 \end{table}
+
+LMA is the less expensive algorithm to solve Rosenbrock Function in 30 dimensions, while DFP
+is the most expensive of all.
+
+Although the column F. Value points to the the same value, this is a rounded value
+and the real values are os order $10^{-22} \approx 10^{-14}$.
+
+The best solutions of all algorithms for Rosenbrock Function, indicated as
+$S_{1}$, $S_{2}$, $S_{3}$ and $S_{4}$ in Table~\ref{solutions:rosenbrock30d}, are shown
+in Table~\ref{detailedsolutions:rosenbrock30d}:
 
@@
 
+The optimal point of Rosenbrock function in 30 dimensions is correctly pointed to $\left[1, 1, \cdots , 1, 1\right]$. The Table~\ref{detailedsolutions:rosenbrock30d}
+shows the same solution to all algorithms, because the values are so small and were rounded to fit on the Table. The differences of
+the optimal point are of order $10^{-14}$ to $10^{-22}$, for the LMA, DFP, LBFGS and BFGS algorithms, respectively.
+
 \end{document}

### 2022-12-19 build_main_latex_file.py

@@ -17,15 +17,38 @@ footer_file = "latex/footer.tex"
 image_comments = {'ackley': ["The isolines of Ackley Function and convergence lines for all algorithms "
                              "are shown in Figure~\\ref{fig:ackley}:",
                             "The isolines for Ackley Function shows that there are at least 4 pitfalls"
-                            " near ther optimal solution, so, the search space needs to be reduced to "
-                            "\$[-0.05, 0.05]\$ to avoid wrong convergence. All the algorithms converges "
+                            " near the optimal solution, so, the search space needs to be reduced to "
+                            "$[-0.05, 0.05]$ to avoid wrong convergence. All the algorithms converges "
                             "quite smoothly following a straight line"],
                   "beale": ["The isolines of Beale Function and convergence lines for all algorithms "
                              "are shown i Figure~\\ref{fig:beale}:",
                             "The isolines for Beale Function shows that there are a large plateau near "
-                            "the solution. For an unknown reason the best algorithm had 80\% of performance"
+                            "the solution. For this reason we believe that the best algorithm had 80\% of performance"
                             " at its best. Quasi-Newton algorithms suffers to converge when the gradient is"
-                            " less significant."]}
+                            " less significant."],
+                  "booth": ["The isolines of Booth Function and convergence lines for all algorithms "
+                            "are shown i Figure~\\ref{fig:booth}:",
+                            "The Figure~\\ref{fig:booth} shows that Booth Function has a well defined "
+                            "valley near $[1, 3]$. "],
+                  "matyas": ["The isolines of Matyas Function and convergence lines for all algorithms "
+                             "are shown i Figure~\\ref{fig:matyas}:",
+                             "The Figure~\\ref{fig:matyas} shows that Matyas Function has a well defined "
+                            "valley near $[0, 0]$. "],
+                  "rastrigin2d": ["The isolines of Rastrigin Function for 2 dimensions and "
+                                  "convergence lines for all algorithms "
+                                  "are shown in Figure~\\ref{fig:rastrigin2d}:",
+                                   "The isolines for Rastrigin Function shows that there are at least 2 pitfalls"
+                                   " near the optimal solution, so, the search space needs to be reduced to "
+                                   "$[-0.15, 0.15]$ to avoid wrong convergence. All the algorithms, except BFGS, converges "
+                                   "quite smoothly following a straight line"],
+                  "rosenbrock2d": ["The isolines of Rosenbrock Function for 2 dimensions "
[…]

### 2022-12-19 latex/footer.tex
Some additions for Article

\section{Discussion}

The main objective of this work is demonstrate the inner work of a optimization class of algorithms called \textit{Quasi-Newton algorithms}. Four of them are presented, along with the results and analysis regarding convergence, function evaluations and function objective values.

For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions. To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.

The \textit{Levenberg-Marquardt Algorithm} implemented for this paper is very sensitive to hyperparameters, namely $\alpha$ and $\lambda$, which was not tunned to every function, so, the conspicuous performance variation is noticeable along the results. LMA is known to be fast and reliable, but in our implementation it was found a little tricky to get the hyperparameters right for all the test functions. But for Rosenbrock and Rastrigin, it is the best option, even for lame implementations like ours.

The \textit{Broyden–Fletcher–Goldfarb–Shanno} Algorithm was the only one that we decided to use it as is from \textit{SciPy}, because it has features desired for this work, like counting of function evaluations, gradient evaluation and iterations. It performed very well for Ackley and Booth Functions, and reasonably well for other functions.

The \textit{Davidon–Fletcher–Powell} Algorithm is not implemented in \textit{SciPy} but its equations shows that it is the dual of BFGS, so, it was easy to implement using some \textit{SciPy} code for BFGS algorithm. In the DFP procedure, there is a Hessian inversion to be evaluated every iteration, then, numerical imprecision would be taken into consideration evaluating its results. While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function. The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.

Finally, the \textit{Limited memory BFGS} has an average performance among the functions. The original algorithm was implemented using code found in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.

In fact there are no algorithm that solves satisfactory the minima problem for an arbitrary function. Form the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.

\end{document}

### 2022-12-19 latex/header.tex
Some additions for Article

@@
 
-The four methods were implemented using the Python language, based on the SciPy, NumPy and SimPy packages.
+The four methods were implemented using the Python language, based on the SciPy, NumPy and SymPy packages.
 The SciPy package already contains standard procedures for numerical optimization and uses the NumPy package for its internal operations.
-The SymPy package is used to assemble the test functions and is very convenient for differentiation of functions.
+The SymPy package is used to assemble the test functions and is a very convenient way for differentiation of functions.
 The LBGFS, DFP and LMA methods, although they have native versions within the SciPy package, were implemented manually following SciPy conventions because the native versions do not support data collection of iterations and/or expect different parameters from the original proposal, such as LMA.

### 2022-12-19 paper/new/article.tex
Some additions for Article

@@
 \end{itemize}
-
 \section{2D Function versions}
@@
 
+\section{Discussion}
+
+The main objective of this work is demonstrate the inner work of a optimization class of algorithms called \textit{Quasi-Newton algorithms}.
+Four of them are presented, along with the results and analysis regarding convergence, function evaluations and function objective values.
+
+For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions.
+To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.
+
+The \textit{Levenberg-Marquardt Algorithm} implemented for this paper is very sensitive to hyperparameters, namely $\alpha$ and $\lambda$, which was not tunned to every function, so, the conspicuous performance variation is noticeable along the results.
+LMA is known to be fast and reliable, but in our implementation it was found a little tricky to get the hyperparameters right for all the test functions.
+But for Rosenbrock and Rastrigin, it is the best option, even for lame implementations like ours.
+
+The \textit{Broyden–Fletcher–Goldfarb–Shanno} Algorithm was the only one that we decided to use it as is from \textit{SciPy}, because it has features desired for this work, like counting of function evaluations, gradient evaluation and iterations.
+It performed very well for Ackley and Booth Functions, and reasonably well for other functions.
+
+The \textit{Davidon–Fletcher–Powell} Algorithm is not implemented in \textit{SciPy} but its equations shows that it is the dual of BFGS, so, it was easy to implement using some \textit{SciPy} code for BFGS algorithm.
+In the DFP procedure, there is a Hessian inversion to be evaluated every iteration, then, numerical imprecision would be taken into consideration evaluating its results.
+While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function.
+The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.
+
+Finally, the \textit{Limited memory BFGS} has an average performance among the functions.
+The original algorithm was implemented using code found in the url https://github.com/qkolj/L-BFGS/blob/master/L-BFGS.ipynb.
+
+In fact there are no algorithm that solves satisfactory the minima problem for an arbitrary function.
+Form the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
+
 \end{document}

### 2022-12-19 Solvers/Solvers/custom_minimizers.py

@@ -653,12 +653,6 @@ def fmin_dfp(f, x0, fprime=None, args=(), gtol=1e-5, norm=Inf,
             return res['x']
 
 
-"""
-Reference: H. B. Nielsen, “Damping parameter in Marquardt’s method”. Report IMM-REP-
-1999-05, Technical University of Denmark, Lyngby, Dinamarca, 2005
-"""
-
-
 def _minimize_dfp(fun, x0, args=(), jac=None, callback=None,
                   gtol=1e-5, norm=Inf, eps=_epsilon, maxiter=None,
                   disp=False, return_all=False, finite_diff_rel_step=None,

### 2022-12-20 latex/footer.tex
Article Review

@@
 
-In fact there are no algorithm that solves satisfactory the minima problem for an arbitrary function.
-Form the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
+In fact, there are no Quasi-Newton algorithms that solver the minima problem for an any function.
+From the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
 

### 2022-12-20 latex/rosenbrock30d_best_fits.tex
Article Review

@@
-T
-he best solutions of all algorithms for Rosenbrock Function, obtained using the minimal
+The best solutions of all algorithms for Rosenbrock Function, obtained using the minimal
 distance of the solution, are shown in Table~\ref{solutions:rosenbrock4d}:

### 2022-12-30 paper/new/article.tex
Article Done

@@
 \end{itemize}
+
 \section{2D Function versions}
@@
 
-The minimal. maximal, mean and median values of the solutions are shown in Table~\ref{function_values:ackley}:
+The minimal, maximal, mean and median values of the solutions are shown in Table~\ref{function_values:ackley}:
 
@@
 The isolines for Ackley Function shows that there are at least 4 pitfalls near the optimal solution, so, the search space needs to be reduced to $[-0.05, 0.05]$ to avoid wrong convergence.
-All the algorithms converges quite smoothly following a straight line\subsection{Beale Function}
+All the algorithms converges quite smoothly following a straight line
+
+\subsection{Beale Function}
 \label{beale2D}
@@
 For implementation, it was decided to put constraints on search space, because for the original search space of some functions, like Ackley and Rastrigin, there are other minimas that will confuse every algorithm tested for this paper, and there is no sense on test a local minima procedure on these conditions.
-To restrain the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.
+Restraining the initial solution to some region in the search space was a cheap and ready solution to avoid the algorithms to stop because of stumbling upon the wrong minimum.
 
@@
 While in some cases it has a superb performance (Like Ackley Function), it has very poor performance in Rosenbrock Function and even in Beale Function.
-The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other functions.
+The increase of dimensions makes DFP suffer of numerical imprecision due to the Hessian inversion, except for Rastrigin, and it is the loser algorithm in other test functions used for this work.
 
@@
 
-In fact, there are no Quasi-Newton algorithms that solver the minima problem for an any function.
+In fact, there are no Quasi-Newton algorithms that solves the minima problem for an arbitrary function.
 From the standpoint of performance and convergence, all the algorithms have an average performance and a reasonable convergence, although we have to restrain the search space to a small area near the optimal solution.
